---
title: "mobility_exploration"
output: html_document
date: "2025-09-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's set our scripts directory, data path, and load our geo data

# DATA LOADING/SETUP
## Sourcing scripts and loading packages
```{r echo=FALSE}
## Set Working Directory ----
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}

# R Packages, Function to load and install packages simultaneously
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
} else {require(pacman)}

p_load(tidyverse, sf, knitr, lubridate, mapview, kable, kableExtra)

# Load geo_analysis and geo_mobility functions
source(file.path(scripts_directory, "Utility Scripts", "geo_analysis2.R"))
source(file.path(scripts_directory, "Utility Scripts", "geo_redcap.r"))
source(file.path(scripts_directory, "MCogMobility", "geo_mobility_exploration.r"))
source(file.path(scripts_directory, "MCogMobility", "geo_mobility.r"))
source(file.path(scripts_directory, "Utility Scripts", "geo_lifedata.r"))


data_path = "/Volumes/cnlab/GeoRemote/Data"
```
## Load descriptives
```{r}
platformType = read_csv(file.path(data_path, "Redcap/utility/platformType.csv"))
cond = read_csv(file.path(data_path, "Redcap/utility/conditions.csv"))
```

## Load raw geodata
```{r}
# Load raw geo observations - no exposures/retailers (yet)
baseline = load_geodata("baseline")
intervention = load_geodata("intervention")

# Want to join the geodata?
geodata = rbind(
  baseline %>% dplyr::mutate(Type = "Baseline"),
  intervention %>% dplyr::mutate(Type = "Intervention")
)

# Want sf object?
geodata_sf = geodata %>%
  dplyr::filter(!is.na(lon), !is.na(lat)) %>% 
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272)

# Beware how much space everything can take up, try to only keep the dataframes you need loaded.
```

We've generated the coordinates for the home addresses. Let's create buffer zones and check the participant's location points in them. Two addresses were PO boxes so we will have to skip them. (GR180 and GR282)

## Load Homes and Lifedata and store_visits
```{r}
homes = read_csv(file.path(data_path, "admin", "geocoded_addresses.csv"))
lifedata = load_lifedata()
store_visits = read_csv(file.path(data_path, "RetailerExposure/store_visits_by_period.csv")) %>%
  dplyr::mutate(Store = case_when(
    grepl("7-ELEVEN", Store) ~ "7-Eleven",
    grepl("7-Eleven", Store) ~ "7-Eleven",
    grepl("CVS*", Store) ~ "CVS"
  ))

baseline_store_hour_summary = read_csv(file.path(data_path, "RetailerExposure/baseline_store_hour_summary.csv"))

baseline_store_participant_summary = read_csv(file.path(data_path, "RetailerExposure/baseline_store_participant_summary.csv"))

intervention_store_hour_summary = read_csv(file.path(data_path, "RetailerExposure/intervention_store_hour_summary.csv"))

intervention_store_participant_summary = read_csv(file.path(data_path, "RetailerExposure/baseline_store_participant_summary.csv"))

homes_sf = homes %>%
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272)

```
Looking at the homes, we do have some inconsistencies in starting in baseline:
GR003 - Home is far separated from all geo points
GR024 - Home is within movement track but no points within home - address slightly off?
GR061 - Home is in city but not close to movement track. Majority of nighttime points are around c(lat = 40.02696613066965, lon = -75.04174214918841)
GR123 - Address and tract in city but never touch
GR175 - Address and tract in city but never touch

We still get some issues especially with apartment buildings.

#Processing Mobility Data
## Process max neighbors to see generated clusters
```{r}
results = process_all_participants_max_neighbors(baseline, buffer_distance = 100, point_id_col = "point_id", save_dir = file.path(data_path, "mobility", "max_neighbors_results"), combine_results = TRUE)
```

We still get some issues, especially with apartment buildings, so lets try something else. This might take a long time to run...

Let's see how many points are within 100 feet of each other and use the maximum of those buffers as a comparison. I'll probably save this after I run it since it will probably take a long time.
```{r}
files <- list.files(file.path(data_path, "admin","mobility", "max_neighbors_results"), pattern = "^max_neighbors_.*\\.rds$", full.names = TRUE)
#existing_results <- load_participant_results(file.path(data_path, "admin","mobility", "max_neighbors_results"))
processed_pids <- str_extract(files, "GR\\d+")
all_pids <- unique(baseline$pid)
remaining_pids <- setdiff(all_pids, processed_pids)
for (pid in remaining_pids) {
  process_participant_max_neighbors(
    df = baseline,
    target_pid = pid,
    buffer_distance = 100,
    save_dir = file.path(data_path, "admin","mobility", "max_neighbors_results")
  )
}

result_gr111 <- process_participant_max_neighbors_efficient(
  df = baseline,
  target_pid = "GR312",
  buffer_distance = 100,
  save_dir = file.path(data_path, "admin","mobility", "max_neighbors_results"),
  max_points = 10000,  # Subsample if more than this
  subsample_method = "systematic"  # or "random"
)
```

```{r}
results <- process_all_participants_batches(
  df = intervention,
  buffer_distance = 100,
  batch_size = 10000,
  cluster_match_distance = 200,
  save_dir = file.path(data_path, "admin","mobility", "max_neighbors_results", "Intervention")
)
```

Okay I saved these out as csvs so we can skip the creation and load the csvs in as we need them.

## Load max-neighbor cluster results
### Baseline
```{r}
baseline = read_csv(file.path(data_path, "admin","mobility", "max_neighbors_results", "Baseline", "max_neighbors_results.csv"))
baseline_clusters = read_csv(file.path(data_path, "admin","mobility", "max_neighbors_results", "Baseline", "max_clusters.csv"))
```

### Intervention
```{r}
intervention = read_csv(file.path(data_path, "admin","mobility", "max_neighbors_results", "Intervention", "max_neighbors_results.csv"))
intervention_clusters = read_csv(file.path(data_path, "admin","mobility", "max_neighbors_results", "Intervention", "max_clusters.csv"))
```

## Times left home

Times left home 
- Let's see how many times they left home in each period, and if it matches up with leaving the home cluster
```{r}
leave_home = load_lifedata() 
leave_home_sum = leave_home %>%
  dplyr::filter(grepl("leave_house", `Prompt Label`)) %>%
  dplyr::filter(Response == 1) %>%
  dplyr::mutate(
    # Create new grouping variable
    Period = case_when(
      Type == "Baseline" ~ "Baseline",
      Type == "Intervention" & day <= 14 ~ "Intervention (Days 1-14)",
      Type == "Intervention" & day > 14 ~ "Intervention (Days 15-28)",
      TRUE ~ "Other"
    )
  ) %>%
  dplyr::group_by(pid, Period) %>%
  dplyr::summarise(leave_house_count = n(), .groups = 'drop')

box_plot <- leave_home_sum %>%
  filter(Period != "Other") %>%  # Remove any "Other" entries
  ggplot(aes(x = Period, y = leave_house_count, fill = Period)) +
  geom_boxplot(alpha = 0.7, width = 0.6) +
  geom_jitter(width = 0.2, alpha = 0.5, size = 2) +
  labs(title = "Distribution of Leave House Events by 14-Day Periods",
       x = "Study Period",
       y = "Number of Leave House Events") +
  scale_fill_manual(values = c(
    "Baseline (Days 1-14)" = "skyblue",
    "Intervention (Days 1-14)" = "lightcoral", 
    "Intervention (Days 15-28)" = "darkred"
  )) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels
  )

box_plot
```
Okay, it doesn't really look like there is any difference in period for the amount of times someone has left their house. Let's take a look at people's geodata on days they said they did not leave the house and see if it matches up to their cluster. It only starts at pid GR197, so maybe the lifepaks that were updated around 09-09-23. let's check baseline first.

## Looking at leave_house=1 raw data
```{r}
leave_house = ema %>%
  dplyr::filter(!is.na(leave_house)) %>%
  dplyr::select(pid, pakID, `Notification Date`, Type, cond, day, leave_house) 

leave_house %>%
  pull(pid) %>%
  unique() %>%
  length() %>%
  paste0(" unique participants with leave_house data") %>%
  print()

baseline_leave_house = dplyr::inner_join(leave_house, baseline, by = c("pid", "Notification Date")) %>%
  filter(!is.na(lon), !is.na(lat), leave_house=='2') %>% 
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272)
baseline_clusters_sf = baseline_clusters %>%
  filter(pid %in% baseline_leave_house$pid) %>%
  sf::st_as_sf(coords = c("max_neighbors_lon", "max_neighbors_lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272) %>%
  sf::st_buffer(dist = 500)
listed_home = homes %>%
  filter(pid %in% baseline_leave_house$pid) %>%
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272) %>% 
  sf::st_buffer(dist = 300)
pids = unique(baseline_leave_house$pid)
for (participant in pids) {
  map = mapview(baseline_clusters_sf %>% filter(pid==participant), 
          col.regions = "blue", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "1000ft Buffer") +
     mapview(listed_home %>% filter(pid==participant), 
          col.regions = "yellow", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "1000ft Buffer") +
  mapview(baseline_leave_house %>% filter(pid==participant), 
          col.regions = "red",
          cex = 4,  # Point size
          layer.name = "Individual Points")
    # Print header and map
  cat("\n\n## Participant:", participant, "\n\n")
  print(map)
  cat("\n\n")
}
```
GR228 - looks like cluster is their workplace, not home
GR240 - cluster and home don't match. Maybe I made the cluster buffers too big!
GR273 - This is one where the cluster is actually better than the home
For the most part, the clusters and address overlap pretty perfectly. Maybe we use the home addresses *except* for where there aren't any points within them, but we should maybe have a limit. Is having 5 points within the home buffer good enough or do we want at least 25 points over the course of the entire study before we use a calculated cluster? It also looks like a *lot* (not all!) of people at least did one trip on a day they answered that they did not leave the home. This was only baseline, let's look at baseline + intervention.

Let's review the clusters between baseline, intervention, and listed homes.

## Reviewing clusters vs listed address
```{r}
baseline_clusters_sf = baseline_clusters %>%
  sf::st_as_sf(coords = c("max_neighbors_lon", "max_neighbors_lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272) %>%
  sf::st_buffer(dist = 400)
intervention_clusters_sf = intervention_clusters %>%
  filter(!is.na(cluster_center_lon), !is.na(cluster_center_lat)) %>%
  sf::st_as_sf(coords = c("cluster_center_lon", "cluster_center_lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272) %>%
  sf::st_buffer(dist = 500)
homes_sf = homes %>%
  sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
  sf::st_transform(crs = 2272) %>% 
  sf::st_buffer(dist = 300)
```

```{r}
pids = unique(intervention_clusters_sf$pid)
for (participant in pids) {
  if (nrow(baseline_clusters_sf %>% filter(pid==participant)) > 0 && nrow(intervention_clusters_sf %>% filter(pid==participant)) > 0 && homes_sf %>% filter(pid==participant) %>% nrow() > 0) {
  map = mapview(baseline_clusters_sf %>% filter(pid==participant), 
          col.regions = "red", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Baseline Cluster") +
     mapview(intervention_clusters_sf %>% filter(pid==participant), 
          col.regions = "blue", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Intervention Cluster") +
     mapview(homes_sf %>% filter(pid==participant), 
          col.regions = "yellow", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Home address listed") +
  print(map)
}}
```
Let's look through some of these. For the most part all clusters overlap each other almost perfectly. I'll list out some of the more off ones here:
GR319 - Address *not* near overlapping baseline/intervention clusters
GR317 - Baseline cluster is *not* touching but is near overlapping address/intervention clusters
GR304 - Address *not* near overlapping baseline/intervention clusters
GR287 - each cluster is in a different part of the city
GR286 - Intervention cluster is *not* near the overlapping home and baseline clusters
GR280 - Baseline cluster is *not* near overlapping address/intervention clusters
GR267 - Intervention cluster is *not* near the overlapping home and baseline clusters
GR266 - Baseline cluster is *not* near overlapping address/intervention clusters
GR265 - Intervention cluster is *not* touching but is near the overlapping home and baseline clusters
GR257 - Intervention cluster is *not* near the overlapping home and baseline clusters
GR252 - *Clusters for baseline and intervention are in chicago???*
GR228 - Address *not* near overlapping baseline/intervention clusters
GR211 - One intervention cluster separated from overlapping intervention/baseline/home: Remove
GR210 - Address *not* near overlapping baseline/intervention clusters
GR208 - Address *not* near overlapping baseline/intervention clusters
GR207 - Baseline and one intervention cluster separate from address/intervention cluster - Remove?
GR204 - One intervention cluster separated from overlapping intervention/baseline/home: Remove
[done] GR195 - Baseline cluster is *not* near overlapping address/intervention clusters
[done] GR188 - Intervention cluster is *not* near the overlapping home and baseline clusters
[done] GR184 - One intervention cluster separated from overlapping intervention/baseline/home: Remove
[done] GR183 - Baseline cluster is *not* near overlapping address/intervention clusters
[done] GR175 - Address *not* near overlapping baseline/intervention clusters
[done] GR174 - Address *not* near overlapping baseline/intervention clusters, but clusters are not residential***
[done] GR162 - Address *not* near overlapping baseline/intervention clusters, but kind of close
[done] GR154 - No clusters are near each other!
[done] GR146 - Intervention cluster is *not* near the overlapping home and baseline clusters
[done] GR133 - Intervention cluster is *not* near the overlapping home and baseline clusters (it's in florida!!!)
[done] GR123 - Address *not* near overlapping baseline/intervention clusters, but clusters are not residential***
[done] GR113 - Intervention cluster is *not* near the overlapping home and baseline clusters
[done] GR110 - Address just barely touching the overlapping baseline/intervention clusters
[done] GR105 - Address *not* near overlapping baseline/intervention clusters
[done] GR099 - Address *not* near overlapping baseline/intervention clusters
[done] GR080 - Address *not* near overlapping baseline/intervention clusters
[done] GR065 - Address *not* near overlapping baseline/intervention clusters
[done] GR061 - Address *not* near overlapping baseline/intervention clusters
[done] GR060 - Intervention cluster is *not* near the overlapping home and baseline clusters
[done] GR047 - Address *not* near overlapping baseline/intervention clusters
[done] GR029 - Intervention cluster is *not* near the overlapping home and baseline clusters
[done] GR027 - One intervention cluster separated from overlapping intervention/baseline/home: Remove
[done] GR025 - Address *not* near overlapping baseline/intervention clusters
[done] GR024 - Address *not* near overlapping baseline/intervention clusters
[done] GR017 - Baseline close but not really near overlapping intervention/home clusters
[done] GR013 - One intervention cluster separated from overlapping intervention/baseline/home: Remove
[done] GR012 - Address *not* near overlapping baseline/intervention clusters
[done] GR003 - Address not near clusters, intervention has two clusters but one overlaps baseline cluster

Okay now let's look at each persons geodata within their clusters and also check to see if a cluster is a commercial building (e.g. their work) and if their address would be a better place

## Viewing clusters that don't overlap well with home address
```{r}
geo_data = rbind(baseline %>% select(pid, lat, lon, datetime, day, `Notification Date`),
                 intervention %>% select(pid, lat, lon, datetime, day, `Notification Date`))

ppt = "GR319" #Update this for new maps
map = mapview(baseline_clusters_sf %>% filter(pid==ppt), 
          col.regions = "red", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Baseline Cluster") +
     mapview(intervention_clusters_sf %>% filter(pid==ppt), 
          col.regions = "blue", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Intervention Cluster") +
     mapview(homes_sf %>% filter(pid==ppt), 
          col.regions = "yellow", 
          alpha.regions = 0.3,  # Transparency for buffers
          layer.name = "Home address listed") + 
  mapview(geo_data %>% filter(pid==ppt, !is.na(lon), !is.na(lat), lubridate::hour(datetime) < 8) %>%
            sf::st_as_sf(coords = c("lon", "lat"),
           crs = 4326) %>% 
      sf::st_transform(crs = 2272),
      col.regions = "green")
print(map)
```

Results:
We will use the address as a default unless noted otherwise here
GR003 - *use baseline cluster* - address is nowhere near any points second intervention cluster is at college
GR024 - *use baseline* - address barely has any points, clusters at home
GR061 - *use baseline* - address has no observations
GR065 - *use address?* address has observations, looks like clusters have more and is also residential. maybe check night times - Look at times after 10pm, home address has none and the clusters have a lot across multiple dates.
GR080 - *use address?* address has observations, looks like clusters have more and is also residential. maybe check night times -times before 6am still have observations even if clusters have more... i guess use address
GR105 - *use baseline* - not a ton of observations, maybe look a little closer. clusters could be residential - address only has data for one night
GR110 - *use baseline cluster* - most points are in cluster which is just next to address
GR123 - *use baseline cluster* - address has no points
GR175 - *use baseline cluster* - address has like 3 points..
GR287 - *use address?? - maybe use intervention cluster* - investigate, all three points are in different areas of the city. intervention has consisted nighttime points across entire study
GR319 - *use address?* - investigate


Okay now he have some clusters we can mostly agree on. Let's do some simple checks.
(The new home clusters were saved to homes)
## Edit homes with better clusters 
```{r}
use_baseline_clusters = c("GR003", "GR105","GR110","GR123","GR175")
homes <- homes %>%
  left_join(baseline_clusters %>% 
              filter(pid %in% use_baseline_clusters) %>%
              select(pid, lat_baseline = max_neighbors_lat, lon_baseline = max_neighbors_lon),
            by = "pid") %>%
  mutate(lat = coalesce(lat_baseline, lat),
         lon = coalesce(lon_baseline, lon)) %>%
  select(pid, lat, lon)
```

Let's see how many points are within 300 feet of the home address at night
## Geopoints home at night
```{r}
whole_study_df = rbind(baseline %>% select(pid, lat, lon, datetime, day, `Notification Date`),
                 intervention %>% select(pid, lat, lon, datetime, day, `Notification Date`)) %>%
  filter(!is.na(lon), !is.na(lat))

# Convert to sf objects and transform to projected CRS
home_sf <- st_as_sf(homes, coords = c("lon", "lat"), crs = 4326) %>%
           st_transform(crs = 2272)

df_sf <- st_as_sf(whole_study_df, coords = c("lon", "lat"), crs = 4326) %>%
         st_transform(crs = 2272)

# Create 300ft buffers (convert feet to meters: 1 ft = 0.3048 m)
home_buffers <- st_buffer(home_sf, dist = 300 * 0.3048)

# Step 5: Join observations with their home buffers and check if within buffer
whole_study_df <- whole_study_df %>%
  mutate(
    # Create temporary geometry for joining
    temp_geom = st_geometry(df_sf)
  )

# Join and check intersection
df_with_home <- df_sf %>%
  st_join(home_buffers, join = st_intersects, left = TRUE, suffix = c("", "_home")) %>%
  mutate(at_home = ifelse(pid == pid_home, 1, 0)) %>%
  st_drop_geometry() %>%
  select(-pid_home)

# Step 2: Calculate nighttime home percentages by participant
night_home_pct <- df_with_home %>%
  dplyr::mutate(
    # Extract hour from datetime
    hour = hour(datetime),
    # Define nighttime (10pm-6am means hour >= 22 OR hour < 6)
    is_night = hour >= 22 | hour < 6
  ) %>%
  dplyr::filter(is_night) %>%  # Only nighttime observations
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    total_night_obs = n(),
    night_obs_at_home = sum(at_home, na.rm = TRUE),
    pct_night_at_home = (night_obs_at_home / total_night_obs) * 100
  )

# Step 3: Create boxplot
ggplot(night_home_pct, aes(x = "", y = pct_night_at_home)) +
  geom_boxplot(fill = "lightblue", alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.5) +  # Show individual points
  labs(
    title = "Percentage of Nighttime Observations at Home",
    y = "% of Night Observations at Home",
    x = ""
  ) +
  theme_minimal() +
  theme(axis.text.x = element_blank())

# View the summary statistics
summary(night_home_pct$pct_night_at_home)
```

## Ppts home by hour
```{r}
# Create the summary data
hourly_at_home <- df_with_home %>%
  dplyr::filter(at_home == 1) %>%
  dplyr::mutate(hour = hour(datetime)) %>%
  dplyr::group_by(hour) %>%
  dplyr::summarise(count = n())

# Create bar graph with nighttime highlighted
ggplot(hourly_at_home, aes(x = hour, y = count)) +
  geom_bar(stat = "identity", aes(fill = hour >= 22 | hour < 6)) +
  scale_fill_manual(values = c("steelblue", "darkblue"), 
                    labels = c("Day", "Night"),
                    name = "Time Period") +
  scale_x_continuous(breaks = 0:23) +
  labs(
    title = "Total Observations at Home by Hour of Day",
    x = "Hour of Day (0 = midnight, 12 = noon)",
    y = "Number of Observations"
  ) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank())
```

Okay now lets look at some of the differences in visiting the retailers during baseline and intervention
we'll also add the condition variable so we can see if there are differences between groups

# Retailer Visit Exploration
```{r}
redcap = load_redcap_data()
cvs_stores = read_csv(file.path(data_path, "Retailers","CVS_Retailers.csv"))

# Let's load 7-11 receipts and see if we can match them to the retailer database
seven_eleven_stores = read_csv(file.path(data_path, "Retailers","seven_eleven_stores_geocoded.csv"))

geo_observations = rbind(baseline %>% dplyr::mutate(Type="Baseline"), intervention %>% dplyr::mutate(Type="Intervention")) %>%
  filter(!is.na(lon) & !is.na(lat)) %>%
  dplyr::mutate(
    # Create new grouping variable
    Period = case_when(
      Type == "Baseline" ~ "Baseline",
      Type == "Intervention" & day <= 14 ~ "Intervention (Days 1-14)",
      Type == "Intervention" & day > 14 ~ "Intervention (Days 15-28)",
      TRUE ~ "Other"
    )
  ) %>%
  merge(redcap %>% select(pid, cond), by = "pid", all.x = TRUE)

# Convert dataframes to sf objects (assuming CRS 4326 - WGS84)
seven_eleven_sf <- seven_eleven_stores %>%
  filter(!is.na(lon) & !is.na(lat)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(crs = 2272)

cvs_sf <- cvs_stores %>%
  filter(!is.na(lon) & !is.na(lat)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(crs = 2272)

geo_observations_sf <- geo_observations %>%
  filter(!is.na(lon) & !is.na(lat)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(crs = 2272)

# Create 300m buffers around stores 
cat("Creating store buffers...\n")
seven_eleven_buffer <- st_buffer(seven_eleven_sf, dist = 300)
cvs_buffer <- st_buffer(cvs_sf, dist = 300)

# Combine all store buffers for "any store" analysis
all_stores_buffer <- st_union(st_union(seven_eleven_buffer), st_union(cvs_buffer))

# Find which observations intersect with buffers
cat("Finding observations near stores...\n")
near_7eleven_idx <- st_intersects(geo_observations_sf, seven_eleven_buffer, sparse = FALSE)
near_cvs_idx <- st_intersects(geo_observations_sf, cvs_buffer, sparse = FALSE)
near_any_idx <- st_intersects(geo_observations_sf, all_stores_buffer, sparse = FALSE)

# Add results back to original dataframe
geo_observations <- geo_observations %>%
  dplyr::mutate(
    near_7eleven = rowSums(near_7eleven_idx) > 0,
    near_cvs = rowSums(near_cvs_idx) > 0,
    near_any_store = as.vector(near_any_idx)
  )

# Summary statistics by Type
summary_stats <- geo_observations %>%
  dplyr::group_by(Period) %>%
  dplyr::summarise(
    total_obs = n(),
    near_7eleven = sum(near_7eleven, na.rm = TRUE),
    near_cvs = sum(near_cvs, na.rm = TRUE),
    near_any_store = sum(near_any_store, na.rm = TRUE),
    pct_near_7eleven = round(100 * near_7eleven / total_obs, 2),
    pct_near_cvs = round(100 * near_cvs / total_obs, 2),
    pct_near_any = round(100 * near_any_store / total_obs, 2)
  )

print(summary_stats)

# Statistical tests
cat("\n=== Chi-square tests ===\n")

# Test for any store
contingency_any <- table(geo_observations$Period, geo_observations$near_any_store)
print("Any store proximity by Type:")
print(contingency_any)
print(chisq.test(contingency_any))

# Test for 7-Eleven
contingency_7eleven <- table(geo_observations$Period, geo_observations$near_7eleven)
print("\n7-Eleven proximity by Type:")
print(contingency_7eleven)
print(chisq.test(contingency_7eleven))

# Test for CVS
contingency_cvs <- table(geo_observations$Type, geo_observations$near_cvs)
print("\nCVS proximity by Type:")
print(contingency_cvs)
print(chisq.test(contingency_cvs))
```


```{r}
summary_by_condition <- geo_observations %>%
  dplyr::filter(!is.na(lon) & !is.na(lat)) %>%
  dplyr::group_by(cond, Period) %>%
  dplyr::summarise(
    n_obs = n(),
    n_near_7eleven = sum(near_7eleven),
    n_near_cvs = sum(near_cvs),
    n_near_any = sum(near_any_store),
    pct_near_7eleven = round(100 * n_near_7eleven / n_obs, 2),
    pct_near_cvs = round(100 * n_near_cvs / n_obs, 2),
    pct_near_any = round(100 * n_near_any / n_obs, 2),
    .groups = "drop"
  )

print(summary_by_condition)

# Overall summary by condition (collapsed across periods)
summary_condition_only <- geo_observations %>%
  dplyr::filter(!is.na(lon) & !is.na(lat)) %>%
  dplyr::group_by(cond) %>%
  dplyr::summarise(
    n_obs = n(),
    n_near_7eleven = sum(near_7eleven),
    n_near_cvs = sum(near_cvs),
    pct_near_7eleven = round(100 * n_near_7eleven / n_obs, 2),
    pct_near_cvs = round(100 * n_near_cvs / n_obs, 2),
    .groups = "drop"
  )

print(summary_condition_only)

# Participant-level summary
participant_summary <- geo_observations %>%
  dplyr::filter(!is.na(lon) & !is.na(lat)) %>%
  dplyr::group_by(pid, cond, Period) %>%
  dplyr::summarise(
    n_obs = n(),
    pct_near_7eleven = round(100 * sum(near_7eleven) / n_obs, 1),
    pct_near_cvs = round(100 * sum(near_cvs) / n_obs, 1),
    pct_near_any = round(100 * sum(near_any_store) / n_obs, 1),
    .groups = "drop"
  )

# ============= VISUALIZATIONS =============

# 1. Bar plot: Store proximity by condition and period
plot1 <- summary_by_condition %>%
  select(cond, Period, pct_near_7eleven, pct_near_cvs) %>%
  pivot_longer(cols = starts_with("pct"), 
               names_to = "Store", 
               values_to = "Percentage") %>%
  mutate(
    Store = recode(Store, 
                   "pct_near_7eleven" = "7-Eleven",
                   "pct_near_cvs" = "CVS"),
    cond = factor(cond, labels = c("Condition 1 (CVS)", 
                                             "Condition 2 (7-11)", 
                                             "Condition 3 (Control)"))
  ) %>%
  ggplot(aes(x = Period, y = Percentage, fill = Store)) +
  geom_col(position = "dodge") +
  facet_wrap(~cond, ncol = 1) +
  labs(title = "Observations Within 300m of Stores by Condition and Period",
       y = "% of Observations",
       x = "Period") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  scale_fill_brewer(palette = "Set2")

print(plot1)
ggsave(file.path(data_path, "proximity_by_condition_period.png"), 
       plot1, width = 12, height = 10)

# 2. Side-by-side comparison of conditions
plot2 <- summary_condition_only %>%
  select(cond, pct_near_7eleven, pct_near_cvs) %>%
  pivot_longer(cols = starts_with("pct"), 
               names_to = "Store", 
               values_to = "Percentage") %>%
  mutate(
    Store = recode(Store, 
                   "pct_near_7eleven" = "7-Eleven",
                   "pct_near_cvs" = "CVS"),
    Condition = factor(cond, labels = c("CVS Condition",
                                             "7-11 Condition", 
                                             "Control"))
  ) %>%
  ggplot(aes(x = cond, y = Percentage, fill = Store)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_dodge(width = 0.7), 
            vjust = -0.5, size = 3.5) +
  labs(title = "Store Proximity by Experimental Condition",
       subtitle = "Overall across all periods",
       y = "% of Observations Within 300m",
       x = "Condition") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set1") +
  ylim(0, max(summary_condition_only$pct_near_7eleven, 
              summary_condition_only$pct_near_cvs) * 1.15)

print(plot2)
ggsave(file.path(data_path, "proximity_by_condition_overall.png"), 
       plot2, width = 10, height = 6)

# 3. Line plot showing trends over periods
plot3 <- summary_by_condition %>%
  select(Condition, Period, pct_near_7eleven, pct_near_cvs) %>%
  pivot_longer(cols = starts_with("pct"), 
               names_to = "Store", 
               values_to = "Percentage") %>%
  mutate(
    Store = recode(Store, 
                   "pct_near_7eleven" = "7-Eleven",
                   "pct_near_cvs" = "CVS"),
    Condition = factor(Condition, labels = c("CVS Condition","7-11 Condition", 
                                                                                 "Control"))
  ) %>%
  ggplot(aes(x = Period, y = Percentage, color = Store, group = Store)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~Condition, ncol = 3) +
  labs(title = "Store Proximity Trends Over Time by Condition",
       y = "% of Observations Within 300m",
       x = "Period") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  scale_color_brewer(palette = "Set1")

print(plot3)
ggsave(file.path(data_path, "proximity_trends.png"), 
       plot3, width = 14, height = 5)

# 4. Heatmap of proximity percentages
plot4 <- summary_by_condition %>%
  select(cond, Period, pct_near_7eleven, pct_near_cvs) %>%
  pivot_longer(cols = starts_with("pct"), 
               names_to = "Store", 
               values_to = "Percentage") %>%
  mutate(
    Store = recode(Store, 
                   "pct_near_7eleven" = "7-Eleven",
                   "pct_near_cvs" = "CVS"),
    Condition = factor(cond, labels = c("CVS Cond.",
                                             "7-11 Cond.", 
                                             "Control"))
  ) %>%
  ggplot(aes(x = Period, y = Store, fill = Percentage)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            color = "black", size = 3) +
  facet_wrap(~Condition, ncol = 1) +
  scale_fill_gradient2(low = "white", high = "darkblue", 
                       midpoint = 15, name = "% Near Store") +
  labs(title = "Heatmap: Store Proximity by Condition and Period",
       x = "Period", y = "Store Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(plot4)
ggsave(file.path(data_path, "proximity_heatmap.png"), 
       plot4, width = 12, height = 8)

# 5. Participant-level variability (boxplot)
plot5 <- participant_summary %>%
  select(pid, cond, Period, pct_near_7eleven, pct_near_cvs) %>%
  pivot_longer(cols = starts_with("pct"), 
               names_to = "Store", 
               values_to = "Percentage") %>%
  mutate(
    Store = recode(Store, 
                   "pct_near_7eleven" = "7-Eleven",
                   "pct_near_cvs" = "CVS"),
    Condition = factor(cond, labels = c("CVS Condition",
                                        "7-11 Condition", 
                                         "Control"))
  ) %>%
  ggplot(aes(x = cond, y = Percentage, fill = Store)) +
  geom_boxplot() +
  labs(title = "Distribution of Store Proximity Across Participants",
       subtitle = "Each point represents one participant-period",
       y = "% of Observations Near Store",
       x = "Condition") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set2")

print(plot5)
ggsave(file.path(data_path, "proximity_distribution.png"), 
       plot5, width = 10, height = 6)

# ============= STATISTICAL TESTS =============

cat("\n=== Statistical Tests ===\n")

# Test 1: Does 7-11 condition have more 7-11 proximity than other conditions?
geo_observations_valid <- geo_observations %>%
  filter(!is.na(lon) & !is.na(lat))

# 7-Eleven proximity by condition
test1_table <- table(geo_observations_valid$Condition, geo_observations_valid$near_7eleven)
cat("\n7-Eleven proximity by condition:\n")
print(test1_table)
print(chisq.test(test1_table))

# CVS proximity by condition
test2_table <- table(geo_observations_valid$Condition, geo_observations_valid$near_cvs)
cat("\nCVS proximity by condition:\n")
print(test2_table)
print(chisq.test(test2_table))

# Pairwise comparisons for 7-Eleven
cat("\nPairwise comparisons for 7-Eleven:\n")
for (i in 1:2) {
  for (j in (i+1):3) {
    subset_data <- geo_observations_valid %>% filter(Condition %in% c(i, j))
    test_table <- table(subset_data$Condition, subset_data$near_7eleven)
    cat(sprintf("Condition %d vs %d:\n", i, j))
    print(chisq.test(test_table))
  }
}

# ============= SAVE RESULTS =============

write_csv(summary_by_condition, 
          file.path(data_path, "summary_by_condition_period.csv"))
write_csv(summary_condition_only, 
          file.path(data_path, "summary_by_condition.csv"))
write_csv(participant_summary, 
          file.path(data_path, "participant_summary.csv"))

cat("\n=== Analysis complete! ===\n")
cat("Summary files and plots saved to:", data_path, "\n")
```


Let's see the spread of participants/condition by urbanicity
# Urbanicity Exploration
```{r}
library(tigris)
neighborhood_data = load(file.path(data_path, "EnvironmentalDatabases", "ICPSR", "ICPSR_38606",
                                   "DS0001", "38606-0001-Data.rda"))
pa_tracts <- tracts(state = "42", year = 2020)
de_tracts <- tracts(state = "10", year = 2020)
nj_tracts <- tracts(state = "34", year = 2020)

# Combine them
all_tracts <- rbind(pa_tracts, de_tracts, nj_tracts) %>%
  left_join(da38606.0001, by = c("GEOID" = "TRACT_FIPS10"))

# If not loaded already
homes = load_home_clusters()
people_with_ruca <- st_join(homes, all_tracts %>% sf::st_transform(crs = 2272), join = st_within)

# Let's add the condition to them
people_with_ruca = people_with_ruca %>%
  merge(redcap %>% select(pid, cond), by = "pid", all.x = TRUE)

people_with_ruca %>%
  st_drop_geometry() %>%
  dplyr::group_by(cond, RUCA7) %>%
  dplyr::summarise(n = n(), .groups = "drop") %>%
  dplyr::group_by(cond) %>%
  dplyr::mutate(
    total = sum(n),
    percent = round(n/total * 100, 1)
  ) %>%
  arrange(cond, RUCA7)

# 3. Visualization - stacked bar chart
people_with_ruca %>%
  st_drop_geometry() %>%
  ggplot(aes(x = factor(cond), fill = RUCA7)) +
  geom_bar(position = "fill") +
  labs(
    x = "Condition",
    y = "Proportion",
    fill = "RUCA Category",
    title = "RUCA Distribution by Condition"
  ) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()
```


Okay let's look at times left the house and compare it to ema
# Times left home geo vs ema
```{r}
library(dplyr)
library(sf)


geodata = geodata %>% filter(!is.na(lat), !is.na(lon))

# Step 1: Join dataframes and prepare data
geodata_with_home <- geodata %>%
  dplyr::arrange(pid, datetime) %>%
  dplyr::left_join(
    homes %>% dplyr::rename(home_lat = lat, home_lon = lon),
    by = "pid"
  ) %>%
  dplyr::mutate(
    date = as.Date(datetime),
    hour = as.numeric(format(datetime, "%H"))
  ) %>%
  filter(!is.na(lat), !is.na(lon))

# Step 2: Convert to sf and calculate distances
geodata_sf <- geodata_with_home %>%
  sf::st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  filter(!is.na(home_lon), !is.na(home_lat))

# Create home points
home_points <- geodata_with_home %>%
  filter(!is.na(home_lon), !is.na(home_lat)) %>%
  sf::st_as_sf(coords = c("home_lon", "home_lat"), crs = 4326) %>%
  dplyr::pull(geometry)

# Calculate distance from home (observation-level data with 'type' preserved)
geodata_with_distance <- geodata_sf %>%
  dplyr::mutate(
    home_point = home_points,
    distance_from_home = as.numeric(sf::st_distance(
      sf::st_transform(geometry, 3857),
      sf::st_transform(home_point, 3857),
      by_element = TRUE
    ))
  ) %>%
  dplyr::select(-home_point)

# Step 3: Check for consecutive points >500m from home between 8am-10pm
daily_leave_home <- geodata_with_distance %>%
  dplyr::filter(hour >= 8, hour <= 18) %>%  # 8am to 10pm
  dplyr::group_by(pid) %>%
  dplyr::arrange(pid, datetime) %>%
  dplyr::mutate(
    away_from_home = distance_from_home > 500,
    prev_away = dplyr::lag(away_from_home, default = FALSE),
    is_consecutive_away = away_from_home & prev_away
  ) %>%
  dplyr::group_by(pid, date) %>%
  dplyr::summarise(
    leave_home = as.integer(any(is_consecutive_away)),
    .groups = "drop"
  )

# Step 4: Calculate total distance traveled per day
daily_distance <- geodata_sf %>%
  dplyr::group_by(pid) %>%
  dplyr::arrange(pid, datetime) %>%
  dplyr::mutate(
    distance_to_next = as.numeric(sf::st_distance(
      sf::st_transform(geometry, 3857),
      sf::st_transform(dplyr::lead(geometry), 3857),
      by_element = TRUE
    ))
  ) %>%
  dplyr::group_by(pid, date) %>%
  dplyr::summarise(
    distance_traveled = sum(distance_to_next, na.rm = TRUE),
    .groups = "drop"
  )

# Merge to get study period
daily_leave_home_merged <- daily_leave_home %>%
    dplyr::left_join(
        geodata %>% 
          dplyr::mutate(date = as.Date(datetime)) %>%
          dplyr::select(pid, date, type) %>% distinct(),
        by = c("pid", "date")
    ) %>%
    dplyr::left_join(
      lifedata %>%
        dplyr::filter(!is.na(leave_house)) %>%
        dplyr::rename(date = `Notification Date`,
                      leave_house_ema = leave_house) %>%
        dplyr::mutate(date = as.Date(date)) %>%
        dplyr::select(pid, date, Responded, leave_house_ema),
        by = c("pid", "date")
    )

# Merge to get condition

daily_leave_home_merged <- daily_leave_home_merged %>%
  dplyr::left_join(
    redcap %>% dplyr::select(pid, cond),
    by = "pid"
  )

both_left_home <- daily_leave_home_merged %>%
  dplyr::filter(!is.na(leave_house_ema), leave_home == 1 & leave_house_ema == 1) %>%
  nrow() %>% print()

# Recode leave_house_ema so 1=left, 0=stayed (2 becomes 0)
daily_leave_home_recoded <- daily_leave_home_merged %>%
  dplyr::filter(!is.na(leave_house_ema)) %>%  # Only where we have EMA data
  dplyr::mutate(
    leave_house_ema_binary = dplyr::case_when(
      leave_house_ema == 1 ~ 1,  # Left house
      leave_house_ema == 2 ~ 0,  # Did NOT leave house
      TRUE ~ NA_real_
    )
  )

# Create confusion matrix
confusion_table <- daily_leave_home_recoded %>%
  dplyr::count(leave_home, leave_house_ema_binary) %>%
  tidyr::pivot_wider(names_from = leave_house_ema_binary, 
                     values_from = n, 
                     values_fill = 0,
                     names_prefix = "EMA_")

print("Confusion Matrix:")
print("Rows = GPS leave_home | Columns = EMA leave_house")
print(confusion_table)

# Calculate agreement statistics
agreement_stats <- daily_leave_home_recoded %>%
  dplyr::summarise(
    total_obs = dplyr::n(),
    both_left = sum(leave_home == 1 & leave_house_ema_binary == 1),
    both_stayed = sum(leave_home == 0 & leave_house_ema_binary == 0),
    gps_left_ema_stayed = sum(leave_home == 1 & leave_house_ema_binary == 0),
    gps_stayed_ema_left = sum(leave_home == 0 & leave_house_ema_binary == 1),
    percent_agreement = ((both_left + both_stayed) / total_obs) * 100
  )

print("\nAgreement Statistics:")
print(agreement_stats)

daily_leave_home_recoded <- daily_leave_home_merged %>%
  dplyr::filter(!is.na(leave_house_ema)) %>%
  dplyr::mutate(
    leave_house_ema_binary = dplyr::case_when(
      leave_house_ema == 1 ~ 1,
      leave_house_ema == 2 ~ 0,
      TRUE ~ NA_real_
    ),
    agreement = leave_home == leave_house_ema_binary  # Changed from 'match' to 'agreement'
  ) %>%
  dplyr::left_join(
    redcap %>% dplyr::select(pid, cond),
    by = "pid"
  )

# Get PIDs with perfect agreement
pids_perfect_match <- daily_leave_home_recoded %>%
  dplyr::group_by(pid, type) %>%
  dplyr::summarise(
    total_days = dplyr::n(),
    matching_days = sum(agreement),
    pct_match = (matching_days / total_days) * 100
  ) %>%
  dplyr::filter(pct_match == 100) %>%
  dplyr::pull(pid)

print(paste("PIDs with perfect agreement:", length(pids_perfect_match)))
print(pids_perfect_match)

# Get PIDs with any disagreement
pids_any_mismatch <- daily_leave_home_recoded %>%
  dplyr::group_by(pid, type) %>%
  dplyr::summarise(
    total_days = dplyr::n(),
    matching_days = sum(agreement),
    pct_match = (matching_days / total_days) * 100
  ) %>%
  dplyr::filter(pct_match < 100) %>%
  dplyr::arrange(pct_match)

print(paste("PIDs with any disagreement:", nrow(pids_any_mismatch)))
print(pids_any_mismatch)


mismatch_summary <- daily_leave_home_recoded %>%
  dplyr::group_by(pid, type) %>%
  dplyr::summarise(
    type = dplyr::first(type),
    cond = dplyr::first(cond),
    days_mismatch = sum(!agreement),
    .groups = "drop"
  )

print(mismatch_summary)

# Graph 1: Bar plot of average mismatches by type and condition
avg_mismatch <- mismatch_summary %>%
  dplyr::group_by(type, cond) %>%
  dplyr::summarise(
    mean_mismatch = mean(days_mismatch),
    sd_mismatch = sd(days_mismatch),
    n = dplyr::n(),
    .groups = "drop"
  )

ggplot2::ggplot(avg_mismatch, 
                ggplot2::aes(x = type, y = mean_mismatch, fill = factor(cond))) +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = mean_mismatch - sd_mismatch,
                 ymax = mean_mismatch + sd_mismatch),
    position = ggplot2::position_dodge(width = 0.9),
    width = 0.2
  ) +
  ggplot2::labs(
    title = "Average Days of GPS-EMA Mismatch by Type and Condition",
    x = "Type",
    y = "Mean Days with Mismatch",
    fill = "Condition"
  ) +
  ggplot2::theme_minimal()
```

Okay let's see if we learn why there might be a mismatch
```{r}
# 1. Count geo observations per pid/date
geo_counts <- geodata_with_home %>%
  group_by(pid, date) %>%
  summarise(
    n_observations = n(),
    .groups = 'drop'
  )

# View the results
print(geo_counts)

# Using semi_join (only returns columns from geo_counts)
geo_counts_disagreement <- geo_counts %>%
  semi_join(
    daily_leave_home_recoded %>% 
      filter(agreement == FALSE) %>%
      st_drop_geometry(),
    by = c("pid", "date")
  )

# Using semi_join (only returns columns from geo_counts)
geo_counts_agreement <- geo_counts %>%
  semi_join(
    daily_leave_home_recoded %>% 
      filter(agreement == TRUE) %>%
      st_drop_geometry(),
    by = c("pid", "date")
  )


# 2. Average geo observations per pid (across all their dates)
avg_agreement <- geo_counts_agreement %>%
  group_by(pid) %>%
  summarise(
    avg_observations = mean(n_observations),
    .groups = 'drop'
  )

avg_disagreement <- geo_counts_disagreement %>%
  group_by(pid) %>%
  summarise(
    avg_observations = mean(n_observations),
    .groups = 'drop'
  )

print(avg_per_pid)

combined_avg <- bind_rows(
  avg_agreement %>% mutate(group = "Agreement"),
  avg_disagreement %>% mutate(group = "Disagreement")
)

# Create boxplot
ggplot(combined_avg, aes(x = group, y = avg_observations, fill = group)) +
  geom_boxplot() +
  labs(
    title = "Average Geo Observations per PID",
    x = "Agreement Status",
    y = "Average Number of Observations"
  ) +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend since x-axis shows groups
```

Eh, agreement does have slightly higher observations but not by much. Let's start looking at retailers. I'd like to see if maybe we can see a difference in unique retailers per day by period, or total unique retailers by period. Then we'll see how many people visit the retailers they did their store visits at during baseline.

# Retailer visit exploration Baseline vs Intervention
## Unique Retailers
```{r}
baseline = load_stay_events(type="Baseline", small_buffer = 100, conditional_buffer = 1000)

# BASELINE - Calculate daily stats first, then aggregate
baseline_retailer_stats <- baseline %>%
  dplyr::filter(!is.na(retailer_id)) %>%
  dplyr::group_by(pid, Notification.Date) %>%
  dplyr::summarise(daily_unique_retailers = n_distinct(retailer_id),
                   .groups = 'drop') %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    avg_unique_retailers_per_day = mean(daily_unique_retailers),
    n_unique_dates = n(),  # Each row is a unique date for this pid
    .groups = 'drop'
  ) %>%
  dplyr::left_join(
    baseline %>%
      dplyr::filter(!is.na(retailer_id)) %>%
      dplyr::group_by(pid) %>%
      dplyr::summarise(total_unique_retailers = n_distinct(retailer_id),
                       .groups = 'drop'),
    by = "pid"
  ) %>%
  dplyr::mutate(retailers_per_unique_date = total_unique_retailers / n_unique_dates)

print(baseline_retailer_stats)

# INTERVENTION - Calculate daily stats first, then aggregate
intervention = load_stay_events(type="Intervention", small_buffer = 100, conditional_buffer = 1000)
intervention = intervention %>% mutate(Notification.Date = as.Date(datetime))

intervention_retailer_stats <- intervention %>%
  dplyr::filter(!is.na(retailer_id)) %>%
  dplyr::group_by(pid, Notification.Date) %>%
  dplyr::summarise(daily_unique_retailers = n_distinct(retailer_id),
                   .groups = 'drop') %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    avg_unique_retailers_per_day = mean(daily_unique_retailers),
    n_unique_dates = n(),  # Each row is a unique date for this pid
    .groups = 'drop'
  ) %>%
  dplyr::left_join(
    intervention %>%
      dplyr::filter(!is.na(retailer_id)) %>%
      dplyr::group_by(pid) %>%
      dplyr::summarise(total_unique_retailers = n_distinct(retailer_id),
                       .groups = 'drop'),
    by = "pid"
  ) %>%
  dplyr::mutate(retailers_per_unique_date = total_unique_retailers / n_unique_dates)

print(intervention_retailer_stats)

# COMBINED STATS
retailer_stats = baseline_retailer_stats %>%
  dplyr::left_join(intervention_retailer_stats, by="pid", suffix=c("_baseline","_intervention")) %>%
  dplyr::filter(!is.na(avg_unique_retailers_per_day_intervention)) %>%
  mutate(day_difference = avg_unique_retailers_per_day_intervention - avg_unique_retailers_per_day_baseline,
         avg_difference = (total_unique_retailers_intervention - total_unique_retailers_baseline),
         retailers_per_date_difference = retailers_per_unique_date_intervention - retailers_per_unique_date_baseline)

# 14-DAY PERIOD ANALYSIS - with per-participant date counting
intervention_retailer_stats_14day <- intervention %>%
  dplyr::filter(!is.na(retailer_id)) %>%
  # Create 14-day period variable
  dplyr::mutate(period = ceiling(day / 14)) %>%
  # Calculate daily unique retailers within each period
  dplyr::group_by(pid, period, Notification.Date) %>%
  dplyr::summarise(daily_unique_retailers = n_distinct(retailer_id),
                   .groups = 'drop') %>%
  # Calculate average per day within each period for each pid
  dplyr::group_by(pid, period) %>%
  dplyr::summarise(
    avg_unique_retailers_per_day = mean(daily_unique_retailers),
    n_days_in_period = n(),  # Each row is a unique date for this pid-period
    .groups = 'drop'
  ) %>%
  # Join with total unique retailers per period per pid
  dplyr::left_join(
    intervention %>%
      dplyr::filter(!is.na(retailer_id)) %>%
      dplyr::mutate(period = ceiling(day / 14)) %>%
      dplyr::group_by(pid, period) %>%
      dplyr::summarise(total_unique_retailers = n_distinct(retailer_id),
                       .groups = 'drop'),
    by = c("pid", "period")
  ) %>%
  dplyr::mutate(retailers_per_unique_date = total_unique_retailers / n_days_in_period)

print(intervention_retailer_stats)

# Calculate difference between period 2 and period 1
period_comparison <- intervention_retailer_stats_14day %>%
  dplyr::filter(period %in% c(1, 2)) %>%
  dplyr::select(pid, period, total_unique_retailers) %>%
  tidyr::pivot_wider(names_from = period, 
                     values_from = total_unique_retailers,
                     names_prefix = "period_") %>%
  dplyr::mutate(difference_period2_minus_period1 = period_2 - period_1)

print(period_comparison)
```

Interesting. So we are definitely getting more unique retailers in intervention... Let's look at the specific 
stores they visited during intervention and see if they visited them during baseline
## Create Store visit baseline vs intervention
```{r}
receipt_coding = read_csv("/Volumes/cnlab/GeoRemote/Data/Receipts/Receipt_coding.csv") %>%
  dplyr::select(pID, Store, `Address - # Street`, Date) %>%
  dplyr::filter(!is.na(`Address - # Street`)) %>%
  dplyr::mutate(Date = mdy(Date)) %>%
  dplyr::group_by(pID, Store, `Address - # Street`) %>%
  dplyr::summarise(n_days = n(),
                   first_visit = min(Date, na.rm = TRUE),
    last_visit = max(Date, na.rm = TRUE)) %>%
  dplyr::distinct() %>%
  dplyr::rename(pid = pID)


post_stores = read_csv("/Volumes/cnlab/GeoRemote/Data/Retailers/seven_eleven_stores_geocoded.csv") %>%
  dplyr::mutate(store = "7-11")
no_post_stores = read_csv("/Volumes/cnlab/GeoRemote/Data/Retailers/CVS_Retailers.csv") %>% 
  dplyr::mutate(full_address = address,
         store = "CVS")

stores = rbind(post_stores, no_post_stores %>% dplyr::select(full_address, lat, lon, store))

stores_joined <- receipt_coding %>%
  crossing(stores) %>%
  dplyr::filter(str_detect(full_address, fixed(`Address - # Street`))) %>%
  dplyr::select(-any_of(c("full_address"))) %>%
  dplyr::distinct()


# Convert result to sf object
stores_joined_sf <- stores_joined %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  sf::st_transform(crs = 2272)

# Must have homes_sf loaded
stores_with_distance <- stores_joined_sf %>%
  dplyr::mutate(
    home_geom = homes_sf$geometry[match(pid, homes_sf$pid)],
    distance_ft = as.numeric(st_distance(geometry, home_geom, by_element = TRUE)),
    distance_mi = round(distance_ft / 5280, 2)
  ) %>%
  dplyr::select(-home_geom)

store_visits = stores_with_distance %>% 
  dplyr::select(pid, Store, `Address - # Street`, n_days, first_visit, last_visit, distance_ft, distance_mi) %>%
  dplyr::mutate(type="Real")

# Convert baseline to sf object
baseline_sf <- baseline %>%
  dplyr::filter(!is.na(lat) & !is.na(lon)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  sf::st_transform(crs = 2272) %>%
  dplyr::mutate(Notification.Date = as.Date(datetime))

# Spatial join - finds matches within a buffer (e.g., 10 meters)
store_days <- st_join(stores_with_distance, baseline_sf, 
                      join = st_is_within_distance, 
                      dist = 1000) %>%
  dplyr::filter(pid.x == pid.y) %>%
  dplyr::rename(pid = pid.x) %>%
  dplyr::select(-pid.y)

# Create summary of hour-visits per store per day per participant
baseline_store_hour_summary <- store_days %>%
  st_drop_geometry() %>%  # Drop spatial geometry for faster processing
  dplyr::mutate(
    date = as.Date(datetime),
    hour = hour(datetime)
  ) %>%
  # Group by participant, store, address, and date-hour combination
  dplyr::group_by(pid, Store, `Address - # Street`, date, hour) %>%
  dplyr::summarize(n_points = n(), .groups = 'drop') %>%
  # Now count distinct hours per day
  dplyr::group_by(pid, Store, `Address - # Street`, date) %>%
  dplyr::summarize(
    n_hour_visits = n(),  # Number of distinct hours visited
    hours_visited = paste(sort(unique(hour)), collapse = ", "),
    .groups = 'drop'
  ) %>%
  arrange(pid, Store, date)

# Create a wider summary showing total hour-visits per store per participant
baseline_store_participant_summary <- baseline_store_hour_summary %>%
  dplyr::group_by(pid, Store, `Address - # Street`) %>%
  dplyr::summarize(
    n_days = n_distinct(date),
    total_hour_visits = sum(n_hour_visits),
    avg_hour_visits_per_day = mean(n_hour_visits),
    .groups = 'drop'
  )
  
  
baseline_stores = store_days %>%
  st_drop_geometry() %>%  # Remove geometry column after join
  dplyr::filter(pid.x == pid.y) %>%  # Only keep matches for same participant
  dplyr::group_by(pid.x, Store, `Address - # Street`) %>%
  dplyr::summarise(
    n_days = n_distinct(Notification.Date),
    first_visit = min(Notification.Date, na.rm = TRUE),
    last_visit = max(Notification.Date, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  dplyr::rename(pid = pid.x) %>%
  dplyr::arrange(pid, desc(n_days)) %>%
  dplyr::mutate(type="Baseline")

# And intervention
intervention_sf = intervention %>%
  dplyr::filter(!is.na(lat) & !is.na(lon)) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326, remove = FALSE) %>%
  sf::st_transform(crs = 2272) %>%
  dplyr::mutate(Notification.Date = as.Date(datetime))

# Spatial join - finds matches within a buffer (e.g., 10 meters)
store_days <- st_join(stores_with_distance, intervention_sf, 
                      join = st_is_within_distance, 
                      dist = 1000) %>%
  dplyr:: filter(pid.x == pid.y) %>%
  dplyr::rename(pid = pid.x) %>%
  dplyr::select(-pid.y)
  
# Create summary of hour-visits per store per day per participant
intervention_store_hour_summary <- store_days %>%
  st_drop_geometry() %>%  # Drop spatial geometry for faster processing
  dplyr::mutate(
    date = as.Date(datetime),
    hour = hour(datetime)
  ) %>%
  # Group by participant, store, address, and date-hour combination
  dplyr::group_by(pid, Store, `Address - # Street`, date, hour) %>%
  dplyr::summarize(n_points = n(), .groups = 'drop') %>%
  # Now count distinct hours per day
  dplyr::group_by(pid, Store, `Address - # Street`, date) %>%
  dplyr::summarize(
    n_hour_visits = n(),  # Number of distinct hours visited
    hours_visited = paste(sort(unique(hour)), collapse = ", "),
    .groups = 'drop'
  ) %>%
  dplyr::arrange(pid, Store, date)

# Create a wider summary showing total hour-visits per store per participant
intervention_store_participant_summary <- intervention_store_hour_summary %>%
  dplyr::group_by(pid, Store, `Address - # Street`) %>%
  dplyr::summarize(
    n_days = n_distinct(date),
    total_hour_visits = sum(n_hour_visits),
    avg_hour_visits_per_day = mean(n_hour_visits),
    .groups = 'drop'
  )
  

intervention_stores = store_days %>%
  st_drop_geometry() %>%  # Remove geometry column after join
  dplyr::filter(pid.x == pid.y) %>%  # Only keep matches for same participant
  dplyr::group_by(pid.x, Store, `Address - # Street`) %>%
  dplyr::summarise(
    n_days = n_distinct(Notification.Date),
    first_visit = min(Notification.Date, na.rm = TRUE),
    last_visit = max(Notification.Date, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  dplyr::rename(pid = pid.x) %>%
  dplyr::arrange(pid, desc(n_days)) %>%
  dplyr::mutate(type="Intervention")

geodata_store_visits = rbind(baseline_stores, intervention_stores) %>%
  left_join(stores_with_distance %>% 
              dplyr::select(pid, Store, `Address - # Street`, distance_ft, distance_mi), by=c("pid","Store", "Address - # Street")) %>%
  rbind(store_visits)

# To save
write_csv(geodata_store_visits, file.path(data_path, "RetailerExposure/store_visits_by_period.csv"))
```

## Analyze store visits by distance
Some Notes about this:
GR207 made some visits to a CVS store in maryland, not caught because it was on 'philadelphia avenue' -_-

```{r}
store_visits_summary = geodata_store_visits %>%
  dplyr::mutate(weighted_distance_ft = distance_ft * n_days) %>%
  dplyr::group_by(type, pid, Store) %>%
  dplyr::summarise(
    total_days = sum(n_days),
    total_weighted_distance_ft = sum(weighted_distance_ft),
    avg_distance_ft = total_weighted_distance_ft / total_days)

# 1. Compare by Type only
ggplot(store_visits_summary, aes(x = type, y = avg_distance_ft, fill = type)) +
  geom_boxplot() +
  labs(title = "Average Distance by Type",
       x = "Type",
       y = "Average Distance (ft)") +
  theme_minimal() +
  theme(legend.position = "none")

# 2. Compare by Store only
ggplot(store_visits_summary, aes(x = Store, y = avg_distance_ft, fill = Store)) +
  geom_boxplot() +
  labs(title = "Average Distance by Store",
       x = "Store",
       y = "Average Distance (ft)") +
  theme_minimal()

# 3. Compare by both Type and Store (side-by-side)
ggplot(store_visits_summary, aes(x = type, y = avg_distance_ft, fill = Store)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(title = "Average Distance by Type and Store",
       x = "Type",
       y = "Average Distance (ft)") +
  theme_minimal()

# 4. Alternative: Faceted view
ggplot(store_visits_summary, aes(x = type, y = avg_distance_ft, fill = type)) +
  geom_boxplot() +
  facet_wrap(~Store) +
  labs(title = "Average Distance by Type, Separated by Store",
       x = "Type",
       y = "Average Distance (ft)") +
  theme_minimal() +
  theme(legend.position = "none")

# 5. Get summary statistics
store_visits_summary %>%
  dplyr::group_by(type, Store) %>%
  dplyr::summarise(
    n = n(),
    mean_dist = mean(avg_distance_ft, na.rm = TRUE),
    median_dist = median(avg_distance_ft, na.rm = TRUE),
    sd_dist = sd(avg_distance_ft, na.rm = TRUE)
  ) %>%
  dplyr::arrange(type, Store)
```

# Mobility Package Exploration
## Clusters
Make sure baseline and intervention geodata is loaded (they do not need to be sf objects). This will use the adapted mobility package code found in geo_mobility.r

First half runs the cluster processing, second half shows a comparison between baseline/intervention cluster numbers.

### Preproc & Calculate Clusters
```{r}
# Make sure geodata is loaded.
# Preprocess
baseline_proc = mobility_preprocess_geodata(baseline)[[1]]
intervention_proc = mobility_preprocess_geodata(intervention)[[1]]

# Calculate Clusters (5 points in 25m is default)
baseline_clusters = calculate_clusters(baseline_proc %>%
                                         st_as_sf(., coords = c("lon", "lat"), crs = 4326) %>%
         st_transform(crs = 2272), eps = 100)
intervention_clusters = calculate_clusters(intervention_proc %>%
                                         st_as_sf(., coords = c("lon", "lat"), crs = 4326) %>%
         st_transform(crs = 2272), eps = 250)
```

#### Compare Periods
```{r}
baseline_summary <- baseline_clusters %>%
  sf::st_drop_geometry() %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    n_baseline_clusters = n_distinct(clusterID),
    n_baseline_days = n_distinct(`Notification Date`))

intervention_summary <- intervention_clusters %>%
  sf::st_drop_geometry() %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    n_intervention_clusters = n_distinct(clusterID),
    n_baseline_days = n_distinct(`Notification Date`))

# Join them together
cluster_comparison <- full_join(baseline_summary, intervention_summary, by = "pid") %>%
  dplyr::rename(n_intervention_days = n_baseline_days.y,
         n_baseline_days = n_baseline_days.x)

# Optional: Replace NAs with 0 if a pid exists in one dataset but not the other
cluster_comparison <- cluster_comparison %>%
  dplyr::mutate(
    n_baseline_clusters = replace_na(n_baseline_clusters, 0),
    n_intervention_clusters = replace_na(n_intervention_clusters, 0)
  )

print(cluster_comparison)

cluster_comparison %>%
  kable(col.names = c("Participant ID", 
                      "Baseline Clusters", 
                      "Baseline Days",
                      "Intervention Clusters", 
                      "Intervention Days"),
        caption = "Cluster Comparison by Participant",
        format = "html") %>%
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE) %>%
  row_spec(0, background = "white", color = "black")
# For an even nicer interactive table, you could use:
# library(DT)
# datatable(cluster_comparison)

# Filter for participants with data in both periods
comparison_plot_data <- cluster_comparison %>%
  filter(n_baseline_days > 0 & n_intervention_days > 0)

# Create a comparison plot
ggplot(comparison_plot_data, aes(x = n_baseline_clusters, y = n_intervention_clusters)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
  labs(title = "Baseline vs Intervention Cluster Counts",
       subtitle = "Red line indicates equal clusters in both periods",
       x = "Number of Baseline Clusters",
       y = "Number of Intervention Clusters") +
  theme_minimal() +
  coord_equal()
```

### Calculate Home Cluster     
```{r}

baseline_home_calc = calculate_home_night(baseline_clusters)
intervention_home_calc = calculate_home_night(intervention_clusters)
```

#### Compare home clusters to homes
```{r}
baseline_home_centroids <- baseline_home_calc %>%
  dplyr::filter(clusterID == home) %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(geometry = st_centroid(st_union(geometry)), .groups = "drop")

# Calculate home centroids for intervention
intervention_home_centroids <- intervention_home_calc %>%
  dplyr::filter(clusterID == home) %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(geometry = st_centroid(st_union(geometry)), .groups = "drop")

# Join and calculate distances
home_distance <- baseline_home_centroids %>%
  st_drop_geometry() %>%
  dplyr::mutate(baseline_geom = st_geometry(baseline_home_centroids)) %>%
  dplyr::left_join(
    intervention_home_centroids %>%
      st_drop_geometry() %>%
      dplyr::mutate(intervention_geom = st_geometry(intervention_home_centroids)),
    by = "pid"
  ) %>%
  dplyr::mutate(
    home_distance_m = as.numeric(st_distance(
      st_sfc(baseline_geom, crs = st_crs(baseline_home_calc)),
      st_sfc(intervention_geom, crs = st_crs(baseline_home_calc)),
      by_element = TRUE
    ))
  ) %>%
  dplyr::select(pid, home_distance_m)

home_distance <- home_distance %>%
  mutate(home_distance_m = round(as.numeric(home_distance_m), 2))

# View the data
print(home_distance)

# Box plot with points
ggplot(home_distance, aes(x = "", y = home_distance_m)) +
  geom_boxplot(fill = "steelblue", alpha = 0.5) +
  geom_jitter(width = 0.1, alpha = 0.6, size = 2) +
  labs(title = "Distance Between Baseline and Intervention Home Clusters",
       x = "",
       y = "Distance (meters)") +
  theme_minimal()

summary(home_distance$home_distance_m)

# Okay so there are just a few BIG outliers here. Let's see how close the home clusters are to our defined homes

# Make sure to load homes_sf from the cell at the beginning of the markdown.
baseline_home_distance <- baseline_home_centroids %>%
  sf::st_drop_geometry() %>%
  dplyr::mutate(baseline_geom = st_geometry(baseline_home_centroids)) %>%
  dplyr::left_join(
    homes_sf %>%
      st_drop_geometry() %>%
      dplyr::mutate(home_geom = st_geometry(homes_sf)),
    by = "pid"
  ) %>%
  dplyr::mutate(
    baseline_distance_m = as.numeric(st_distance(
      st_sfc(baseline_geom, crs = st_crs(baseline_home_calc)),
      st_sfc(home_geom, crs = st_crs(homes_sf)),
      by_element = TRUE
    ))
  ) %>%
  dplyr::select(pid, baseline_distance_m)

# Calculate distance between intervention home centroids and homes_sf
intervention_home_distance <- intervention_home_centroids %>%
  st_drop_geometry() %>%
  dplyr::mutate(intervention_geom = st_geometry(intervention_home_centroids)) %>%
  dplyr::left_join(
    homes_sf %>%
      st_drop_geometry() %>%
     dplyr::mutate(home_geom = st_geometry(homes_sf)),
    by = "pid"
  ) %>%
  dplyr::mutate(
    intervention_distance_m = as.numeric(st_distance(
      st_sfc(intervention_geom, crs = st_crs(intervention_home_calc)),
      st_sfc(home_geom, crs = st_crs(homes_sf)),
      by_element = TRUE
    ))
  ) %>%
  dplyr::select(pid, intervention_distance_m)

# Combine both distances
home_distance_comparison <- baseline_home_distance %>%
  dplyr::full_join(intervention_home_distance, by = "pid") %>%
  dplyr::mutate(
    baseline_distance_m = round(baseline_distance_m, 2),
    intervention_distance_m = round(intervention_distance_m, 2)
  )

# Create summary statistics
baseline_summary <- summary(home_distance_comparison$baseline_distance_m)
intervention_summary <- summary(home_distance_comparison$intervention_distance_m)

summary_df <- data.frame(
  Statistic = names(baseline_summary),
  Baseline = as.vector(baseline_summary),
  Intervention = as.vector(intervention_summary)
)

summary_df %>%
  kable(caption = "Distance from Home Summary Statistics (meters)",
        digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE) %>%
  row_spec(0, background = "white", color = "black")
```

### Total Distance
```{r}
baseline_total_distance = calculate_total_distance(
  baseline_home_calc,
  baseline_proc,
  baseline
) %>%
  # Remove duplicate lat/lon columns (keeping .x versions)
  dplyr::select(-lat.y, -lon.y) %>%
  # Rename remaining columns to remove .x suffix
  dplyr::rename(lat = lat.x, lon = lon.x)

baseline_avg_distance_per_day <- baseline_total_distance %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    total_distance_m = first(distanceM),  # Get the distance value (same for all rows per pid)
    total_distance_km = first(distanceKM),
    n_days = n_distinct(`Notification Date`),  # Count unique days
    avg_distance_per_day_m = total_distance_m / n_days,
    avg_distance_per_day_km = total_distance_km / n_days
  ) %>%
  dplyr::mutate(
    avg_distance_per_day_m = round(avg_distance_per_day_m, 2),
    avg_distance_per_day_km = round(avg_distance_per_day_km, 2)
  )

intervention_total_distance = calculate_total_distance(
  intervention_home_calc,
  intervention_proc,
  intervention
) %>%
  # Remove duplicate lat/lon columns (keeping .x versions)
  dplyr::select(-lat.y, -lon.y) %>%
  # Rename remaining columns to remove .x suffix
  dplyr::rename(lat = lat.x, lon = lon.x)

intervention_avg_distance_per_day <- intervention_total_distance %>%
  dplyr::group_by(pid) %>%
  dplyr::summarise(
    total_distance_m = first(distanceM),  # Get the distance value (same for all rows per pid)
    total_distance_km = first(distanceKM),
    n_days = n_distinct(`Notification Date`),  # Count unique days
    avg_distance_per_day_m = total_distance_m / n_days,
    avg_distance_per_day_km = total_distance_km / n_days
  ) %>%
  dplyr::mutate(
    avg_distance_per_day_m = round(avg_distance_per_day_m, 2),
    avg_distance_per_day_km = round(avg_distance_per_day_km, 2)
  )

distance_comparison <- baseline_avg_distance_per_day %>%
  dplyr::select(pid, 
         baseline_avg_m = avg_distance_per_day_m,
         baseline_avg_km = avg_distance_per_day_km) %>%
  dplyr::full_join(
    intervention_avg_distance_per_day %>%
      dplyr::select(pid, 
             intervention_avg_m = avg_distance_per_day_m,
             intervention_avg_km = avg_distance_per_day_km),
    by = "pid"
  ) %>%
  dplyr::mutate(
    difference_m = intervention_avg_m - baseline_avg_m,
    difference_km = intervention_avg_km - baseline_avg_km,
    percent_change = ((intervention_avg_m - baseline_avg_m) / baseline_avg_m) * 100
  )

baseline_sum <- summary(distance_comparison$baseline_avg_km)
intervention_sum <- summary(distance_comparison$intervention_avg_km)
difference_sum <- summary(distance_comparison$difference_km)

# Create summary statistics table
summary_stats <- data.frame(
  Statistic = names(baseline_sum),
  Baseline_km = as.vector(baseline_sum),
  Intervention_km = as.vector(intervention_sum),
  Difference_km = as.vector(difference_sum)
)

summary_stats %>%
  kable(col.names = c("Statistic", "Baseline (km/day)", "Intervention (km/day)", "Difference (km/day)"),
        caption = "Average Daily Distance Comparison",
        digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE) %>%
  row_spec(0, background = "white", color = "black") %>%
  column_spec(1:4, background = "white", color = "black")

# Create side-by-side boxplots
distance_comparison %>%
  pivot_longer(cols = c(baseline_avg_km, intervention_avg_km),
               names_to = "period",
               values_to = "avg_km") %>%
  mutate(period = ifelse(period == "baseline_avg_km", "Baseline", "Intervention")) %>%
  ggplot(aes(x = period, y = avg_km, fill = period)) +
  geom_boxplot(alpha = 0.7, outlier.shape = 16, outlier.size = 2) +
  geom_jitter(width = 0.2, alpha = 0.3, size = 1.5) +
  scale_fill_manual(values = c("Baseline" = "steelblue", "Intervention" = "coral")) +
  labs(title = "Average Daily Distance: Baseline vs Intervention",
       x = "Period",
       y = "Average Daily Distance (km)") +
  theme_minimal() +
  theme(legend.position = "none",
        text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5))
```

#### Total Distance by Condition/Period
Some outliers? GR027, GR046, GR177, GR236
```{r}
distance_comparison = distance_comparison %>%
  dplyr::left_join(cond, by="pid") %>%
  dplyr::filter(! pid %in% c("GR027","GR046", "GR177", "GR236")) # Comment out to keep

distance_comparison %>%
  pivot_longer(cols = c(baseline_avg_km, intervention_avg_km),
               names_to = "period",
               values_to = "avg_km") %>%
  dplyr::mutate(period = ifelse(period == "baseline_avg_km", "Baseline", "Intervention"),
         period = factor(period, levels = c("Baseline", "Intervention")),
         cond = factor(cond)) %>%
  ggplot(aes(x = "", y = avg_km, fill = period)) +
  geom_boxplot(alpha = 0.7, outlier.shape = 16) +
  geom_jitter(width = 0.2, alpha = 0.3, size = 1.5) +
  facet_grid(period ~ cond, labeller = label_both) +
  scale_fill_manual(values = c("Baseline" = "steelblue", "Intervention" = "coral")) +
  labs(title = "Average Daily Distance by Period and Condition",
       x = "",
       y = "Average Daily Distance (km)",
       fill = "Period") +
  theme_minimal() +
  theme(legend.position = "bottom",
        strip.text = element_text(size = 11, face = "bold"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

distance_comparison %>%
  dplyr::filter(!is.na(baseline_avg_km) & !is.na(intervention_avg_km)) %>%
  tidyr::pivot_longer(cols = c(baseline_avg_km, intervention_avg_km),
               names_to = "period",
               values_to = "avg_km") %>%
  dplyr::mutate(period = ifelse(period == "baseline_avg_km", "Baseline", "Intervention"),
         period = factor(period, levels = c("Baseline", "Intervention")),
         cond = factor(cond, labels = c("Condition 1", "Condition 2", "Condition 3"))) %>%
  ggplot2::ggplot(ggplot2::aes(x = period, y = avg_km, color = cond, group = cond)) +
  ggplot2::stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, size = 1) +
  ggplot2::stat_summary(fun = mean, geom = "line", size = 1.2) +
  ggplot2::stat_summary(fun = mean, geom = "point", size = 4) +
  ggplot2::scale_color_brewer(palette = "Set1") +
  ggplot2::labs(title = "Mean Average Daily Distance by Condition",
       subtitle = "Error bars show standard error",
       x = "",
       y = "Average Daily Distance (km)",
       color = "Condition") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5),
        plot.subtitle = ggplot2::element_text(hjust = 0.5, size = 9),
        legend.position = "bottom")

```

### Calculate Places Visited

```{r}
baseline_places_visited_complete = calculate_places_visited(baseline_clusters)
baseline_places_visited = baseline_places_visited_complete %>%
  dplyr::select(pid, placesVisited_baseline = placesVisited) %>%
  dplyr::distinct()

intervention_places_visited_complete = calculate_places_visited(intervention_clusters) 
intervention_places_visited = intervention_places_visited_complete %>%
  dplyr::select(pid, placesVisited_intervention = placesVisited) %>%
  dplyr::distinct()

placesVisited = baseline_places_visited %>%
  dplyr::full_join(intervention_places_visited, by="pid") %>%
  dplyr::mutate(
    difference = placesVisited_intervention - placesVisited_baseline
  )

# Add condition
placesVisited = placesVisited %>%
  dplyr::left_join(cond, by="pid")

placesVisited %>%
  dplyr::filter(!is.na(placesVisited_baseline) & !is.na(placesVisited_intervention)) %>%
  dplyr::filter(!pid %in% c("GR027","GR046", "GR177", "GR236")) %>%
  tidyr::pivot_longer(cols = c(placesVisited_baseline, placesVisited_intervention),
               names_to = "period",
               values_to = "n_places") %>%
  dplyr::mutate(
    period = ifelse(period == "placesVisited_baseline", "Baseline", "Intervention"),
    period = factor(period, levels = c("Baseline", "Intervention")),
    cond = factor(cond, labels = c("Condition 1", "Condition 2", "Condition 3"))
  ) %>%
  ggplot2::ggplot(ggplot2::aes(x = period, y = n_places, color = cond, group = cond)) +
  ggplot2::stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, size = 1) +
  ggplot2::stat_summary(fun = mean, geom = "line", size = 1.2) +
  ggplot2::stat_summary(fun = mean, geom = "point", size = 4) +
  ggplot2::scale_color_brewer(palette = "Set1") +
  ggplot2::labs(title = "Mean Number of Places Visited by Condition",
       subtitle = "Error bars show standard error",
       x = "",
       y = "Number of Places Visited",
       color = "Condition") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5),
        plot.subtitle = ggplot2::element_text(hjust = 0.5, size = 9),
        legend.position = "bottom")

summary_table <- placesVisited %>%
  dplyr::filter(!is.na(placesVisited_baseline) & !is.na(placesVisited_intervention)) %>%
  dplyr::group_by(cond) %>%
  dplyr::summarise(
    n = dplyr::n(),
    mean_baseline = round(mean(placesVisited_baseline, na.rm = TRUE), 1),
    mean_intervention = round(mean(placesVisited_intervention, na.rm = TRUE), 1),
    mean_difference = round(mean(difference, na.rm = TRUE), 1),
    median_baseline = median(placesVisited_baseline, na.rm = TRUE),
    median_intervention = median(placesVisited_intervention, na.rm = TRUE),
    median_difference = median(difference, na.rm = TRUE)
  ) %>%
  dplyr::mutate(cond = paste("Condition", cond))

summary_table %>%
  kable(col.names = c("Condition", "N", "Mean Baseline", "Mean Intervention", 
                      "Mean Difference", "Median Baseline", "Median Intervention", "Median Difference"),
        caption = "Summary Statistics: Places Visited by Condition") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE) %>%
  row_spec(0, background = "white", color = "black") %>%
  column_spec(1:8, background = "white", color = "black")
```

### Calculate key locations
```{r}
baseline_key_locations = calculate_key_locations(baseline_home_calc %>% sf::st_drop_geometry())
intervention_key_locations = calculate_key_locations(intervention_home_calc %>% sf::st_drop_geometry())
```

### Calculate time at home/travel
```{r}
baseline_time_mobility <- calculate_time_at_home(baseline_key_locations) %>%
  calculate_travel_time()
intervention_time_mobility <- calculate_time_at_home(intervention_key_locations) %>%
  calculate_travel_time()
```

### Calculate centroids and entropy
```{r}
baseline_time_mobility <- baseline_time_mobility %>%
  left_join(
    baseline_home_calc %>% 
      dplyr::select(pid, datetime, geometry),  # Select only needed columns
    by = c("pid", "datetime")
  ) %>%
  st_sf()

baseline_entropy = calculate_entropy(baseline_time_mobility)

intervention_time_mobility <- intervention_time_mobility %>%
  left_join(
    intervention_home_calc %>% 
      dplyr::select(pid, datetime, geometry),  # Select only needed columns
    by = c("pid", "datetime")
  ) %>%
  st_sf()

intervention_entropy = calculate_entropy(intervention_time_mobility)
```

### Calculate Routine Index
```{r}
baseline_routine = calculate_routine_index(baseline_entropy)
intervention_routine = calculate_routine_index(intervention_entropy)
```

```{r}
visualize_by_pid <- function(pid_value,
                             intervention_proc,
                             intervention_centroids_100m,
                             intervention_centroids_250m) {
  
  
  # Create mapview layers with different colors
  map <- mapview(intervention_proc %>% dplyr::filter(pid == pid_value), 
                 col.regions = "blue",
                 color = "blue",
                 cex = 4,
                 layer.name = "Individual Points",
                 legend = TRUE) +
    mapview(intervention_centroids_100m %>% dplyr::filter(pid==pid_value),
            col.regions = "red",
            color = "red", 
            cex = 8,
            pch = 17,  # triangle
            layer.name = "Clusters 100m",
            legend = TRUE) +
    mapview(intervention_centroids_250m %>% dplyr::filter(pid==pid_value),
            col.regions = "green",
            color = "green",
            cex = 10,
            pch = 15,  # square
            layer.name = "Clusters 250m",
            legend = TRUE)
  
  return(map)
}


visualize_by_pid("GR031",
                 intervention_proc,
                 intervention_centroids_100m,
                 intervention_centroids_250m)
```