---
title: "baseline_analysis"
author: "Ben Muzekari"
date: "2024-08-02"
output: html_document
---

### requires that ncooper_replication has already been run 

```{r}
library(robustHD)
winsorizedDF <- All_data %>% group_by(pid) %>%
 mutate(exposures = (Winsorize(exposures, na.rm = TRUE)),
         daily_average_crave = (Winsorize(daily_average_crave, na.rm = TRUE)),
         daily_average_neg = (Winsorize(daily_average_neg, na.rm = TRUE)),
         stress_rating = (Winsorize(stress_rating, na.rm = TRUE)),
         microagg = (Winsorize(microagg, na.rm = TRUE)),
         daily_cigs = Winsorize(daily_cigs, na.rm = TRUE))
```




## Calculate within and between exposure, microaggression, stress, and negative mood measures
```{r}
#splitting exposures into within and between components
winsorizedDF$exposureSplit <- with(winsorizedDF, ave(exposures, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$discrim_any_split <- with(winsorizedDF, ave(microagg, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$discrim_count_split <- with(winsorizedDF, ave(microagg_count, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$neg_split <- with(winsorizedDF, ave(daily_average_neg, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$stress_split <- with(winsorizedDF, ave(stress_rating, pid, FUN=function(x) mean(x, na.rm=TRUE)))

#Set the grand mean
winsorizedDF$exposureGMean <- ave(winsorizedDF$exposureSplit, na.rm = TRUE)
winsorizedDF$discrim_any_GMean <- ave(winsorizedDF$discrim_any_split, na.rm = TRUE)
winsorizedDF$discrim_count_GMean <- ave(winsorizedDF$discrim_count_split, na.rm = TRUE)
winsorizedDF$neg_GMean <- ave(winsorizedDF$neg_split, na.rm = TRUE)
winsorizedDF$stress_GMean <- ave(winsorizedDF$stress_split, na.rm = TRUE)

#Subtract grand mean from the raw exposures
winsorizedDF$exposurec <- winsorizedDF$exposures - winsorizedDF$exposureGMean
winsorizedDF$discrim_any_c <- winsorizedDF$microagg - winsorizedDF$discrim_any_GMean
winsorizedDF$discrim_count_c <- winsorizedDF$microagg_count - winsorizedDF$discrim_count_GMean
winsorizedDF$neg_c <- winsorizedDF$daily_average_neg - winsorizedDF$neg_GMean
winsorizedDF$stress_c <- winsorizedDF$stress_rating - winsorizedDF$stress_GMean

#Now we create a between-subjects mean from this grand mean centered variable
winsorizedDF$exposurebw <- with(winsorizedDF, ave(exposurec, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$discrim_any_bw <- with(winsorizedDF, ave(discrim_any_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$discrim_count_bw <- with(winsorizedDF, ave(discrim_count_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$neg_bw <- with(winsorizedDF, ave(neg_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
winsorizedDF$stress_bw <- with(winsorizedDF, ave(stress_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))

#And then a within-subjects mean using this between-subject mean
winsorizedDF$exposurewn <- winsorizedDF$exposurec - winsorizedDF$exposurebw
winsorizedDF$discrim_any_wn <- winsorizedDF$discrim_any_c - winsorizedDF$discrim_any_bw
winsorizedDF$discrim_count_wn <- winsorizedDF$discrim_count_c - winsorizedDF$discrim_count_bw
winsorizedDF$neg_wn <- winsorizedDF$neg_c - winsorizedDF$neg_bw
winsorizedDF$stress_wn <- winsorizedDF$stress_c - winsorizedDF$stress_bw

```

# correlation of negative affect variables
```{r}
cor(winsorizedDF$daily_average_neg, winsorizedDF$stress_rating, use = "complete.obs")
library(rmcorr)
rmcorr(pid, neg_wn, stress_wn, winsorizedDF)

```
# Hypotheses & Research Questions
(switched all models from lme to lmer becuase lme was getting errors when I tried adding random effects)

##Stress as an outcome

### Hypothesis 1:
On days when smokers experience interpersonal discrimination, they will feel more stressed and negative than they will on days when they don’t experience interpersonal discrimination 
```{r}
H1a <- lmer(stress_rating ~ 1 + discrim_any_wn + discrim_any_bw + day + (1 + discrim_any_wn | pid), 
            data = winsorizedDF)
summary(H1a)

summary(lmer(stress_rating ~ 1 + discrim_count_wn + discrim_count_bw + day + (1 + discrim_count_wn | pid), 
            data = winsorizedDF))


winsorizedDFNA <- winsorizedDF[complete.cases(winsorizedDF$stress_rating),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$microagg),]
#winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$daysCrave),]
#winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$regSpeedStayEvent_100ft),]

H1aplot <- lmer(stress_rating ~ 1 + microagg + day + (1  | pid), 
            data = winsorizedDFNA)
summary(H1aplot)
```
###Plot/Viz
```{r}
winsorizedDFNA$predH1 <- predict(H1aplot)

ggplot(data=winsorizedDFNA, aes(x=microagg, y=predH1, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="green3") +
  xlab("Interpersonal Discrimination") + ylab("Predicted Stress") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination makes people more stresed")
```


### main effect of exposure
```{r}
Slow.Stress<- lmer(stress_rating ~ 1 + exposurewn + exposurebw + day + (1 | pid), 
             data=winsorizedDF) #model failed to converge so took out random effects 
summary(Slow.Stress)
```
### H4 interactions on stress outcome
```{r}
#only main effect of wn and bw discrim
H4aSlow.Stress<- lmer(stress_rating ~ 1 + discrim_any_wn + discrim_any_bw + exposurewn + exposurebw + discrim_any_wn*exposurewn + day + (1 | pid), 
             data=winsorizedDF) #model failed to converge so took out random effects 

summary(H4aSlow.Stress)
```

##Negative mood as an outcome

### Hypothesis 1:
On days when smokers experience interpersonal discrimination, they will feel more stressed and negative than they will on days when they don’t experience interpersonal discrimination 
```{r}
H1a_neg <- lmer(daily_average_neg ~ 1 + discrim_any_wn + discrim_any_bw + day + (1 + discrim_any_wn | pid), 
            data = winsorizedDF)
summary(H1a_neg)


# following model is rank deficient with or without random effects
summary(lmer(daily_average_neg ~ 1 + discrim_count_wn + discrim_count_bw + day + (1  | pid), 
            data = winsorizedDF))

```


### main effect of exposure
```{r}
Slow.Neg<- lmer(daily_average_neg ~ 1 + exposurewn + exposurebw + day + (1 | pid), 
             data=winsorizedDF) #model failed to converge so took out random effects 
summary(Slow.Neg)
```
### H4 interactions on neg mood outcome
```{r}
#only main effect of wn and bw discrim
H4aSlow.Neg<- lmer(daily_average_neg ~ 1 + microagg + exposurewn + exposurebw + microagg*exposurewn + day + (1 | pid), 
             data=winsorizedDF) #model failed to converge so took out random effects 

summary(H4aSlow.Neg)
```

## Cig craving as an outcome
```{r}
H2 <- lmer(daily_average_crave ~ 1 + discrim_any_wn + discrim_any_bw + day + (1  | pid), 
            data = winsorizedDF)
summary(H2)

summary(lmer(daily_average_crave ~ 1 + discrim_count_wn + discrim_count_bw + day + (1 + discrim_count_wn | pid), 
            data = winsorizedDF))


H2 <- lmer(daily_average_crave ~ 1 + microagg +  day + (1  | pid), 
            data = winsorizedDF)
summary(H2)
```

```{r}
winsorizedDFNA <- winsorizedDF[complete.cases(winsorizedDF$stress_rating),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$microagg),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$daily_average_crave),]
```

```{r}
H2a_plot <- lmer(daily_average_crave ~ 1 + microagg + day + (1  | pid), 
            data = winsorizedDFNA)
summary(H2a_plot)
```

###Plot/Viz
```{r}
winsorizedDFNA$predH2 <- predict(H2a_plot)

ggplot(data=winsorizedDFNA, aes(x=microagg, y=predH2, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="green3") +
  xlab("Interpersonal Discrimination") + ylab("Predicted Craving") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination increases cigarette craving")
``````


```{r}
winsorizedDFNA <- winsorizedDF[complete.cases(winsorizedDF$stress_rating),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$microagg),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$daily_average_crave),]
winsorizedDFNA <- winsorizedDFNA[complete.cases(winsorizedDFNA$daily_cigs),]

```

```{r}
H3a_plot <- lmer(daily_cigs ~ 1 + microagg + day + (1  | pid), 
            data = winsorizedDFNA)
summary(H3a_plot)
```

###Plot/Viz
```{r}
winsorizedDFNA$predH3 <- predict(H3a_plot)

ggplot(data=winsorizedDFNA, aes(x=microagg, y=predH3, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="green3") +
  xlab("Interpersonal Discrimination") + ylab("Predicted Smoking") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination increases cigarette smoking")
``````

###Craving, exposure, microaggression
```{r}
H4crave <- lmer(daily_average_crave ~ 1 + microagg + exposurewn + exposurebw + microagg*exposurewn + day + (1  | pid), data = winsorizedDF, na.action = na.omit) #took out discrim_any_wn and discrim_any_wn*regSpeedExpo_100ft_wn random effects to to singularity error; also exposurewn

summary(H4crave)


Hnew <- lmer(exposures ~ 1 + microagg + daily_average_crave + day + (1  | pid), data = winsorizedDF, na.action = na.omit) #took out discrim_any_wn and discrim_any_wn*regSpeedExpo_100ft_wn random effects to to singularity error; also exposurewn

summary(Hnew)


Hnew <- lmer(daily_cigs ~ 1 + exposurewn + exposurebw + microagg + day + (1  | pid), data = winsorizedDF, na.action = na.omit) #took out discrim_any_wn and discrim_any_wn*regSpeedExpo_100ft_wn random effects to to singularity error; also exposurewn
summary(Hnew)
```


H4aSlow.Neg<- lmer(daily_average_neg ~ 1 + discrim_any_wn + discrim_any_bw + exposurewn + exposurebw + discrim_any_wn*exposurewn + day + (1 | pid), 
             data=winsorizedDF) #model failed to converge so took out random effects 


####plotting interaction 
```{r}
library(ggiraph)
library(ggiraphExtra)
library(ggeffects)

# Define the variables for the interaction plot
terms <- c("discrim_any_wn", "exposurewn")

# Use ggpredict to calculate and plot the interaction
interact_plot_primary1 <- ggpredict(H4aSlow.Neg, terms)

# Print the interaction plot
plot(interact_plot_primary1)
```
