---
title: "baseline_analysis"
author: "Ben Muzekari"
date: "2024-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#R Packages ##Fuction to load and install packages simultaneously
```{r}
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
```

##load and install
```{r, results = FALSE}
packages <- c("plyr", "tidyverse", "ggplot2", "DescTools", "psych", "lmerTest") #need to run plyr first or else it will cause problems!!!!
ipak(packages)
```

## Load in REDCap Data
```{r}
# If your working directory is in the GeoRemote Scripts folder, it'll set the correct path. If it's not, it will ask you to select a file in the directory
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}

source(file.path(scripts_directory, "Utility Scripts/geo_redcap.r"))
redcap <- load_redcap()
```

## Select variables of interest
```{r}
redcap_vars <-redcap[, c("pid","age_calc","gender","ethnicity",
                         "race___1", "race___2", "race___3","race___4",
                         "race___5","race___6","race___7")]
```

## Recode race into one variable and drop old columns
```{r}
# Create a race column based on existing columns
redcap_vars$races_selected <- apply(redcap_vars[, c("race___1", "race___2", "race___3", "race___4", "race___5", "race___6", "race___7")], 1, function(row) {
  selected_indices <- which(row == 1)
  if(length(selected_indices) == 0) {
    NA
  } else {
    as.numeric(selected_indices)
  }
})

# Drop old race columns
cols_to_remove <- grep("^race___", names(redcap_vars))
redcap_vars <- redcap_vars[, -cols_to_remove]
```

## How variables are coded
```{r}
#Gender
# 1	Man
# 4	Non-binary
# 5	Genderqueer
# 6	Agender
# 7	Gender fluid
# 2	Woman
# 8	I prefer to self-describe
# 3	Prefer not to say

# Latino/Hispanic Ethnicity
# 1	Yes
# 0	No
# 2	Prefer not to say

#Race
# 4	race___4	American Indian or Alaska Native
# 1	race___1	Asian
# 2	race___2	Black
# 3	race___3	Pacific Islander or Hawaiian Native
# 5	race___5	White
# 6	race___6	Prefer to self-describe
# 7	race___7	Prefer not to say
```


## Recode variables to factors
```{r}
# Convert race column to character
redcap_vars$races_selected <- as.character(redcap_vars$races_selected)

# Recode if multiple values are selected
redcap_vars$races_selected <- sapply(redcap_vars$races_selected, function(x) {
  # check if value is a list (indicates more than one selection)
  if (grepl("c\\(", x)) {
    return("8")  # If it is a list, recode as 8 (More than one)
  } else {
    return(x)  # If it is not a list, keep as is
  }
})

# Define levels for gender factor
gender_levels <- c("1", "2", "3", "4", "5", "6", "7", "8")
gender_labels <- c("Man", "Woman", "Prefer not to say", "Non-binary", "Genderqueer", 
                   "Agender", "Gender fluid", "I prefer to self-describe")

# Define levels for race factor
race_levels <- c("1", "2", "3", "4", "5", "6", "7", "8")
race_labels <- c("Asian", "Black", "Pacific Islander or Hawaiian Native", "American Indian or Alaska Native", "White", "Prefer to self-describe", "Prefer not to say", "More than one")

# Define levels for ethnicity factor
ethnicity_levels <- c("0", "1", "2")
ethnicity_labels <- c("No", "Yes", "Prefer not to say")

# Rename vars
names(redcap_vars)[names(redcap_vars) == "races_selected"] <- "race"
names(redcap_vars)[names(redcap_vars) == "age_calc"] <- "age"

# Convert columns to factors
redcap_vars <- redcap_vars %>%
  mutate(
    ethnicity = factor(ethnicity, levels = ethnicity_levels, labels = ethnicity_labels),
    gender = factor(gender, levels = gender_levels, labels = gender_labels),
    race = factor(race, levels = race_levels, labels = race_labels)
  )
```

## Read in FTND data
```{r}
FTND <- read_csv("/Volumes/cnlab/GeoRemote/Data/Qualtrics/scored_survey_measures/ftsd.csv")
```

# Rename score column and subset to first session
```{r}
#FTND_Session_1 <- FTND %>%
#  rename(FTND_score = score) %>%
#  filter(sm_session == 1)


FTND_Session_1 <-FTND[which(FTND$sm_session==1),]
FTND_Session_1$FTND_score=FTND_Session_1$score
```

# Merge redcap variables with FTND
```{r}
Covariates <- redcap_vars %>%
  left_join(FTND_Session_1 %>% select(pid, FTND_score), by = "pid")
```

## Read in EMA data
```{r}
source(file.path(scripts_directory, "Utility Scripts/geo_lifedata.r"))
ema = load_lifedata()
```

# Filter to only Baseline period
```{r}
ema_baseline <- ema %>%
  filter(Type == 'Baseline')
```


## Merge EMA data and demographics data
```{r}
EMA_Baseline_Covariates <- ema_baseline %>%
  left_join(Covariates, by = c("pid")) 
```

## Add average negative mood
```{r}
avg_neg <- EMA_Baseline_Covariates %>%
        filter(`Prompt Label` == "neg") %>%
        group_by(pid, `Notification Date`) %>%
        summarise(daily_average_neg = mean(as.numeric(Response), na.rm = TRUE))

# Merge the result back to the original dataframe
EMA_Baseline_Covariates <- left_join(EMA_Baseline_Covariates, select(avg_neg, pid, `Notification Date`, daily_average_neg), by = c("pid", "Notification Date"))
```

## Subset to daily stress value 
```{r}
EMA_Baseline_Covariates_Distinct_stress <- EMA_Baseline_Covariates[which(EMA_Baseline_Covariates$`Prompt Label`=="stress"),]
EMA_Baseline_Covariates_Distinct_stress$stress_rating <- EMA_Baseline_Covariates_Distinct_stress$Response
```

## Obtain distinct rows --- not using since I'm subsetting for stress
#```{r}
#EMA_Baseline_Covariates_Distinct <- EMA_Baseline_Covariates  %>% 
#  distinct(pid, day, daily_average_crave, daily_average_neg, daily_cigs, age, gender, ethnicity, race)
#```


## Load in geo data.  ----- change to "no expired" version
```{r}
baseline_1000ft_100ft <- read.csv("/Volumes/cnlab/GeoRemote/Data/RetailerExposure/ConditionalBuffer/Baseline/1000ft_100ft_exposures_activeRetailersOnly.csv")
```


## Get exposure counts by pid and day
```{r}
baseline_1000ft_100ft_exposures <- baseline_1000ft_100ft %>%
  group_by(pid, Notification.Date, day) %>%
  ## I added day in the line above
  summarise(
    exposures = ifelse(all(is.na(exposure_id)), 0, n_distinct(exposure_id, na.rm = TRUE))
  )

# print pid count
num_unique_values <- length(unique(baseline_1000ft_100ft_exposures$pid))
print(num_unique_values)
#[1] 273
```

```{r}
# check if people have less than x days

# Sample data creation for illustration purposes
# ema <- data.frame(pid = c(rep(1, 14), rep(2, 13), rep(3, 14)), day = c(1:14, 1:13, 1:14))

# Define the expected days
expected_days <- 1:14

# Function to check if all expected days are present
check_days <- function(df) {
  # Get the unique pid values
  pids <- unique(df$pid)
  
  # Initialize a vector to store pids that don't have all days
  missing_days_pids <- c()
  
  # Loop through each pid and check for missing days
  for (pid in pids) {
    # Subset the dataframe for the current pid
    pid_df <- df[df$pid == pid, ]
    
    # Get the days present for the current pid
    pid_days <- pid_df$day
    
    # Check if any expected day is missing
    if (!all(expected_days %in% pid_days)) {
      missing_days_pids <- c(missing_days_pids, pid)
    }
  }
  
  return(missing_days_pids)
}

# Apply the function to the ema dataframe
missing_pids <- check_days(baseline_1000ft_100ft_exposures)
#missing_pids <- check_days(All_data)

# Print the pids with missing days
missing_pids
```


## Merge Geo data and EMA_Demographics data
```{r}
All_data <- left_join(baseline_1000ft_100ft_exposures, EMA_Baseline_Covariates_Distinct_stress, by = c("pid", "day"))

All_data$stress_rating<-as.numeric(All_data$stress_rating)
```

## Create df with averages by pid
```{r}
average_df_by_pid <- All_data %>%
  group_by(pid) %>%
  summarize(
    exposures = mean(exposures, na.rm = TRUE),
    daily_average_crave = mean(daily_average_crave, na.rm = TRUE),
    daily_average_neg = mean(daily_average_crave, na.rm = TRUE),
    daily_cigs = mean(daily_cigs, na.rm = TRUE),
    daily_stress = mean(as.numeric(stress_rating), na.rm = TRUE),
    daily_micro_count = mean(microagg_count, na.rm = TRUE)
  )
```

# Get exposures summary and plot hists
```{r}
describe(All_data$exposures)
hist(na.omit(All_data$exposures), breaks = 2000) # each row
#hist(average_df_by_pid$exposures, breaks = 100, main = "Histogram of Average Exposures by PID", xlab = "Average Exposures") # each person's average
```

## Calculate within and between exposure, microaggression, stress, and negative mood measures
```{r}
#splitting exposures into within and between components
All_data$exposureSplit <- with(All_data, ave(exposures, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$discrim_any_split <- with(All_data, ave(microagg, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$discrim_count_split <- with(All_data, ave(microagg_count, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$neg_split <- with(All_data, ave(daily_average_neg, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$stress_split <- with(All_data, ave(stress_rating, pid, FUN=function(x) mean(x, na.rm=TRUE)))

#Set the grand mean
All_data$exposureGMean <- ave(All_data$exposureSplit, na.rm = TRUE)
All_data$discrim_any_GMean <- ave(All_data$discrim_any_split, na.rm = TRUE)
All_data$discrim_count_GMean <- ave(All_data$discrim_count_split, na.rm = TRUE)
All_data$neg_GMean <- ave(All_data$neg_split, na.rm = TRUE)
All_data$stress_GMean <- ave(All_data$stress_split, na.rm = TRUE)

#Subtract grand mean from the raw exposures
All_data$exposurec <- All_data$exposures - All_data$exposureGMean
All_data$discrim_any_c <- All_data$microagg - All_data$discrim_any_GMean
All_data$discrim_count_c <- All_data$microagg_count - All_data$discrim_count_GMean
All_data$neg_c <- All_data$daily_average_neg - All_data$neg_GMean
All_data$stress_c <- All_data$stress_rating - All_data$stress_GMean

#Now we create a between-subjects mean from this grand mean centered variable
All_data$exposurebw <- with(All_data, ave(exposurec, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$discrim_any_bw <- with(All_data, ave(discrim_any_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$discrim_count_bw <- with(All_data, ave(discrim_count_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$neg_bw <- with(All_data, ave(neg_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))
All_data$stress_bw <- with(All_data, ave(stress_c, pid, FUN=function(x) mean(x, na.rm=TRUE)))

#And then a within-subjects mean using this between-subject mean
All_data$exposurewn <- All_data$exposurec - All_data$exposurebw
All_data$discrim_any_wn <- All_data$discrim_any_c - All_data$discrim_any_bw
All_data$discrim_count_wn <- All_data$discrim_count_c - All_data$discrim_count_bw
All_data$neg_wn <- All_data$neg_c - All_data$neg_bw
All_data$stress_wn <- All_data$stress_c - All_data$stress_bw

```

# correlation of negative affect variables
```{r}
cor(All_data$daily_average_neg, All_data$stress_rating, use = "complete.obs")

rmcorr(pid, daysNeg_wn, stress_wn, All_data)
```
# Hypotheses & Research Questions
(switched all models from lme to lmer becuase lme was getting errors when I tried adding random effects)

##Stress as an outcome

### Hypothesis 1:
On days when smokers experience interpersonal discrimination, they will feel more stressed and negative than they will on days when they don’t experience interpersonal discrimination 
```{r}
H1a <- lmer(stress_rating ~ 1 + discrim_any_wn + discrim_any_bw + day + (1 + discrim_any_wn | pid), 
            data = All_data)
summary(H1a)

summary(lmer(stress_rating ~ 1 + discrim_count_wn + discrim_count_bw + day + (1 + discrim_count_wn | pid), 
            data = All_data))

H1a <- lmer(stress_rating ~ 1 + microagg+ day + (1 | pid), 
            data = All_data)

summary(H1a)

```


### main effect of exposure
```{r}
Slow.Stress<- lmer(stress_rating ~ 1 + exposurewn + exposurebw + day + (1 | pid), 
             data=All_data) #model failed to converge so took out random effects 
summary(Slow.Stress)
```
### H4 interactions on stress outcome
```{r}
#only main effect of wn and bw discrim
H4aSlow.Stress<- lmer(stress_rating ~ 1 + discrim_any_wn + discrim_any_bw + exposurewn + exposurebw + discrim_any_wn*exposurewn + day + (1 | pid), 
             data=All_data) #model failed to converge so took out random effects 

summary(H4aSlow.Stress)
```

##Stress as an outcome

### Hypothesis 1:
On days when smokers experience interpersonal discrimination, they will feel more stressed and negative than they will on days when they don’t experience interpersonal discrimination 
```{r}
H1a_neg <- lmer(daily_average_neg ~ 1 + discrim_any_wn + discrim_any_bw + day + (1 + discrim_any_wn | pid), 
            data = All_data)
summary(H1a_neg)


# following model is rank deficient with or without random effects
summary(lmer(daily_average_neg ~ 1 + discrim_count_wn + discrim_count_bw + day + (1  | pid), 
            data = All_data))

```


### main effect of exposure
```{r}
Slow.Neg<- lmer(daily_average_neg ~ 1 + exposurewn + exposurebw + day + (1 | pid), 
             data=All_data) #model failed to converge so took out random effects 
summary(Slow.Neg)
```
### H4 interactions on neg mood outcome
```{r}
#only main effect of wn and bw discrim
H4aSlow.Neg<- lmer(daily_average_neg ~ 1 + discrim_any_wn + discrim_any_bw + exposurewn + exposurebw + discrim_any_wn*exposurewn + day + (1 | pid), 
             data=All_data) #model failed to converge so took out random effects 

summary(H4aSlow.Neg)
```

## Cig craving as an outcome
```{r}
H2 <- lmer(daily_average_crave ~ 1 + discrim_any_wn + discrim_any_bw + day + (1  | pid), 
            data = All_data)
summary(H2)

summary(lmer(daily_average_crave ~ 1 + discrim_count_wn + discrim_count_bw + day + (1 + discrim_count_wn | pid), 
            data = All_data))

```



###Craving, exposure, microaggression
```{r}
H4crave <- lmer(daily_average_crave ~ 1 + discrim_any_wn + discrim_any_bw + exposurewn + exposurebw + discrim_any_wn*exposurewn + day + (1  | pid), data = All_data, na.action = na.omit) #took out discrim_any_wn and discrim_any_wn*regSpeedExpo_100ft_wn random effects to to singularity error; also exposurewn

summary(H4crave)
```
```{r}
#library(robustHD)
winsorizedDF <- All_data %>% group_by(pid) %>%
 mutate(exposures = (Winsorize(exposures, na.rm = TRUE)),
         daily_average_crave = (Winsorize(daily_average_crave, na.rm = TRUE)),
         daily_average_neg = (Winsorize(daily_average_neg, na.rm = TRUE)),
         stress_rating = (Winsorize(stress_rating, na.rm = TRUE)),
         microagg = (Winsorize(microagg, na.rm = TRUE)))
```

