---
title: "Aim3_mobility"
author: "NC"
date: "2024-12-18"
output: html_document
---

# Setup {.tabset}
## Set scripts directory
```{r, echo=FALSE}
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

## Load analysis functions
```{r}
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis.r")) # <- Change the file to load different scripts, e.g. "geo_lifedata.r"

source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_lifedata.r"))
```

Load ema
```{r}
ema = load_lifedata()
ema_wide = load_lifedata(format = "wide")
```

## Load EMA, and covariate data
```{r}
EMA_Baseline_Covariates_Distinct = load_ema_with_covs(Type="Baseline",
                                                      ema_variables = c("day", "day_in_study","daily_average_crave", "daily_cigs", "daily_stress"),
                        redcap_variables = c("pid","age","gender","ethnicity","race","intervention_complete","cond")) %>%
  add_survey_measure("FTND", session=1) %>%
  add_descriptives(vars="platformType") %>%
  distinct()
```

```{r}
EMA_Intervention_Covariates_Distinct = load_ema_with_covs(Type="Intervention",
                                                      ema_variables = c("day", "day_in_study","daily_average_crave", "daily_cigs", "daily_stress"),
                        redcap_variables = c("pid","age","gender","ethnicity","race","intervention_complete","cond")) %>%
  add_survey_measure("FTND", session=3) %>%
  add_descriptives(vars="platformType") %>%
  distinct()


#[num_receipts]
```
## Load and reduce mobility data 
```{r}
mobility <- read_csv("/Volumes/cnlab/GeoRemote/Data/RetailerExposure/Mobility/geodata_clusters_minPts20.csv")

Mobility_Distinct <- mobility  %>% 
  distinct(pid, type, uniqueLocations, timeSpentAtHome, travelTime, totaltime, entropy, placesVisited)
```

## Append daily count dataframes 
```{r}
EMA_Baseline_Covariates_Distinct$phase<-"baseline"
EMA_Intervention_Covariates_Distinct$phase<-"intervention"

data_daily_comb_long <- rbind(EMA_Baseline_Covariates_Distinct, EMA_Intervention_Covariates_Distinct)
  
data_daily_comb_long <- data_daily_comb_long %>%
  mutate(
    cond = case_when(
      cond == 1 ~ "Low",
      cond == 2 ~ "High",
      cond == 3 ~ "Control",
      TRUE ~ as.character(cond) 
    ),
    cond = factor(cond, levels = c("Control", "Low", "High"))
  )

data_daily_comb_long$cond_base<-ifelse(data_daily_comb_long$cond=="Control",0,1)

data_daily_comb_long <- data_daily_comb_long %>%
  filter(!is.na(cond))
```

## Example lmer models
```{r}
lme_craving_itt <- lmer(daily_average_crave ~ phase * cond + (phase|pid), data = data_daily_comb_long)
summary(lme_craving_itt)

lme_stress_itt <- lmer(daily_stress ~ phase * cond + (phase|pid), data = data_daily_comb_long)
summary(lme_stress_itt)

lme_stress_itt <- lmer(daily_stress ~ phase * cond_base + (phase|pid), data = data_daily_comb_long)
summary(lme_stress_itt)

```


## Merge daily count dataframes, for the percent change version 
```{r}
colnames(EMA_Baseline_Covariates_Distinct)<-c("pid","day_baseline","day_in_study","daily_average_crave_baseline","daily_cigs_baseline","daily_stress_baseline","age","gender","etnicity","race","intervention_complete","cond","FTND_score_baseline","platformType","phase")

colnames(EMA_Intervention_Covariates_Distinct)<-c("pid","day_intervention","day_in_study","daily_average_crave_intervention","daily_cigs_intervention","daily_stress_intervention","age","gender","etnicity","race","intervention_complete","cond","FTND_score_intervention","platformType","phase")

data_daily_comb<-merge(EMA_Baseline_Covariates_Distinct, EMA_Intervention_Covariates_Distinct, by=c('pid'))
```

## Winsorize merged data
```{r}
EMA_Baseline_Covariates_Distinct = winsorize_variables(EMA_Baseline_Covariates_Distinct, 
                               c("daily_average_crave_baseline",
                                 "daily_cigs_baseline",
                                 "daily_stress_baseline"))

EMA_Intervention_Covariates_Distinct = winsorize_variables(EMA_Intervention_Covariates_Distinct, 
                              c("daily_average_crave_intervention",
                                 "daily_cigs_intervention",
                                 "daily_stress_intervention"))
```

## Create average smoking and craving variables (baseline, intervention) for each person - wide 
```{r}
baseline_means <- aggregate(list(baseline_crave=EMA_Baseline_Covariates_Distinct$daily_average_crave_baseline, baseline_cigs=EMA_Baseline_Covariates_Distinct$daily_cigs_baseline, baseline_FTND=EMA_Baseline_Covariates_Distinct$FTND_score_baseline,baseline_stress=EMA_Baseline_Covariates_Distinct$daily_stress_baseline), by = list(pid=EMA_Baseline_Covariates_Distinct$pid), mean, na.rm=TRUE)

intervention_means <- aggregate(list(intervention_crave=EMA_Intervention_Covariates_Distinct$daily_average_crave_intervention, intervention_cigs=EMA_Intervention_Covariates_Distinct$daily_cigs_intervention, intervention_FTND=EMA_Intervention_Covariates_Distinct$FTND_score_intervention, intervention_stress=EMA_Intervention_Covariates_Distinct$daily_stress_intervention,intervention_cond=EMA_Intervention_Covariates_Distinct$cond), by = list(pid=EMA_Intervention_Covariates_Distinct$pid), mean, na.rm=TRUE)

data_averages_comb <- merge(baseline_means,intervention_means,by=c('pid'))

```

## Create average smoking and craving variables (baseline, intervention) for each person - long 
```{r}
baseline_means <- aggregate(list(crave=EMA_Baseline_Covariates_Distinct$daily_average_crave_baseline, cigs=EMA_Baseline_Covariates_Distinct$daily_cigs_baseline, FTND=EMA_Baseline_Covariates_Distinct$FTND_score_baseline, stress=EMA_Baseline_Covariates_Distinct$daily_stress_baseline,cond=EMA_Baseline_Covariates_Distinct$cond), by = list(pid=EMA_Baseline_Covariates_Distinct$pid), mean, na.rm=TRUE)
baseline_means$phase<-"baseline"

intervention_means <- aggregate(list(crave=EMA_Intervention_Covariates_Distinct$daily_average_crave_intervention, cigs=EMA_Intervention_Covariates_Distinct$daily_cigs_intervention, FTND=EMA_Intervention_Covariates_Distinct$FTND_score_intervention, stress=EMA_Intervention_Covariates_Distinct$daily_stress_intervention,cond=EMA_Intervention_Covariates_Distinct$cond), by = list(pid=EMA_Intervention_Covariates_Distinct$pid), mean, na.rm=TRUE)
intervention_means$phase<-"intervention"

data_averages_long <- rbind(baseline_means,intervention_means)

condition_averages <- aggregate(list(crave=data_averages_long$crave, cigs=data_averages_long$crave, stress=data_averages_long$stress), by=list(cond=data_averages_long$cond), mean, na.rm=TRUE)

condition_sds <- aggregate(list(crave=data_averages_long$crave, cigs=data_averages_long$crave, stress=data_averages_long$stress), by=list(cond=data_averages_long$cond), sd, na.rm=TRUE) 
```

## Merge mobility variables
```{r}
#add phase column with different capitalization to match data_averages_long
Mobility_Distinct$phase<-ifelse(Mobility_Distinct$type=="Baseline","baseline","intervention")
#merge EMA and mobility data
allvars <- merge(data_averages_long, Mobility_Distinct,by=c("pid","phase"))

```


## Look at aggregate comparisons, including only those who completed the intervention
```{r}
EMA_Intervention_Covariates_Distinct_complete <- EMA_Intervention_Covariates_Distinct[which(EMA_Intervention_Covariates_Distinct$intervention_complete==1),]

completelist<-data.frame(unique(EMA_Intervention_Covariates_Distinct_complete$pid))
colnames(completelist)<-c("pid")

allvars_complete<-merge(allvars,completelist,by=c("pid"))
```


```{r}
condition_averages <- aggregate(list(crave=allvars$crave, cigs=allvars$cigs, stress=allvars$stress,loc=allvars$uniqueLocations,home=allvars$timeSpentAtHome,travel=allvars$travelTime,entropy=allvars$entropy,places=allvars$placesVisited), by=list(cond=allvars$cond,phase=allvars$phase), mean, na.rm=TRUE)

condition_sds <- aggregate(list(crave=allvars$crave, cigs=allvars$cigs, stress=allvars$stress,loc=allvars$uniqueLocations,home=allvars$timeSpentAtHome,travel=allvars$travelTime,entropy=allvars$entropy,places=allvars$placesVisited), by=list(cond=allvars$cond,phase=allvars$phase), sd, na.rm=TRUE)


complete_condition_averages <- aggregate(list(crave=allvars_complete$crave, cigs=allvars_complete$cigs, stress=allvars_complete$stress,loc=allvars_complete$uniqueLocations,home=allvars_complete$timeSpentAtHome,travel=allvars_complete$travelTime,entropy=allvars_complete$entropy,places=allvars_complete$placesVisited), by=list(cond=allvars_complete$cond,phase=allvars_complete$phase), mean, na.rm=TRUE)

complete_condition_sds <- aggregate(list(crave=allvars_complete$crave, cigs=allvars_complete$cigs, stress=allvars_complete$stress,loc=allvars_complete$uniqueLocations,home=allvars_complete$timeSpentAtHome,travel=allvars_complete$travelTime,entropy=allvars_complete$entropy,places=allvars_complete$placesVisited), by=list(cond=allvars_complete$cond,phase=allvars_complete$phase), sd, na.rm=TRUE)

```

## Test change 
[look at Aim 3 models Ben wrote for a regression base, and code for plots]

## Reshape long to wide for change scores 
```{r}
allvars_complete_wide<- reshape(allvars_complete,idvar=c("pid"),timevar=c("phase"),direction="wide")

```



## Change variables
```{r}
allvars_complete_wide$change_cigs <- (allvars_complete_wide$cigs.baseline - allvars_complete_wide$cigs.intervention) / allvars_complete_wide$cigs.baseline

allvars_complete_wide$change_crave <- (allvars_complete_wide$crave.baseline - allvars_complete_wide$crave.intervention) / allvars_complete_wide$crave.baseline

allvars_complete_wide$change_stress <- (allvars_complete_wide$stress.baseline - allvars_complete_wide$stress.intervention) / allvars_complete_wide$stress.baseline

allvars_complete_wide$change_uniqueLoc <- (allvars_complete_wide$uniqueLocations.baseline - allvars_complete_wide$uniqueLocations.intervention) / allvars_complete_wide$uniqueLocations.baseline

allvars_complete_wide$change_timeHome <- (allvars_complete_wide$timeSpentAtHome.baseline - allvars_complete_wide$timeSpentAtHome.intervention) / allvars_complete_wide$timeSpentAtHome.baseline

allvars_complete_wide$change_entropy <- (allvars_complete_wide$entropy.baseline - allvars_complete_wide$entropy.intervention) / allvars_complete_wide$entropy.baseline

allvars_complete_wide$change_placesVisited <- (allvars_complete_wide$placesVisited.baseline - allvars_complete_wide$placesVisited.intervention) / allvars_complete_wide$placesVisited.baseline
```

## Change variable correlations
```{r}
cor.test(allvars_complete_wide$change_cigs, allvars_complete_wide$change_stress, na.rm=TRUE)
cor.test(allvars_complete_wide$change_cigs, allvars_complete_wide$change_uniqueLoc, na.rm=TRUE)
cor.test(allvars_complete_wide$change_cigs, allvars_complete_wide$change_timeHome, na.rm=TRUE)
cor.test(allvars_complete_wide$change_cigs, allvars_complete_wide$change_entropy, na.rm=TRUE)
cor.test(allvars_complete_wide$change_cigs, allvars_complete_wide$change_placesVisited, na.rm=TRUE)

cor.test(allvars_complete_wide$change_crave, allvars_complete_wide$change_stress, na.rm=TRUE)
cor.test(allvars_complete_wide$change_crave, allvars_complete_wide$change_uniqueLoc, na.rm=TRUE)
cor.test(allvars_complete_wide$change_crave, allvars_complete_wide$change_timeHome, na.rm=TRUE)
cor.test(allvars_complete_wide$change_crave, allvars_complete_wide$change_entropy, na.rm=TRUE)
cor.test(allvars_complete_wide$change_crave, allvars_complete_wide$change_placesVisited, na.rm=TRUE)

```

# Winsorize
```{r}
allvars_complete_wide_wins <- allvars_complete_wide %>%
    mutate(
        crave_baseline_winsorized = Winsorize(crave.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        crave_intervention_winsorized = Winsorize(crave.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        cigs_baseline_winsorized = Winsorize(cigs.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        cigs_intervention_winsorized = Winsorize(cigs.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        stress_baseline_winsorized = Winsorize(stress.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        stress_intervention_winsorized = Winsorize(stress.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        uniqueLocations_intervention_winsorized = Winsorize(uniqueLocations.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        uniqueLocations_baseline_winsorized = Winsorize(uniqueLocations.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        entropy_baseline_winsorized = Winsorize(entropy.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        entropy_intervention_winsorized = Winsorize(entropy.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        timeHome_intervention_winsorized = Winsorize(timeSpentAtHome.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        timeHome_baseline_winsorized = Winsorize(timeSpentAtHome.baseline, probs = c(0.05, 0.95), na.rm = TRUE),
        places_intervention_winsorized = Winsorize(placesVisited.intervention, probs = c(0.05, 0.95), na.rm = TRUE),
        places_baseline_winsorized = Winsorize(placesVisited.baseline, probs = c(0.05, 0.95), na.rm = TRUE)
    ) 
```




## Change variables winsorized
```{r}
allvars_complete_wide_wins$cond <- factor(allvars_complete_wide_wins$cond.intervention)
allvars_complete_wide_wins$condR <- relevel(allvars_complete_wide_wins$cond, ref = 2)

allvars_complete_wide_wins$change_cigs <- (allvars_complete_wide_wins$cigs_baseline_winsorized - allvars_complete_wide_wins$cigs_intervention_winsorized) / allvars_complete_wide_wins$cigs_baseline_winsorized

allvars_complete_wide_wins$change_crave <- (allvars_complete_wide_wins$crave_baseline_winsorized - allvars_complete_wide_wins$crave_intervention_winsorized) / allvars_complete_wide_wins$crave_baseline_winsorized

allvars_complete_wide_wins$change_stress <- (allvars_complete_wide_wins$stress_baseline_winsorized - allvars_complete_wide_wins$stress_intervention_winsorized) / allvars_complete_wide_wins$stress_baseline_winsorized

allvars_complete_wide_wins$change_uniqueLoc <- (allvars_complete_wide_wins$uniqueLocations_baseline_winsorized - allvars_complete_wide_wins$uniqueLocations_intervention_winsorized) / allvars_complete_wide_wins$uniqueLocations_baseline_winsorized

allvars_complete_wide_wins$change_timeHome <- (allvars_complete_wide_wins$timeHome_baseline_winsorized - allvars_complete_wide_wins$timeHome_intervention_winsorized) / allvars_complete_wide_wins$timeHome_baseline_winsorized

allvars_complete_wide_wins$change_entropy <- (allvars_complete_wide_wins$entropy_baseline_winsorized - allvars_complete_wide_wins$entropy_intervention_winsorized) / allvars_complete_wide_wins$entropy_baseline_winsorized

allvars_complete_wide_wins$change_placesVisited <- (allvars_complete_wide_wins$places_baseline_winsorized - allvars_complete_wide_wins$places_intervention_winsorized) / allvars_complete_wide_wins$places_baseline_winsorized
```

## Change variable winsorized correlations
```{r}
cor.test(allvars_complete_wide_wins$change_cigs, allvars_complete_wide_wins$change_stress, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs, allvars_complete_wide_wins$change_uniqueLoc, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs, allvars_complete_wide_wins$change_timeHome, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs, allvars_complete_wide_wins$change_entropy, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs, allvars_complete_wide_wins$change_placesVisited, na.rm=TRUE)

cor.test(allvars_complete_wide_wins$change_crave, allvars_complete_wide_wins$change_stress, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave, allvars_complete_wide_wins$change_uniqueLoc, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave, allvars_complete_wide_wins$change_timeHome, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave, allvars_complete_wide_wins$change_entropy, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave, allvars_complete_wide_wins$change_placesVisited, na.rm=TRUE)

```


# Winsorize change variables 
```{r}
allvars_complete_wide_wins <- allvars_complete_wide_wins %>%
    mutate(
        change_cigs_winsorized = Winsorize(change_cigs, probs = c(0.05, 0.95), na.rm = TRUE),
        change_crave_winsorized = Winsorize(change_crave, probs = c(0.05, 0.95), na.rm = TRUE),
        change_stress_winsorized = Winsorize(change_stress, probs = c(0.05, 0.95), na.rm = TRUE),
        change_uniqueLoc_winsorized = Winsorize(change_uniqueLoc, probs = c(0.05, 0.95), na.rm = TRUE),
        change_timeHome_winsorized = Winsorize(change_timeHome, probs = c(0.05, 0.95), na.rm = TRUE),
        change_entropy_winsorized = Winsorize(change_entropy, probs = c(0.05, 0.95), na.rm = TRUE),
        change_placesVisited_winsorized = Winsorize(change_placesVisited, probs = c(0.05, 0.95), na.rm = TRUE)
    ) 
```



## Change variable winsorized correlations
```{r}
cor.test(allvars_complete_wide_wins$change_cigs_winsorized, allvars_complete_wide_wins$change_stress_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs_winsorized, allvars_complete_wide_wins$change_uniqueLoc_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs_winsorized, allvars_complete_wide_wins$change_timeHome_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs_winsorized, allvars_complete_wide_wins$change_entropy_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_cigs_winsorized, allvars_complete_wide_wins$change_placesVisited_winsorized, na.rm=TRUE)

cor.test(allvars_complete_wide_wins$change_crave_winsorized, allvars_complete_wide_wins$change_stress_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave_winsorized, allvars_complete_wide_wins$change_uniqueLoc_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave_winsorized, allvars_complete_wide_wins$change_timeHome_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave_winsorized, allvars_complete_wide_wins$change_entropy_winsorized, na.rm=TRUE)
cor.test(allvars_complete_wide_wins$change_crave_winsorized, allvars_complete_wide_wins$change_placesVisited_winsorized, na.rm=TRUE)

```
## Change variable winsorized correlations
```{r}
summary(lm(change_cigs_winsorized ~ change_stress_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_cigs_winsorized ~ change_uniqueLoc_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_cigs_winsorized ~ change_timeHome_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_cigs_winsorized ~ change_entropy_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_cigs_winsorized ~ change_placesVisited_winsorized * as.factor(condR), data=allvars_complete_wide_wins))

summary(lm(change_crave_winsorized ~ change_stress_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_crave_winsorized ~ change_uniqueLoc_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_crave_winsorized ~ change_timeHome_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_crave_winsorized ~ change_entropy_winsorized * as.factor(condR), data=allvars_complete_wide_wins))
summary(lm(change_crave_winsorized ~ change_placesVisited_winsorized * as.factor(condR), data=allvars_complete_wide_wins))

```








#### Does mobility change from baseline to intervention?
is there a larger mobility change in the experimental groups than in the control group;Does mo is there a difference in mobility change in the CVS vs 7-Eleven groups 
```{r}
summary(lm(allvars_complete$crave ~ as.factor(allvars_complete$cond), data=allvars_complete))

```


#### regressions predicting smoking / craving from mobility interaction with time period? 
#### ^^ this wouldn't account for experimental condition 
```{r}

```
#### regression predicting % CHANGE in smoking / craving from % CHANGE in mobility, interacting with experimental group assignment? 
```{r}

```


## Plot stress

```{r, echo=FALSE}

ggplot(avg_stress_baseline, aes(x = cond, y = avg_value, fill = cond)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = avg_value - se_value, ymax = avg_value + se_value), width = 0.2) +
  scale_fill_manual(values = palette_condition) +
  labs(title = "Average Daily Stress",
       x = "Condition",
       y = "Average Daily Stress") +
  plot_aes
```

