---
title: "Aim 1 Analysis"
author: "Ben Muzekari"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # Show code by default
  message = FALSE,  # Suppress messages by default
  warning = FALSE   # Suppress warnings by default
)
```

# Setup {.tabset}
## Set scripts directory
```{r, echo=FALSE}
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

## Load analysis functions
```{r}
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis2.r"))
```

## Load EMA, and covariate data
```{r}
EMA_Baseline_Covariates_Distinct = load_ema_with_covs(Type="Baseline",
                                                      ema_variables = c("Responded","Session Name", "Notification Time", "Response_Time", "day", "crave", "daily_average_crave", "daily_cigs", "daily_stress", "cvg_1", "cvg_2", "cigs", "neg", "pos"),
                        redcap_variables = c("pid","age","gender","ethnicity","race")) %>%
  add_survey_measure("FTND", session=1) %>%
  add_descriptives(vars="platformType") %>%
  distinct()
```

## Hour-level data
Run cell below to create the within-day hour-level data:
```{r}
# geo_baseline_1000ft_100ft_exposures = load_geodata_within_day_exposures("Baseline","1000ft")
# 
# df = create_ema_var_to_geodata(ema=EMA_Baseline_Covariates_Distinct,
#                           geodata=geo_baseline_1000ft_100ft_exposures, t=1, unit="hours")
```

Run cell below to load the within-day hour-level data:
```{r}
within_day_hour_df = merge_ema_with_geo_exposures(EMA_Baseline_Covariates_Distinct, type="baseline", buffer = "1000ft", t=1,unit="hours") %>%
  arrange(pid, day, Response_Time)
```
### Clean and process data further
```{r}
# remove duplicates
within_day_hour_df <- within_day_hour_df %>% distinct(pid, day, Response_Time, .keep_all = TRUE)

# remove participants with no geo data (i.e. values in before_prompt_exposures_1000ft_100ft that are NA)
within_day_hour_df <- within_day_hour_df %>%
  filter(!is.na(before_prompt_exposures_1000ft_100ft))

# calculate time since start
within_day_hour_df <- within_day_hour_df %>%
  mutate(
    start_time_static = case_when(
      `Session Name` == "Summary_1" ~ as_hms(format(as.POSIXct(`Notification Time`) - hours(5), "%H:%M:%S")), # select first coverage survey and subtract 5 hours to obtain static start time
      TRUE ~ as_hms(NA) 
    )
  ) %>%
  group_by(pid) %>%
  fill(start_time_static, .direction = "downup") %>%
  ungroup()

# compute time since start
within_day_hour_df <- within_day_hour_df %>% # clean time since start
  mutate(
    response_time_hms = as_hms(format(Response_Time, "%H:%M:%S")),  # convert response time to hms format
    time_since_start_static = as.numeric(if_else(
      response_time_hms < start_time_static,  # if response time is before the start time (i.e. responses that occur after midnight)
      response_time_hms + 86400 - start_time_static,  # add 24 hours (i.e. 86400 seconds) before subtracting to ensure there are no negative time since start values
      response_time_hms - start_time_static  # if response time is not before start time, just subtract
    )) / 60  # convert seconds to minutes
  ) 

# df excluding outlier
within_day_hour_df_no_outlier <- within_day_hour_df %>%
  filter(!(pid %in% c("GR293")))
  
# filter, winsorize, and split (no outlier)
within_day_hour_df_no_outlier <- within_day_hour_df_no_outlier %>%
  filter(`Session Name` == "Check-Ins") %>% # filter to only 'Check-Ins'
  # convert values to numeric
  mutate(crave = as.numeric(crave), 
         hour_cigs = as.numeric(cigs
            )) %>%
  # winsorize variables
  winsorize_variables(c(
    "before_prompt_exposures_1000ft_100ft",
    "after_prompt_exposures_1000ft_100ft",
    "crave",
    "hour_cigs"
    )) %>%
  # split variables into within and between
  split_within_between(c(
    "crave_wins",
    "hour_cigs_wins",
    "before_prompt_exposures_1000ft_100ft_wins",
    "after_prompt_exposures_1000ft_100ft_wins"
  )) %>% 
  ungroup()

# filter, winsorize, and split
within_day_hour_df <- within_day_hour_df %>%
  filter(`Session Name` == "Check-Ins") %>% # filter to only 'Check-Ins'
  # convert values to numeric
  mutate(crave = as.numeric(crave), 
         hour_cigs = as.numeric(cigs
            )) %>%
  # winsorize variables
  winsorize_variables(c(
    "before_prompt_exposures_1000ft_100ft",
    "after_prompt_exposures_1000ft_100ft",
    "crave",
    "hour_cigs"
    )) %>%
  # split variables into within and between
  split_within_between(c(
    "crave_wins",
    "hour_cigs_wins",
    "before_prompt_exposures_1000ft_100ft_wins",
    "after_prompt_exposures_1000ft_100ft_wins"
  )) %>% 
  ungroup()
```

### Plot static start times
```{r}
# convert to minutes since midnight
within_day_hour_df <- within_day_hour_df %>%
  mutate(start_time_static_numeric = hour(start_time_static) * 60 + minute(start_time_static) + second(start_time_static) / 60)

within_day_hour_df_no_outlier <- within_day_hour_df_no_outlier %>%
  mutate(start_time_static_numeric = hour(start_time_static) * 60 + minute(start_time_static) + second(start_time_static) / 60)

# plot histogram
ggplot(within_day_hour_df, aes(x = start_time_static_numeric)) +
  geom_histogram(binwidth = 30, fill = "blue", color = "black") + 
  labs(title = "Distribution of start Times",
       x = "Start Time",
       y = "Count") +
  scale_x_continuous(breaks = seq(0, 1440, by = 120), labels = function(x) sprintf("%02d:%02d", x %/% 60, x %% 60)) +
  theme_minimal()
```

## create time since start static quadratic and cubic
```{r}
within_day_hour_df$time_since_start_static_quadratic <- within_day_hour_df$time_since_start_static^2
within_day_hour_df$time_since_start_static_cubic <- within_day_hour_df$time_since_start_static^3

within_day_hour_df_no_outlier$time_since_start_static_quadratic <- within_day_hour_df_no_outlier$time_since_start_static^2
within_day_hour_df_no_outlier$time_since_start_static_cubic <- within_day_hour_df_no_outlier$time_since_start_static^3
```

## Define models
```{r}
exposure_before_model_1000ft_wins <- create_model_function_lme(
  model = "before_prompt_exposures_1000ft_100ft_wins_wn + before_prompt_exposures_1000ft_100ft_wins_bw + day",
  random_effects = ~ before_prompt_exposures_1000ft_100ft_wins_wn | pid,
  correlation = NULL,
  method = "REML"
)

exposure_after_model_craving_wins <- create_model_function_lme(
  model = "crave_wins_wn + crave_wins_bw + day",
  random_effects = ~ crave_wins_wn | pid,
  correlation = NULL,
  method = "REML"
)

exposure_after_model_cigs_wins <- create_model_function_lme(
  model = "hour_cigs_wins_wn + hour_cigs_wins_bw + day",
  random_effects = ~ hour_cigs_wins_wn | pid,
  correlation = NULL,
  method = "REML"
)
```

### crave ~ before prompt 1000ft (linear, quadratic, cubic)
```{r}
lme_craving_1000ft_100ft_linear_quadratic_cubic =
  exposure_before_model_1000ft_wins(
    within_day_hour_df,
    dv= "crave_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_craving_1000ft_100ft_linear_quadratic_cubic)
get_lme_stats(lme_craving_1000ft_100ft_linear_quadratic_cubic)
intervals(lme_craving_1000ft_100ft_linear_quadratic_cubic, which = "fixed")
```

### crave ~ before prompt 1000ft (controlling for cigs)
```{r}
lme_craving_1000ft_100ft_linear_quadratic_cubic_cigs_control =
    exposure_before_model_1000ft_wins(
        within_day_hour_df,
        dv = "crave_wins",
        covs = c("time_since_start_static","time_since_start_static_quadratic", 
                 "time_since_start_static_cubic", "hour_cigs_wins_wn"))

summary(lme_craving_1000ft_100ft_linear_quadratic_cubic_cigs_control)
get_lme_stats(lme_craving_1000ft_100ft_linear_quadratic_cubic_cigs_control)
intervals(lme_craving_1000ft_100ft_linear_quadratic_cubic_cigs_control, which = "fixed")
```

### crave ~ before prompt 1000ft (no_time_since_start_static)
```{r}
lme_craving_1000ft_100ft_no_time_since_start_static =
  exposure_before_model_1000ft_wins(
    within_day_hour_df,
    dv= "crave_wins")

summary(lme_craving_1000ft_100ft_no_time_since_start_static)
get_lme_stats(lme_craving_1000ft_100ft_no_time_since_start_static)
intervals(lme_craving_1000ft_100ft_no_time_since_start_static, which = "fixed")
```

### crave ~ before prompt 1000ft (no_time_since_start_static; controlling for cigs)
```{r}
lme_craving_1000ft_100ft_no_time_since_start_static_cigs_control =
  exposure_before_model_1000ft_wins(
    within_day_hour_df,
    dv= "crave_wins",
    covs = c("hour_cigs_wins_wn"))

summary(lme_craving_1000ft_100ft_no_time_since_start_static_cigs_control)
get_lme_stats(lme_craving_1000ft_100ft_no_time_since_start_static_cigs_control)
intervals(lme_craving_1000ft_100ft_no_time_since_start_static_cigs_control)
```

### after prompt 1000ft ~ crave 
```{r}
lme_craving_1000ft_100ft_reverse = 
  exposure_after_model_craving_wins(
    within_day_hour_df, 
    dv= "after_prompt_exposures_1000ft_100ft_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_craving_1000ft_100ft_reverse)
get_lme_stats(lme_craving_1000ft_100ft_reverse)
intervals(lme_craving_1000ft_100ft_reverse)
```

### after prompt 1000ft ~ crave (no_time_since_start_static)
```{r}
lme_craving_1000ft_100ft_reverse_no_time_since_start_static = 
  exposure_after_model_craving_wins(
    within_day_hour_df, 
    dv= "after_prompt_exposures_1000ft_100ft_wins")

summary(lme_craving_1000ft_100ft_reverse_no_time_since_start_static)
get_lme_stats(lme_craving_1000ft_100ft_reverse_no_time_since_start_static)
intervals(lme_craving_1000ft_100ft_reverse_no_time_since_start_static)
```

### cigs ~ before prompt 1000ft
```{r}
lme_cigs_1000ft_100ft_linear_quadratic_cubic = 
  exposure_before_model_1000ft_wins(
    within_day_hour_df, 
    dv= "hour_cigs_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_1000ft_100ft_linear_quadratic_cubic)
get_lme_stats(lme_cigs_1000ft_100ft_linear_quadratic_cubic)
intervals(lme_cigs_1000ft_100ft_linear_quadratic_cubic)
```
### cigs ~ before prompt 1000ft (no outlier)
```{r}
lme_cigs_1000ft_100ft_linear_quadratic_cubic_no_outlier = 
  exposure_before_model_1000ft_wins(
    within_day_hour_df_no_outlier, 
    dv= "hour_cigs_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_1000ft_100ft_linear_quadratic_cubic_no_outlier)
get_lme_stats(lme_cigs_1000ft_100ft_linear_quadratic_cubic_no_outlier)
intervals(lme_cigs_1000ft_100ft_linear_quadratic_cubic_no_outlier)
```


### cigs ~ before prompt 1000ft (no_time_since_start_static)
```{r}
lme_cigs_1000ft_100ft_no_time_since_start_static = 
  exposure_before_model_1000ft_wins(
    within_day_hour_df, 
    dv= "hour_cigs_wins")

summary(lme_cigs_1000ft_100ft_no_time_since_start_static)
get_lme_stats(lme_cigs_1000ft_100ft_no_time_since_start_static)
intervals(lme_cigs_1000ft_100ft_no_time_since_start_static)
```

### after prompt 1000ft ~ cigs
```{r}
lme_cigs_1000ft_100ft_reverse = 
  exposure_after_model_cigs_wins(
    within_day_hour_df, 
    dv= "after_prompt_exposures_1000ft_100ft_wins",
    covs=c("time_since_start_static", "time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_1000ft_100ft_reverse)
get_lme_stats(lme_cigs_1000ft_100ft_reverse)
intervals(lme_cigs_1000ft_100ft_reverse)
```

### after prompt 1000ft ~ cigs (no_time_since_start_static)
```{r}
lme_cigs_1000ft_100ft_reverse_no_time_since_start_static = 
  exposure_after_model_cigs_wins(
    within_day_hour_df, 
    dv= "after_prompt_exposures_1000ft_100ft_wins")

summary(lme_cigs_1000ft_100ft_reverse_no_time_since_start_static)
get_lme_stats(lme_cigs_1000ft_100ft_reverse_no_time_since_start_static)
intervals(lme_cigs_1000ft_100ft_reverse_no_time_since_start_static)
```

### crave ~ cigs 
```{r}
lme_cigs_craving = 
  exposure_after_model_cigs_wins(
    within_day_hour_df, 
    dv= "crave_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_craving)
get_lme_stats(lme_cigs_craving)
intervals(lme_cigs_craving)
```

### crave ~ cigs (no_time_since_start_static)
```{r}
lme_cigs_craving_no_time_since_start_static = 
  exposure_after_model_cigs_wins(
    within_day_hour_df, 
    dv= "crave_wins")

summary(lme_cigs_craving_no_time_since_start_static)
get_lme_stats(lme_cigs_craving_no_time_since_start_static)
intervals(lme_cigs_craving_no_time_since_start_static, which = "fixed")
```

## 2-1 hour lag
Run cell below to create the within-day hour-level data using a 2 to 1 hour lag assess exposures prior to hourly cigarettes:
```{r}
# df = create_ema_var_to_geodata_2_hours(ema=EMA_Baseline_Covariates_Distinct,
#                           geodata=geo_baseline_1000ft_100ft_exposures, t=1, unit="hours")
```

Run cell below to load the within-day hour-level data using a 2 to 1 hour lag assess exposures prior to hourly cigarettes:
```{r}
within_day_2_hour_lag_df = merge_ema_with_geo_exposures(EMA_Baseline_Covariates_Distinct, type="baseline", buffer = "1000ft", t="2_to_1",unit="hours") %>%
  arrange(pid, day, Response_Time)
```

### Clean and process data further
```{r}
# remove duplicates
within_day_2_hour_lag_df <- within_day_2_hour_lag_df %>% distinct(pid, day, Response_Time, .keep_all = TRUE)

# remove participants with no geo data (i.e. values in before_prompt_exposures_1000ft_100ft that NA)
within_day_2_hour_lag_df <- within_day_2_hour_lag_df %>%
  filter(!is.na(before_prompt_exposures_1000ft_100ft))

# calculate time since start
within_day_2_hour_lag_df <- within_day_2_hour_lag_df %>%
  mutate(
    start_time_static = case_when(
      `Session Name` == "Summary_1" ~ as_hms(format(as.POSIXct(`Notification Time`) - hours(5), "%H:%M:%S")), # select first coverage survey and subtract 5 hours to obtain static start time
      TRUE ~ as_hms(NA) 
    )
  ) %>%
  group_by(pid) %>%
  fill(start_time_static, .direction = "downup") %>%
  ungroup()

# clean time since start
within_day_2_hour_lag_df <- within_day_2_hour_lag_df %>% # clean time since start
  mutate(
    response_time_hms = as_hms(format(Response_Time, "%H:%M:%S")),  # convert response time to hms format
    time_since_start_static = as.numeric(if_else(
      response_time_hms < start_time_static,  # if response time is before the start time (i.e. responses that occur after midnight)
      response_time_hms + 86400 - start_time_static,  # add 24 hours (i.e. 86400 seconds) before subtracting to ensure there are no negative time since start values
      response_time_hms - start_time_static  # if response time is not before start time, just subtract
    )) / 60  # convert seconds to minutes
  ) 

# df excluding outlier
within_day_2_hour_lag_df_no_outlier <- within_day_2_hour_lag_df %>%
  filter(!(pid %in% c("GR293")))
  
# filter, winsorize, and split (no outlier)
within_day_2_hour_lag_df_no_outlier <- within_day_2_hour_lag_df_no_outlier %>%
  filter(`Session Name` == "Check-Ins") %>% # filter to only 'Check-Ins'
  # convert values to numeric
  mutate(crave = as.numeric(crave), 
         hour_cigs = as.numeric(cigs
            )) %>%
  # winsorize variables
  winsorize_variables(c(
    "before_prompt_exposures_1000ft_100ft",
    "after_prompt_exposures_1000ft_100ft",
    "crave",
    "hour_cigs"
    )) %>%
  # split variables into within and between
  split_within_between(c(
    "crave_wins",
    "hour_cigs_wins",
    "before_prompt_exposures_1000ft_100ft_wins",
    "after_prompt_exposures_1000ft_100ft_wins"
  )) %>% 
  ungroup()

# filter, winsorize, and split
within_day_2_hour_lag_df <- within_day_2_hour_lag_df %>%
  filter(`Session Name` == "Check-Ins") %>% # filter to only 'Check-Ins'
  # convert values to numeric
  mutate(crave = as.numeric(crave), 
         hour_cigs = as.numeric(cigs
            )) %>%
  # winsorize variables
  winsorize_variables(c(
    "before_prompt_exposures_1000ft_100ft",
    "after_prompt_exposures_1000ft_100ft",
    "crave",
    "hour_cigs"
    )) %>%
  # split variables into within and between
  split_within_between(c(
    "crave_wins",
    "hour_cigs_wins",
    "before_prompt_exposures_1000ft_100ft_wins",
    "after_prompt_exposures_1000ft_100ft_wins"
  )) %>% 
  ungroup()
```

## create time since start static quadratic and cubic
```{r}
within_day_2_hour_lag_df$time_since_start_static_quadratic <- within_day_2_hour_lag_df$time_since_start_static^2
within_day_2_hour_lag_df$time_since_start_static_cubic <- within_day_2_hour_lag_df$time_since_start_static^3

within_day_2_hour_lag_df_no_outlier$time_since_start_static_quadratic <- within_day_2_hour_lag_df_no_outlier$time_since_start_static^2
within_day_2_hour_lag_df_no_outlier$time_since_start_static_cubic <- within_day_2_hour_lag_df_no_outlier$time_since_start_static^3
```

### cigs ~ before prompt 1000ft (2-1 hours)
```{r}
lme_cigs_2_hour_lag_1000ft_100ft = 
  exposure_before_model_1000ft_wins(
    within_day_2_hour_lag_df, 
    dv= "hour_cigs_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_2_hour_lag_1000ft_100ft)
get_lme_stats(lme_cigs_2_hour_lag_1000ft_100ft)
intervals(lme_cigs_2_hour_lag_1000ft_100ft)
```

### cigs ~ before prompt 1000ft (no outlier)
```{r}
lme_cigs_2_hour_lag_1000ft_100ft_no_outlier = 
  exposure_before_model_1000ft_wins(
    within_day_2_hour_lag_df_no_outlier, 
    dv= "hour_cigs_wins",
    covs=c("time_since_start_static","time_since_start_static_quadratic", "time_since_start_static_cubic"))

summary(lme_cigs_2_hour_lag_1000ft_100ft_no_outlier)
get_lme_stats(lme_cigs_2_hour_lag_1000ft_100ft_no_outlier)
intervals(lme_cigs_2_hour_lag_1000ft_100ft_no_outlier)
```

### cigs ~ before prompt 1000ft (no_time_since_start_static)
```{r}
lme_cigs_2_hour_lag_1000ft_100ft_no_time_since_start_static = 
  exposure_before_model_1000ft_wins(
    within_day_2_hour_lag_df, 
    dv= "hour_cigs_wins")

summary(lme_cigs_2_hour_lag_1000ft_100ft_no_time_since_start_static)
get_lme_stats(lme_cigs_2_hour_lag_1000ft_100ft_no_time_since_start_static)
intervals(lme_cigs_2_hour_lag_1000ft_100ft_no_time_since_start_static)
```

### plots
```{r}
# get fixed effects 
fixed_effects_crave <- fixef(lme_craving_1000ft_100ft_linear_quadratic_cubic)
fixed_effects_cigs <- fixef(lme_cigs_1000ft_100ft_linear_quadratic_cubic)
fixed_effects_cigs_lag <- fixef(lme_cigs_2_hour_lag_1000ft_100ft)

# get random effects (intercepts and slopes)
random_effects_crave <- ranef(lme_craving_1000ft_100ft_linear_quadratic_cubic) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

random_effects_cigs <- ranef(lme_cigs_1000ft_100ft_linear_quadratic_cubic) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

random_effects_cigs_lag <- ranef(lme_cigs_2_hour_lag_1000ft_100ft) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

# compute predictions
within_day_hour_df_crave <- within_day_hour_df %>%
  left_join(random_effects_crave, by = "pid") %>%
  mutate(predicted = (fixed_effects_crave["(Intercept)"] + intercept) +
                     (fixed_effects_crave["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

within_day_hour_df_cigs <- within_day_hour_df %>%
  left_join(random_effects_cigs, by = "pid") %>%
  mutate(predicted = (fixed_effects_cigs["(Intercept)"] + intercept) +
                     (fixed_effects_cigs["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

within_day_2_hour_lag_df_cigs <- within_day_2_hour_lag_df %>%
  left_join(random_effects_cigs_lag, by = "pid") %>%
  mutate(predicted = (fixed_effects_cigs_lag["(Intercept)"] + intercept) +
                     (fixed_effects_cigs_lag["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

# get betas and p-values
get_labels <- function(model, term) {
  s <- summary(model)
  beta <- s$tTable[term, "Value"]
  p <- s$tTable[term, "p-value"]
  
  beta_label <- bquote(italic(b) == .(round(beta, 2)))
  
  # Proper conditional formatting for p-values
  p_label <- if (p < 0.001) {
    bquote(italic(p) < 0.001)
  } else {
    bquote(italic(p) == .(round(p, 2)))
  }
  
  list(beta_label = beta_label, p_label = p_label)
}

labels_crave <- get_labels(lme_craving_1000ft_100ft_linear_quadratic_cubic, "before_prompt_exposures_1000ft_100ft_wins_wn")
labels_cigs  <- get_labels(lme_cigs_1000ft_100ft_linear_quadratic_cubic, "before_prompt_exposures_1000ft_100ft_wins_wn")
labels_lag   <- get_labels(lme_cigs_2_hour_lag_1000ft_100ft, "before_prompt_exposures_1000ft_100ft_wins_wn")

# label positions
x_crave <- max(within_day_hour_df_crave$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_crave <- max(within_day_hour_df_crave$predicted, na.rm = TRUE) * 0.99

x_cigs <- max(within_day_hour_df_cigs$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_cigs <- max(within_day_hour_df_cigs$predicted, na.rm = TRUE) * 0.99

x_lag <- max(within_day_2_hour_lag_df_cigs$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_lag <- max(within_day_2_hour_lag_df_cigs$predicted, na.rm = TRUE) * 0.99

# plot function
make_plot <- function(df, ylab, x, y, beta_label, p_label) {
  ggplot(df, aes(x = before_prompt_exposures_1000ft_100ft_wins_wn, y = predicted)) +
    geom_line(aes(group = pid), color = "gray", alpha = 0.5, size = 0.8) +
    geom_smooth(method = "lm", se = TRUE, color = "maroon", fill = "maroon", size = 1.5, alpha = 0.7) +
    labs(x = "", y = ylab) +
    annotate("text", x = x, y = y, label = beta_label, size = 6, hjust = 1) +
    annotate("text", x = x, y = y * 0.9, label = p_label, size = 6, hjust = 1) +
    theme_minimal() +
    theme(
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 16),
      panel.grid = element_blank(),
      axis.line = element_line(color = "black")
    )
}

# build plots
plot_crave <- make_plot(
  within_day_hour_df_crave,
  "Current craving",
  x_crave,
  y_crave,
  labels_crave$beta_label,
  labels_crave$p_label
) +
  labs(x = "\nLast-hour tobacco retail exposure (within-person)",
       y = "Current craving") +
  theme(axis.title.x = element_text(hjust = -0.100, size = 13))

plot_cigs <- make_plot(
  within_day_hour_df_cigs,
  "Last-hour cigarettes",
  x_cigs,
  y_cigs,
  labels_cigs$beta_label,
  labels_cigs$p_label
) +
  labs(x = NULL, y = "Last-hour cigarettes")

plot_cigs_lag <- make_plot(
  within_day_2_hour_lag_df_cigs,
  "Last-hour cigarettes (2-hour lag)",
  x_lag,
  y_lag,
  labels_lag$beta_label,
  labels_lag$p_label
) +
  labs(x = "  Last-hour (2 hour lag)\ntobacco retail exposure\n       (within-person)",
       y = NULL) +
  theme(axis.title.x = element_text(hjust = 0.1, size = 13))  


# combine plots
final_plot <- wrap_plots(plot_crave, plot_cigs, plot_cigs_lag, ncol = 3) +
  plot_annotation(
    theme = theme(plot.caption = element_text(size = 12, hjust = 0.5))
  )

# show plot
print(final_plot)
```

# check outliers
```{r}
average_within_day_hour_df_pid <- within_day_hour_df %>%
  group_by(pid) %>%
  dplyr::summarize(
    hour_cigs = mean(hour_cigs, na.rm = TRUE),
    crave = mean(crave, na.rm = TRUE)
  )
```

# GR293 outlier z-score (cigs)
```{r}
max_val <- max(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
mean_val <- mean(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
sd_val <- sd(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
z_max <- (max_val - mean_val) / sd_val
z_max
```

# second highest z-score (cigs)
```{r}
sorted_vals <- sort(average_within_day_hour_df_pid$hour_cigs, decreasing = TRUE, na.last = NA)
second_highest <- sorted_vals[2]

mean_val <- mean(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
sd_val <- sd(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
z_second_highest <- (second_highest - mean_val) / sd_val
z_second_highest
```

# lowest (cigs)
```{r}
sorted_vals <- sort(average_within_day_hour_df_pid$hour_cigs, decreasing = TRUE, na.last = NA)
lowest <- sorted_vals[273]

mean_val <- mean(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
sd_val <- sd(average_within_day_hour_df_pid$hour_cigs, na.rm = TRUE)
lowest <- (lowest - mean_val) / sd_val
lowest
```

# max (crave)
```{r}
max_val <- max(average_within_day_hour_df_pid$crave, na.rm = TRUE)
mean_val <- mean(average_within_day_hour_df_pid$crave, na.rm = TRUE)
sd_val <- sd(average_within_day_hour_df_pid$crave, na.rm = TRUE)
z_max <- (max_val - mean_val) / sd_val
z_max
```

# lowest (crave)
```{r}
sorted_vals <- sort(average_within_day_hour_df_pid$crave, decreasing = TRUE, na.last = NA)
lowest <- sorted_vals[273]

mean_val <- mean(average_within_day_hour_df_pid$crave, na.rm = TRUE)
sd_val <- sd(average_within_day_hour_df_pid$crave, na.rm = TRUE)
z_lowest <- (lowest - mean_val) / sd_val
z_lowest
```


### plots excluding outlier
```{r}
# get fixed effects 
fixed_effects_crave <- fixef(lme_craving_1000ft_100ft_linear_quadratic_cubic)
fixed_effects_cigs <- fixef(lme_cigs_1000ft_100ft_linear_quadratic_cubic)
fixed_effects_cigs_lag <- fixef(lme_cigs_2_hour_lag_1000ft_100ft)

# get random effects (intercepts and slopes)
random_effects_crave <- ranef(lme_craving_1000ft_100ft_linear_quadratic_cubic) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

random_effects_cigs <- ranef(lme_cigs_1000ft_100ft_linear_quadratic_cubic) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

random_effects_cigs_lag <- ranef(lme_cigs_2_hour_lag_1000ft_100ft) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `before_prompt_exposures_1000ft_100ft_wins_wn`
  )

# compute predictions
within_day_hour_df_crave <- within_day_hour_df %>%
  left_join(random_effects_crave, by = "pid") %>%
  mutate(predicted = (fixed_effects_crave["(Intercept)"] + intercept) +
                     (fixed_effects_crave["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

within_day_hour_df_cigs <- within_day_hour_df %>%
  left_join(random_effects_cigs, by = "pid") %>%
  mutate(predicted = (fixed_effects_cigs["(Intercept)"] + intercept) +
                     (fixed_effects_cigs["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

within_day_2_hour_lag_df_cigs <- within_day_2_hour_lag_df %>%
  left_join(random_effects_cigs_lag, by = "pid") %>%
  mutate(predicted = (fixed_effects_cigs_lag["(Intercept)"] + intercept) +
                     (fixed_effects_cigs_lag["before_prompt_exposures_1000ft_100ft_wins_wn"] + slope) * 
                     before_prompt_exposures_1000ft_100ft_wins_wn)

# get betas and p-values
get_labels <- function(model, term) {
  s <- summary(model)
  beta <- s$tTable[term, "Value"]
  p <- s$tTable[term, "p-value"]
  
  beta_label <- bquote(italic(b) == .(round(beta, 2)))
  
  # Proper conditional formatting for p-values
  p_label <- if (p < 0.001) {
    bquote(italic(p) < 0.001)
  } else {
    bquote(italic(p) == .(round(p, 2)))
  }
  
  list(beta_label = beta_label, p_label = p_label)
}

labels_crave <- get_labels(lme_craving_1000ft_100ft_linear_quadratic_cubic, "before_prompt_exposures_1000ft_100ft_wins_wn")
labels_cigs  <- get_labels(lme_cigs_1000ft_100ft_linear_quadratic_cubic, "before_prompt_exposures_1000ft_100ft_wins_wn")
labels_lag   <- get_labels(lme_cigs_2_hour_lag_1000ft_100ft, "before_prompt_exposures_1000ft_100ft_wins_wn")

# label positions
x_crave <- max(within_day_hour_df_crave$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_crave <- max(within_day_hour_df_crave$predicted, na.rm = TRUE) * 0.99

x_cigs <- max(within_day_hour_df_cigs$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
#y_cigs <- max(within_day_hour_df_cigs$predicted, na.rm = TRUE) * 0.99
y_cigs <- 5

x_lag <- max(within_day_2_hour_lag_df_cigs$before_prompt_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
#y_lag <- max(within_day_2_hour_lag_df_cigs$predicted, na.rm = TRUE) * 0.99
y_lag <- 5

# plot function
make_plot <- function(df, ylab, x, y, beta_label, p_label) {
  ggplot(df, aes(x = before_prompt_exposures_1000ft_100ft_wins_wn, y = predicted)) +
    geom_line(aes(group = pid), color = "gray", alpha = 0.5, size = 0.8) +
    geom_smooth(method = "lm", se = TRUE, color = "maroon", fill = "maroon", size = 1.5, alpha = 0.7) +
    labs(x = "", y = ylab) +
    annotate("text", x = x, y = y, label = beta_label, size = 6, hjust = 1) +
    annotate("text", x = x, y = y * 0.9, label = p_label, size = 6, hjust = 1) +
    theme_minimal() +
    theme(
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 16),
      panel.grid = element_blank(),
      axis.line = element_line(color = "black")
    )
}

# no outlier version
within_day_hour_df_cigs_no_outlier <- within_day_hour_df_cigs %>% filter(pid != "GR293")
within_day_2_hour_lag_df_cigs_no_outlier <- within_day_2_hour_lag_df_cigs %>% filter(pid != "GR293")

# build plots
plot_crave <- make_plot(
  within_day_hour_df_crave,
  "Current craving",
  x_crave,
  y_crave,
  labels_crave$beta_label,
  labels_crave$p_label
) +
  labs(x = "\nLast-hour tobacco retail exposure (within-person)",
       y = "Current craving") +
  theme(axis.title.x = element_text(hjust = -0.100, size = 13))

plot_cigs <- make_plot(
  within_day_hour_df_cigs_no_outlier,
  "Last-hour cigarettes",
  x_cigs,
  y_cigs,
  labels_cigs$beta_label,
  labels_cigs$p_label
) +
  labs(x = NULL, y = "Last-hour cigarettes")

plot_cigs_lag <- make_plot(
  within_day_2_hour_lag_df_cigs_no_outlier,
  "Last-hour cigarettes (2-hour lag)",
  x_lag,
  y_lag,
  labels_lag$beta_label,
  labels_lag$p_label
) +
  labs(x = "  Last-hour (2 hour lag)\ntobacco retail exposure\n       (within-person)",
       y = NULL) +
  theme(axis.title.x = element_text(hjust = 0.1, size = 13))  

# combine plots
final_plot <- wrap_plots(plot_crave, plot_cigs, plot_cigs_lag, ncol = 3) +
  plot_annotation(
    theme = theme(plot.caption = element_text(size = 12, hjust = 0.5))
  )

# show plot
print(final_plot)
```