---
title: "Intervention Analysis"
output: html_document
---

This document contains plots and statistics for the intervention data from the GeoSmoking Study.

The data used in this script is from *"/Volumes/cnlab/GeoRemote/Output/aim_3/all_data.csv"*. This data file was generated via *"/GeoRemote/Scripts/Analysis/aim_3_preprocessing.Rmd"* which serves to preproccess and export the data so it could then imported in this script in ready-to-analyze form.

The subject-by-condition breakdown is the following:

**Intent-to-treat (N = 282)**

Control: 70 Low Exposure: 105 High Exposure: 107

**Subjects with full compliance (N = 167)**

Control: 66
Low Exposure: 57 
High Exposure: 44

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     
  message = FALSE,  
  warning = FALSE   
)
```

```{r, echo=FALSE}
# Set scripts directory
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

```{r}
# Load analysis functions
library(ggplot2) # having trouble loading this is in with the utility scripts, so loading alone
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis2.r"))
```

```{r}
# Read data
itt <-read.csv("/Volumes/cnlab/GeoRemote/Output/aim_3/EMA_geo_combined.csv")
```

```{r}
# I am winsorizng and splitting variables in this script because we will have to do this twice: once for intent-to-treat and once for completers

# Winsorize variables
itt = winsorize_variables(itt, 
                               c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_500ft_100ft",
                                 "daily_exposures_1000ft_100ft"))

# Split variables
itt <- split_within_between(itt,
                                 c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_500ft_100ft",
                                 "daily_exposures_1000ft_100ft"))
```

```{r}
# set factor levels in particular order so they are presented in this order when for analysis
itt$cond <- factor(itt$cond,
                       levels = c("Control", "Low", "High"))
```

```{r}
#print(length(unique(itt$pid)))
#[1] 282
```

```{r}
# itt %>%
#   group_by(cond) %>%
#   summarise(n = n_distinct(pid))
# 1 Control    70
# 2 Low       105
# 3 High      107
```

```{r}
# read the data in again, but this time call it completers
completers <-read.csv("/Volumes/cnlab/GeoRemote/Output/aim_3/EMA_geo_combined.csv")
```

```{r}
# Subset to those who only completed all 20 store visits
completers <- completers[completers$intervention_complete == 1, ]
#print(length(unique(completers$pid)))
#[1] 168

### check NUMBERS ####
```

```{r}
# Winsorize variables
completers = winsorize_variables(completers, 
                               c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_500ft_100ft",
                                 "daily_exposures_1000ft_100ft"))

# Split variables
completers <- split_within_between(completers,
                                 c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_500ft_100ft",
                                 "daily_exposures_1000ft_100ft"))
```

```{r}
# set factor levels in particular order so they are presented in this order when for analysis
completers$cond <- factor(completers$cond,
                       levels = c("Control", "Low", "High"))
```

```{r}
# completers %>%
#   group_by(cond) %>%
#   summarise(n = n_distinct(pid))
# 
# 1 Control    66
# 2 Low        44
# 3 High       57
# 4 NA          1

###### note to deal with NA here ##########
```

```{r}
# create a function to calculate the mean and standard error
calc_mean_se <- function(data, var, group_by_phase = TRUE, pid_col = "pid",
                         output = c("summary", "pid")) {
  output <- match.arg(output)
  v   <- rlang::ensym(var)
  pid <- rlang::sym(pid_col)

  if (group_by_phase) {
    pid_level <- data %>%
      dplyr::group_by(!!pid, phase, cond) %>%
      dplyr::summarise(pid_mean = mean(!!v, na.rm = TRUE), .groups = "drop") %>%
      dplyr::filter(!is.nan(pid_mean))

    summary <- pid_level %>%
      dplyr::group_by(phase, cond) %>%
      dplyr::summarise(
        n_pids = dplyr::n(),
        mean   = mean(pid_mean),
        se     = if (dplyr::n() > 1) stats::sd(pid_mean) / sqrt(dplyr::n()) else NA_real_,
        .groups = "drop"
      )
  } else {
    pid_level <- data %>%
      dplyr::group_by(!!pid, cond) %>%
      dplyr::summarise(pid_mean = mean(!!v, na.rm = TRUE), .groups = "drop") %>%
      dplyr::filter(!is.nan(pid_mean))

    summary <- pid_level %>%
      dplyr::group_by(cond) %>%
      dplyr::summarise(
        n_pids = dplyr::n(),
        mean   = mean(pid_mean),
        se     = if (dplyr::n() > 1) stats::sd(pid_mean) / sqrt(dplyr::n()) else NA_real_,
        .groups = "drop"
      )
  }

  if (output == "pid") pid_level else summary
}
```

```{r}
# Palette for phase comparisons
palette_phase <- c(
  "Baseline"     = "#79C3BC",  
  "Intervention" = "#C37980"   
)

# Palette for condition comparisons
palette_condition <- c(
  "Control" = "#C29B5B",  # deep teal
  "Low"     = "#5BC29B",
  "High"    = "#9B5BC2"   # rust
)
```

# Plots and models of primary outcomes {.tabset}

```{r}
# create dfs that have 2 rows per subject, like we preregistered: https://osf.io/acbje/overview

model_df_itt <- itt %>%
  group_by(pid, phase, cond) %>%
  summarize(
    mean_crave_wins = mean(daily_average_crave_wins, na.rm = TRUE),
    mean_cigs_wins  = mean(daily_cigs_wins, na.rm = TRUE),
    .groups = "drop"
  )

model_df_completers <- completers %>%
  group_by(pid, phase, cond) %>%
  summarize(
    mean_crave_wins = mean(daily_average_crave_wins, na.rm = TRUE),
    mean_cigs_wins  = mean(daily_cigs_wins, na.rm = TRUE),
    .groups = "drop"
  )
```

## Craving {.tabset}

### Intent-to-treat

```{r}
craving_summary_itt <- calc_mean_se(
  itt,
  "daily_average_crave_wins",
  group_by_phase = TRUE,
  output = "summary"
)

ggplot(craving_summary_itt, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Mean daily craving", fill = "Phase",
       title = "Mean daily craving by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
craving_pid_means_itt <- calc_mean_se(itt, daily_average_crave, TRUE, output = "pid")

ggplot(craving_pid_means_itt,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of mean daily craving by condition and phase",
    x = "Mean daily craving",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

# preregistered
craving_lme <- lmer(mean_crave_wins ~ phase * cond + (1|pid), data = model_df_itt)
summary(craving_lme)

# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + (phase|pid), data = itt)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + (1|pid), data = itt)
summary(craving_lme_by_row_no_slope)
```


### Completers

```{r}
craving_summary_completers <- calc_mean_se(completers, "daily_average_crave_wins", group_by_phase = TRUE, output = "summary")

ggplot(craving_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Mean daily craving", fill = "Phase",
       title = "Mean daily craving by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
craving_pid_means_completers <- calc_mean_se(completers, daily_average_crave, TRUE, output = "pid")

ggplot(craving_pid_means_completers,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of mean daily craving by condition and phase",
    x = "Mean daily craving",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

# preregistered
craving_lme <- lmer(mean_crave_wins ~ phase * cond + (1|pid), data = model_df_completers)
summary(craving_lme)

# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)


##### why are there only 167 subjects, but 168 when counting above? ###### CHECK
```

### Completers: covariates

# FTND
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + FTND_score + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + FTND_score + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Age
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + age + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + age + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Gender
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + gender + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + gender + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Ethnicity
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + ethnicity + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + ethnicity + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Race
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + race + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + race + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Stress
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + daily_stress_wins + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + daily_stress_wins + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Negative mood
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + daily_average_neg_wins + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + daily_average_neg_wins + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Positive mood
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + daily_average_pos_wins + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + daily_average_pos_wins + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# Exposure
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + daily_exposures_1000ft_100ft + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + daily_exposures_1000ft_100ft + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

# All covariates
```{r}
# using repeated measures approach
craving_lme_by_row <- lmer(daily_average_crave_wins ~ phase * cond + FTND_score + age + gender + ethnicity + race + daily_stress_wins + daily_average_neg_wins + daily_average_pos_wins + daily_exposures_1000ft_100ft + (phase|pid), data = completers)
summary(craving_lme_by_row)

# using repeated measures approach, no random slope
craving_lme_by_row_no_slope <- lmer(daily_average_crave_wins ~ phase * cond + FTND_score + age + gender + ethnicity + race + daily_stress_wins + daily_average_neg_wins + daily_average_pos_wins + daily_exposures_1000ft_100ft + (1|pid), data = completers)
summary(craving_lme_by_row_no_slope)
```

## Smoking {.tabset}

### Intent-to-treat

```{r}
smoking_summary_itt <- calc_mean_se(itt, "daily_cigs_wins", group_by_phase = TRUE, output = "summary")

ggplot(smoking_summary_itt, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily cigarettes", fill = "Phase",
       title = "Daily cigarettes by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
smoking_pid_means_itt <- calc_mean_se(itt, daily_cigs, TRUE, output = "pid")

ggplot(smoking_pid_means_itt,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily cigarettes by condition and phase",
    x = "Mean daily cigarettes",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

# preregistered
smoking_lme <- lmer(mean_cigs_wins ~ phase * cond + (1|pid), data = model_df_itt)
summary(smoking_lme)

# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + (phase|pid), data = itt)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + (1|pid), data = itt)
summary(smoking_lme_by_row_no_slope)
```

### Completers

```{r}
smoking_summary_completers <- calc_mean_se(completers, "daily_cigs_wins", group_by_phase = TRUE,  output = "summary")

ggplot(smoking_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily cigarettes", fill = "Phase",
       title = "Daily cigarettes by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
smoking_pid_means_completers <- calc_mean_se(completers, daily_cigs, TRUE, output = "pid")

ggplot(smoking_pid_means_completers,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily cigarettes by condition and phase",
    x = "Mean daily cigarettes",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

# preregistered
smoking_lme <- lmer(mean_cigs_wins ~ phase * cond + (1|pid), data = model_df_completers)
summary(smoking_lme)

# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```
### Completers: covariates

# FTND
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + FTND_score + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + FTND_score + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Age
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + age + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + age + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Gender
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + gender + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + gender + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Ethnicity
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + ethnicity + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + ethnicity + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Race
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + race + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + race + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Stress
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + daily_stress_wins + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + daily_stress_wins + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Negative mood
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + daily_average_neg_wins + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + daily_average_neg_wins + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Positive mood
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + daily_average_pos_wins + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + daily_average_pos_wins + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# Exposure
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + daily_exposures_1000ft_100ft + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + daily_exposures_1000ft_100ft + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```

# All covariates
```{r}
# using repeated measures approach
smoking_lme_by_row <- lmer(daily_cigs_wins ~ phase * cond + FTND_score + age + gender + ethnicity + race + daily_stress_wins + daily_average_neg_wins + daily_average_pos_wins + daily_exposures_1000ft_100ft + (phase|pid), data = completers)
summary(smoking_lme_by_row)

# using repeated measures approach, no random slope
smoking_lme_by_row_no_slope <- lmer(daily_cigs_wins ~ phase * cond + FTND_score + age + gender + ethnicity + race + daily_stress_wins + daily_average_neg_wins + daily_average_pos_wins + daily_exposures_1000ft_100ft + (1|pid), data = completers)
summary(smoking_lme_by_row_no_slope)
```


# Test whether variables predict compliance {.tabset}

```{r}
itt_means <- itt %>%
  group_by(pid) %>%
  filter(phase == "Baseline") %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))
```

```{r}
model <- lm(num_receipts ~ FTND_score, data = itt_means)
summary(model)
```

```{r}
itt_means_low <- itt %>%
  group_by(pid) %>%
  filter(cond == "Low") %>%
  filter(phase == "Baseline") %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

model <- lm(num_receipts ~ FTND_score, data = itt_means_low)
summary(model)
```

```{r}
itt_means_high <- itt %>%
  group_by(pid) %>%
  filter(cond == "High") %>%
  filter(phase == "Baseline") %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

model <- lm(num_receipts ~ FTND_score, data = itt_means_high)
summary(model)
```

```{r}
model <- lm(num_receipts ~ daily_cigs_wins, data = itt_means)
summary(model)
```

```{r}
model <- lm(num_receipts ~ daily_average_crave, data = itt_means)
summary(model)
```

```{r}
model <- lm(num_receipts ~ daily_stress_wins, data = itt_means)
summary(model)
```

```{r}
model <- lm(num_receipts ~ daily_average_neg_wins, data = itt_means)
summary(model)
```

```{r}
model <- lm(num_receipts ~ daily_average_pos_wins, data = itt_means)
summary(model)
```

```{r}
model <- lm(num_receipts ~ age, data = itt_means)
summary(model)
```

```{r}
#model <- lm(num_receipts ~ baseline_smoking, data = itt_means)
#summary(model)
```

```{r}
#cor.test(itt_means$baseline_smoking, itt_means$FTND_score)
```



```{r}
model <- lm(num_receipts ~ daily_exposures_1000ft_100ft_wins, data = itt_means)
summary(model)
```




# Plots of additional variables {.tabset}

## FTND

```{r}
ftnd_summary <- calc_mean_se(completers, "FTND_score", group_by_phase = FALSE)

# plot
ggplot(ftnd_summary, aes(x = cond, y = mean, fill = cond)) +
  geom_col(color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
  scale_fill_manual(values = palette_condition) +
  labs(x = "Condition", y = "FTND score",
       title = "Mean FTND score by condition") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Age

```{r}
age_summary <- calc_mean_se(completers, "age", group_by_phase = FALSE)

# plot
ggplot(age_summary, aes(x = cond, y = mean, fill = cond)) +
  geom_col(color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
  scale_fill_manual(values = palette_condition) +
  labs(x = "Condition", y = "Age",
       title = "Mean age by condition") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Exposures 1000 feet (Intent-to-treat)
```{r}
exposures_summary_itt <- calc_mean_se(itt, "daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_itt, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily exposures", fill = "Phase",
       title = "Daily exposures by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
exposures_pid_means_itt <- calc_mean_se(itt, daily_exposures_1000ft_100ft, TRUE, output = "pid")

ggplot(exposures_pid_means_itt,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily exposures by condition and phase",
    x = "Mean daily exposures",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )


# using repeated measures approach
daily_exposures_lme_by_row <- lmer(daily_exposures_1000ft_100ft  ~ phase * cond + (phase|pid), data = itt)
summary(daily_exposures_lme_by_row)

# using repeated measures approach, no random slope
daily_exposures_lme_by_row_no_slope <- lmer(daily_exposures_1000ft_100ft ~ phase * cond + (1|pid), data = itt)
summary(daily_exposures_lme_by_row_no_slope)
```

## Exposures 1000 feet (Intent-to-treat): excluding days where at least one point is outside study areas
```{r}
exposures_summary_itt_exclude_at_least_point_outside_by_day <- itt %>%
  dplyr::filter(at_least_point_outside_by_day == FALSE) %>%
  calc_mean_se("daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_itt_exclude_at_least_point_outside_by_day, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.2,
    position = position_dodge(0.6)
  ) +
  scale_fill_manual(values = palette_phase) +
  labs(
    x = "Condition",
    y = "Daily exposures",
    fill = "Phase",
    title = "Daily exposures by condition and phase"
  ) +
  theme_bw(base_size = 14) +
  theme(
    axis.text = element_text(color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```



## Exposures 1000 feet (Completers)
```{r}
exposures_summary_completers <- calc_mean_se(completers, "daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily exposures", fill = "Phase",
       title = "Daily exposures by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
exposures_pid_means_completers <- calc_mean_se(completers, daily_exposures_500ft_100ft, TRUE, output = "pid")

ggplot(exposures_pid_means_completers,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily exposures by condition and phase",
    x = "Mean daily exposures",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

# using repeated measures approach
daily_exposures_lme_by_row_completers <- lmer(daily_exposures_1000ft_100ft  ~ phase * cond + (phase|pid), data = completers)
summary(daily_exposures_lme_by_row_completers)

# using repeated measures approach, no random slope
daily_exposures_by_row_no_slope_completers <- lmer(daily_exposures_1000ft_100ft ~ phase * cond + (1|pid), data = completers)
summary(daily_exposures_by_row_no_slope_completers)
```

## Exposures 1000 feet (Completers): excluding days where at least one point is outside study areas
```{r}
exposures_summary_completers_exclude_at_least_point_outside_by_day <- completers %>%
  dplyr::filter(at_least_point_outside_by_day == FALSE) %>%
  calc_mean_se("daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers_exclude_at_least_point_outside_by_day, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.2,
    position = position_dodge(0.6)
  ) +
  scale_fill_manual(values = palette_phase) +
  labs(
    x = "Condition",
    y = "Daily exposures",
    fill = "Phase",
    title = "Daily exposures by condition and phase"
  ) +
  theme_bw(base_size = 14) +
  theme(
    axis.text = element_text(color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```

## Exposures 1000 feet (Completers): IOS Users
```{r}
# subset to just IOS users
completers_ios <- completers %>% 
  filter(platformType == "IOS")

exposures_summary_completers_ios <- calc_mean_se(completers_ios, "daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily exposures", fill = "Phase",
       title = "Daily exposures by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
exposures_pid_means_completers_ios <- calc_mean_se(completers_ios, daily_exposures_1000ft_100ft, TRUE, output = "pid")

ggplot(exposures_pid_means_completers_ios,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily exposures by condition and phase",
    x = "Mean daily exposures",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )
```

## Exposures 1000 feet (Completers): IOS Users; excluding days where at least one point is outside study areas
```{r}
exposures_summary_completers_ios_exclude_at_least_point_outside_by_day <- completers_ios %>%
  dplyr::filter(at_least_point_outside_by_day == FALSE) %>%
  calc_mean_se("daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers_ios_exclude_at_least_point_outside_by_day, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.2,
    position = position_dodge(0.6)
  ) +
  scale_fill_manual(values = palette_phase) +
  labs(
    x = "Condition",
    y = "Daily exposures",
    fill = "Phase",
    title = "Daily exposures by condition and phase"
  ) +
  theme_bw(base_size = 14) +
  theme(
    axis.text = element_text(color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```


## Exposures 1000 feet (Completers): Android Users
```{r}
# subset to just IOS users
completers_android <- completers %>% 
  filter(platformType == "ANDROID")

exposures_summary_completers_android <- calc_mean_se(completers_android, "daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily exposures", fill = "Phase",
       title = "Daily exposures by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# plot distributions 
exposures_pid_means_completers_android <- calc_mean_se(completers_android, daily_exposures_1000ft_100ft, TRUE, output = "pid")

ggplot(exposures_pid_means_completers_ios,
       aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of daily exposures by condition and phase",
    x = "Mean daily exposures",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )
```

## Exposures 1000 feet (Completers): Android Users; excluding days where at least one point is outside study areas
```{r}
exposures_summary_completers_android_exclude_at_least_point_outside_by_day <- completers_android %>%
  dplyr::filter(at_least_point_outside_by_day == FALSE) %>%
  calc_mean_se("daily_exposures_1000ft_100ft", group_by_phase = TRUE)

ggplot(exposures_summary_completers_android_exclude_at_least_point_outside_by_day, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(
    aes(ymin = mean - se, ymax = mean + se),
    width = 0.2,
    position = position_dodge(0.6)
  ) +
  scale_fill_manual(values = palette_phase) +
  labs(
    x = "Condition",
    y = "Daily exposures",
    fill = "Phase",
    title = "Daily exposures by condition and phase"
  ) +
  theme_bw(base_size = 14) +
  theme(
    axis.text = element_text(color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
```

## Distance (Completers): all points included
```{r}
distance_all_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included", group_by_phase = TRUE)

ggplot(distance_all_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included
```{r}
distance_all_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included", group_by_phase = TRUE)

ggplot(distance_all_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): all points included
```{r}
distance_all_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included", group_by_phase = TRUE)

ggplot(distance_all_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): all points included under 125 mph
```{r}
distance_all_under_125_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included_under_125_mph", group_by_phase = TRUE)

ggplot(distance_all_under_125_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 125 mph
```{r}
distance_all_under_125_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included_under_125_mph", group_by_phase = TRUE)

ggplot(distance_all_under_125_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): all points included under 125 mph
```{r}
distance_all_under_125_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included_under_125_mph", group_by_phase = TRUE)

ggplot(distance_all_under_125_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): all points included under 100 mph
```{r}
distance_all_under_100_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included_under_100_mph", group_by_phase = TRUE)

ggplot(distance_all_under_100_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 100 mph
```{r}
distance_all_under_100_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included_under_100_mph", group_by_phase = TRUE)

ggplot(distance_all_under_100_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): all points included under 100 mph
```{r}
distance_all_under_100_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included_under_100_mph", group_by_phase = TRUE)

ggplot(distance_all_under_100_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): all points included under 75 mph
```{r}
distance_all_under_75_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included_under_75_mph", group_by_phase = TRUE)

ggplot(distance_all_under_75_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 75 mph
```{r}
distance_all_under_75_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included_under_75_mph", group_by_phase = TRUE)

ggplot(distance_all_under_75_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): all points included under 75 mph
```{r}
distance_all_under_75_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included_under_75_mph", group_by_phase = TRUE)

ggplot(distance_all_under_75_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): all points included under 50 mph
```{r}
distance_all_under_50_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included_under_50_mph", group_by_phase = TRUE)

ggplot(distance_all_under_50_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 50 mph
```{r}
distance_all_under_50_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included_under_50_mph", group_by_phase = TRUE)

ggplot(distance_all_under_50_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 50 mph
```{r}
distance_all_under_50_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included_under_50_mph", group_by_phase = TRUE)

ggplot(distance_all_under_50_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): all points included under 25 mph
```{r}
distance_all_under_25_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_all_points_included_under_25_mph", group_by_phase = TRUE)

ggplot(distance_all_under_25_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): all points included under 25 mph
```{r}
distance_all_under_25_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_all_points_included_under_25_mph", group_by_phase = TRUE)

ggplot(distance_all_under_25_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): all points included under 25 mph
```{r}
distance_all_under_25_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_all_points_included_under_25_mph", group_by_phase = TRUE)

ggplot(distance_all_under_25_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area 
```{r}
distance_only_study_area_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area", group_by_phase = TRUE)

ggplot(distance_only_study_area_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): only points in study area 
```{r}
distance_only_study_area_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area", group_by_phase = TRUE)

ggplot(distance_only_study_area_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area 
```{r}
distance_only_study_area_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area", group_by_phase = TRUE)

ggplot(distance_only_study_area_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area under 125 mph
```{r}
distance_only_study_area_under_125_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area_under_125_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_125_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): only points in study area under 125 mph
```{r}
distance_only_study_area_under_125_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area_under_125_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_125_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area under 125 mph
```{r}
distance_only_study_area_under_125_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area_under_125_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_125_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area under 100 mph
```{r}
distance_only_study_area_under_100_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area_under_100_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_100_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): only points in study area under 100 mph
```{r}
distance_only_study_area_under_100_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area_under_100_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_100_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area under 100 mph
```{r}
distance_only_study_area_under_100_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area_under_100_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_100_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area under 75 mph
```{r}
distance_only_study_area_under_75_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area_under_75_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_75_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): only points in study area under 75 mph
```{r}
distance_only_study_area_under_75_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area_under_75_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_75_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area under 75 mph
```{r}
distance_only_study_area_under_75_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area_under_75_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_75_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area under 50 mph
```{r}
distance_only_study_area_under_50_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area_under_50_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_50_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (IOS Completers): only points in study area under 50 mph
```{r}
distance_only_study_area_under_50_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area_under_50_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_50_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area under 50 mph
```{r}
distance_only_study_area_under_50_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area_under_50_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_50_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Completers): only points in study area under 25 mph
```{r}
distance_only_study_area_under_25_mph_summary_completers <- calc_mean_se(completers, "distance_traveled_day_miles_only_points_in_study_area_under_25_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_25_mph_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# using repeated measures approach
daily_distance_lme_by_row_completers <- lmer(distance_traveled_day_miles_only_points_in_study_area_under_25_mph  ~ phase * cond + (phase|pid), data = completers)
summary(daily_distance_lme_by_row_completers)

daily_distance_lme_by_row_completers_no_random_slope <- lmer(distance_traveled_day_miles_only_points_in_study_area_under_25_mph  ~ phase * cond + (1|pid), data = completers)
summary(daily_distance_lme_by_row_completers_no_random_slope)
```

## Distance (IOS Completers): only points in study area under 25 mph
```{r}
distance_only_study_area_under_25_mph_summary_completers_ios <- calc_mean_se(completers_ios, "distance_traveled_day_miles_only_points_in_study_area_under_25_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_25_mph_summary_completers_ios, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Distance (Android Completers): only points in study area under 25 mph
```{r}
distance_only_study_area_under_25_mph_summary_completers_android <- calc_mean_se(completers_android, "distance_traveled_day_miles_only_points_in_study_area_under_25_mph", group_by_phase = TRUE)

ggplot(distance_only_study_area_under_25_mph_summary_completers_android, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Distance (miles)", fill = "Phase",
       title = "Distance (miles) by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

```{r}
mobility_vars <- c(
  "distance_traveled_day_miles_all_points_included",
  "distance_traveled_day_miles_all_points_included_under_125_mph",
  "distance_traveled_day_miles_all_points_included_under_100_mph",
  "distance_traveled_day_miles_all_points_included_under_75_mph",
  "distance_traveled_day_miles_all_points_included_under_50_mph",
  "distance_traveled_day_miles_all_points_included_under_25_mph",
  "distance_traveled_day_miles_only_points_in_study_area",
  "distance_traveled_day_miles_only_points_in_study_area_under_125_mph",
  "distance_traveled_day_miles_only_points_in_study_area_under_100_mph",
  "distance_traveled_day_miles_only_points_in_study_area_under_75_mph",
  "distance_traveled_day_miles_only_points_in_study_area_under_50_mph",
  "distance_traveled_day_miles_only_points_in_study_area_under_25_mph"
)

change_df <- completers %>%
  group_by(pid, phase) %>%
  summarise(
    mean_cigs    = mean(daily_cigs, na.rm = TRUE),
    mean_crave   = mean(daily_average_crave, na.rm = TRUE),
    across(
      all_of(mobility_vars),
      ~ mean(.x, na.rm = TRUE),
      .names = "mean_{.col}"
    ),
    .groups = "drop"
  )

change_scores <- change_df %>%
  pivot_wider(
    names_from = phase,
    values_from = c(mean_cigs, mean_crave, starts_with("mean_"))
  )

mean_cols <- c(
  "mean_cigs",
  "mean_crave",
  paste0("mean_", mobility_vars)
)

for (v in mean_cols) {
  change_scores[[paste0("delta_", sub("^mean_", "", v))]] <-
    change_scores[[paste0(v, "_Intervention")]] -
    change_scores[[paste0(v, "_Baseline")]]
}
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included,
           y = delta_crave)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included,
           y = delta_crave)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_125_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_125_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_100_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_75_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_50_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_all_points_included_under_25_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area_under_125_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area_under_100_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area_under_75_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```

```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area_under_50_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```


```{r}
ggplot(change_scores,
       aes(x = delta_distance_traveled_day_miles_only_points_in_study_area_under_25_mph,
           y = delta_cigs)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw(base_size = 14)
```


## Replication of Correlational Results
```{r}
# Read data
itt_intervention <-read.csv("/Volumes/cnlab/GeoRemote/Output/aim_3/EMA_geo_combined.csv")

itt_intervention <- itt_intervention %>%
  dplyr::filter(phase == "Intervention")
```

```{r}
# Winsorize variables
itt_intervention = winsorize_variables(itt_intervention, 
                               c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_1000ft_100ft"))

# Split variables
itt_intervention <- split_within_between(itt_intervention,
                                 c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_1000ft_100ft_wins"))
```

```{r}
craving_lme <- lmer(daily_average_crave_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (1|pid), data = itt_intervention)
summary(craving_lme)

craving_lme <- lmer(daily_average_crave_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (daily_exposures_1000ft_100ft_wins_wn|pid), data = itt_intervention)
summary(craving_lme)
```

```{r}
smoking_lme <- lmer(daily_cigs_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (1|pid), data = itt_intervention)
summary(smoking_lme)

smoking_lme <- lmer(daily_cigs_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (daily_exposures_1000ft_100ft_wins_wn|pid), data = itt_intervention)
summary(smoking_lme)
```



```{r}
# Read data
completers_intervention <-read.csv("/Volumes/cnlab/GeoRemote/Output/aim_3/EMA_geo_combined.csv")

completers_intervention <- completers_intervention[completers_intervention$intervention_complete == 1, ]

completers_intervention <- completers_intervention %>%
  dplyr::filter(phase == "Intervention")
```

```{r}
# Winsorize variables
completers_intervention = winsorize_variables(completers_intervention, 
                               c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_1000ft_100ft"))

# Split variables
completers_intervention <- split_within_between(completers_intervention,
                                 c("daily_average_crave",
                                 "daily_cigs", 
                                 "daily_stress",
                                 "daily_average_neg",
                                 "daily_average_pos",
                                 "daily_exposures_1000ft_100ft_wins"))
```

```{r}
craving_lme <- lmer(daily_average_crave_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (1|pid), data = completers_intervention)
summary(craving_lme)

craving_lme <- lmer(daily_average_crave_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (daily_exposures_1000ft_100ft_wins_wn|pid), data = completers_intervention)
summary(craving_lme)
```

```{r}
smoking_lme <- lmer(daily_cigs_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (1|pid), data = completers_intervention)
summary(smoking_lme)

smoking_lme <- lmer(daily_cigs_wins ~ daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day + (daily_exposures_1000ft_100ft_wins_wn|pid), data = completers_intervention)
summary(smoking_lme)
```

## Observations (Intent-to-treat)
```{r}
observations_summary_itt <- calc_mean_se(itt, "n_observations_per_day", group_by_phase = TRUE)

ggplot(observations_summary_itt, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily observations", fill = "Phase",
       title = "Daily observations by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Observations (Completers)
```{r}
observations_summary_completers <- calc_mean_se(completers, "n_observations_per_day", group_by_phase = TRUE)

ggplot(observations_summary_completers, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily observations", fill = "Phase",
       title = "Daily observations by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Stress

```{r}
stress_summary <- calc_mean_se(completers, "daily_stress", group_by_phase = TRUE)

ggplot(stress_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily stress", fill = "Phase",
       title = "Daily stress by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Negative mood

```{r}
neg_mood_summary <- calc_mean_se(completers, "daily_average_neg", group_by_phase = TRUE)

ggplot(neg_mood_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily negative mood", fill = "Phase",
       title = "Daily average negative mood by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Positive mood

```{r}
pos_mood_summary <- calc_mean_se(completers, "daily_average_pos", group_by_phase = TRUE)

# plot
ggplot(pos_mood_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(color = "black", width = 0.6, position = position_dodge(0.6)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Daily positive mood", fill = "Phase",
       title = "Daily average positive mood by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# 1) Summarize: % of each category level within each condition (pid-weighted)
cat_percent_by_cond <- function(data, cat_var,
                                pid_col = "pid",
                                cond_col = "cond",
                                drop_na = TRUE,
                                cond_order = c("Control", "Low", "High")) {
  v   <- rlang::ensym(cat_var)
  pid <- rlang::sym(pid_col)
  cnd <- rlang::sym(cond_col)

  # Collapse to one row per participant (uses first observed value per pid)
  base <- data %>%
    group_by(!!pid) %>%
    summarise(
      !!cnd := dplyr::first(!!cnd),
      !!v   := dplyr::first(!!v),
      .groups = "drop"
    )

  if (drop_na) base <- drop_na(base, !!v, !!cnd)

  # Consistent cond order everywhere
  base[[cond_col]] <- factor(base[[cond_col]], levels = cond_order)

  # Percent within each condition (each pid counts once)
  summary <- base %>%
    count(!!cnd, !!v, name = "n") %>%
    group_by(!!cnd) %>%
    mutate(total = sum(n), percent = 100 * n / total) %>%
    ungroup()

  summary
}

# 2) Plot helper: stacked % bars (or dodged) with labels
plot_cat_percent_by_cond <- function(summary_df, cat_var,
                                     cond_col = "cond",
                                     stacked = TRUE,
                                     plot_title = NULL) {
  v   <- rlang::ensym(cat_var)
  cnd <- rlang::sym(cond_col)

  pos <- if (stacked) "stack" else position_dodge(width = 0.6)

  ggplot(summary_df, aes(x = !!cnd, y = percent, fill = !!v)) +
    geom_col(width = 0.6, color = "black", position = pos) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +
    labs(
      x = "Condition",
      y = "Percent of participants",
      fill = rlang::as_label(v),
      title = plot_title
    ) +
    theme_bw(base_size = 14)
}
```

## Race

```{r}
race_summary <- cat_percent_by_cond(completers, "race")
plot_cat_percent_by_cond(race_summary, "race", stacked = FALSE,
                         plot_title = "Distribution of race by condition")
```

## Ethnicity

```{r}
ethnicity_summary <- cat_percent_by_cond(completers, "ethnicity")
plot_cat_percent_by_cond(ethnicity_summary, "ethnicity", stacked = FALSE,
                         plot_title = "Distribution of ethnicity by condition \n Yes = Latino/Hispanic")
```

## Gender

```{r}
gender_summary <- cat_percent_by_cond(completers, "gender")
plot_cat_percent_by_cond(gender_summary, "gender", stacked = FALSE,
                         plot_title = "Distribution of gender by condition")
```

## OS

```{r}
os_summary <- cat_percent_by_cond(completers, "platformType")
palette_os <- c("IOS" = "#3B9AB2", "ANDROID" = "#EBCC2A")

# plot
plot_cat_percent_by_cond(
  os_summary,
  cat_var = "platformType",
  stacked = FALSE,
  plot_title = "Distribution of operating system by condition"
) +
  scale_fill_manual(values = palette_os)

```

# Temporal patterns of primary outcomes {.tabset}

```{r}
daily_mean_se <- function(data, var,
                          group_by_phase = TRUE,
                          pid_col  = "pid",
                          day_col  = "day",
                          cond_col = "cond") {
  v    <- rlang::ensym(var)
  pid  <- rlang::sym(pid_col)
  day  <- rlang::sym(day_col)
  cond <- rlang::sym(cond_col)

  if (group_by_phase) {
    # 1) participant-level means per day within phase × cond
    pid_day <- data %>%
      dplyr::group_by(!!pid, phase, !!cond, !!day) %>%
      dplyr::summarise(pid_day_mean = mean(!!v, na.rm = TRUE), .groups = "drop_last") %>%
      dplyr::filter(!is.nan(pid_day_mean)) %>%
      dplyr::ungroup()

    # 2) mean & SE across participants for each day × cond × phase
    out <- pid_day %>%
      dplyr::group_by(phase, !!cond, !!day) %>%
      dplyr::summarise(
        n_pids = dplyr::n(),
        mean   = mean(pid_day_mean),
        se     = dplyr::if_else(n_pids > 1, stats::sd(pid_day_mean) / sqrt(n_pids), NA_real_),
        .groups = "drop"
      ) %>%
      dplyr::arrange(phase, !!cond, !!day)

  } else {
    # 1) participant-level means per day within cond only
    pid_day <- data %>%
      dplyr::group_by(!!pid, !!cond, !!day) %>%
      dplyr::summarise(pid_day_mean = mean(!!v, na.rm = TRUE), .groups = "drop_last") %>%
      dplyr::filter(!is.nan(pid_day_mean)) %>%
      dplyr::ungroup()

    # 2) mean & SE across participants for each day × cond
    out <- pid_day %>%
      dplyr::group_by(!!cond, !!day) %>%
      dplyr::summarise(
        n_pids = dplyr::n(),
        mean   = mean(pid_day_mean),
        se     = dplyr::if_else(n_pids > 1, stats::sd(pid_day_mean) / sqrt(n_pids), NA_real_),
        .groups = "drop"
      ) %>%
      dplyr::arrange(!!cond, !!day)
  }

  out
}

plot_daily_mean_se <- function(summary_df,
                               day_col   = "day",
                               cond_col  = "cond",
                               phase_col = "phase",
                               ribbon    = TRUE,
                               point     = TRUE,
                               linewidth = 1,
                               point_size = 2.5,
                               title = NULL,
                               ylab  = NULL,
                               xlab  = "Day",
                               facet_scales = "free_x") { 

  day_sym   <- rlang::sym(day_col)
  cond_sym  <- rlang::sym(cond_col)
  has_phase <- phase_col %in% names(summary_df)
  if (has_phase) phase_sym <- rlang::sym(phase_col)

  p <- ggplot2::ggplot(summary_df,
                       ggplot2::aes(x = !!day_sym, y = mean, color = !!cond_sym, group = !!cond_sym))

  if (ribbon) {
    p <- p + ggplot2::geom_ribbon(
      ggplot2::aes(ymin = mean - se, ymax = mean + se, fill = !!cond_sym),
      alpha = 0.20, linewidth = 0, color = NA
    )
  }

  p <- p + ggplot2::geom_line(linewidth = linewidth)
  if (point) p <- p + ggplot2::geom_point(size = point_size)

  if (has_phase) {
    p <- p + ggplot2::facet_wrap(rlang::as_quosure(phase_sym), ncol = 1, scales = facet_scales)
  }

  p +
    ggplot2::labs(title = title, x = xlab, y = ylab, color = "Condition", fill = "Condition") +
    ggplot2::theme_bw(base_size = 14) +
    ggplot2::scale_x_continuous(
      breaks = seq(
        min(summary_df[[day_col]], na.rm = TRUE),
        max(summary_df[[day_col]], na.rm = TRUE),
        by = 1
      )
    )
}

```

```{r}
# Check day counts for both phases
# completers %>%
#   filter(phase == "Baseline") %>%
#   group_by(pid) %>%
#   summarise(day_count = n_distinct(day)) %>%
#   filter(day_count > 14) %>%
#   pull(pid)
#character(0)

# completers %>%
#   filter(phase == "Intervention") %>%
#   group_by(pid) %>%
#   summarise(day_count = n_distinct(day)) %>%
#   filter(day_count > 28) %>%
#   pull(pid)
#[1] "GR066" "GR236" - there are 2 subjects with more than 28 days

# investigating these data
GR066 <- completers %>%
  filter(pid == "GR066") #29 days, data for all days

GR236 <- completers %>%
  filter(pid == "GR236") #30 days, no data on day 13
```

```{r}
# FOR NOW: removing rows where day count is over 28
itt <- itt %>%
  filter(!(phase == "Intervention" & day > 28))

completers <- completers %>%
  filter(!(phase == "Intervention" & day > 28))
```

## Group level {.tabset}

```{r}
itt <- itt %>%
  mutate(week = ceiling(day / 7))

completers <- completers %>%
  mutate(week = ceiling(day / 7))
```

### Craving: Day-level

```{r, fig.width=10, fig.height=8}
craving_daily <- daily_mean_se(
  data = completers,
  var = daily_average_crave,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  craving_daily,
  title = "Daily craving by condition and phase",
  ylab = "Daily craving"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```
### Craving: Week-level

```{r}
craving_weekly <- daily_mean_se(
  data = completers,
  var  = daily_average_crave,       
  group_by_phase = TRUE,
  pid_col  = "pid",
  day_col  = "week",       
  cond_col = "cond"
)

plot_daily_mean_se(
  summary_df = craving_weekly,
  day_col    = "week",       
  xlab       = "Week",
  ylab = "Daily craving",
  title      = "Daily craving by condition and phase"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```




### Smoking: Day-level

```{r, fig.width=10, fig.height=8}
smoking_daily <- daily_mean_se(
  data = completers,
  var = daily_cigs,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  smoking_daily,
  title = "Daily smoking by condition and phase",
  ylab = "Daily cigarettes"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

### Smoking: Week-level

```{r}
smoking_weekly <- daily_mean_se(
  data = completers,
  var  = daily_cigs,       
  group_by_phase = TRUE,
  pid_col  = "pid",
  day_col  = "week",       
  cond_col = "cond"
)

plot_daily_mean_se(
  summary_df = smoking_weekly,
  day_col    = "week",       
  xlab       = "Week",
  ylab = "Daily craving",
  title      = "Daily ccigarettes by condition and phase"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```



## Subject level {.tabset}

```{r}
library(dplyr)
library(ggplot2)
library(purrr)
library(rlang)
library(patchwork)

make_plots_by_condition <- function(data, var,
                                    pid_col   = "pid",
                                    day_col   = "day",
                                    phase_col = "phase",
                                    cond_col  = "cond",
                                    time_unit = c("day","week"),
                                    ylab      = NULL,
                                    phase_levels = c("Baseline","Intervention"),
                                    color_values = NULL,
                                    skip_single_phase = FALSE) {

  time_unit <- match.arg(time_unit)

  # helper: aggregate to weekly level if requested
  aggregate_time <- function(df) {
    if (time_unit == "day") {
      df %>%
        mutate(.x = .data[[day_col]], .y = {{ var }})
    } else { # "week"
      df %>%
        mutate(.week = ceiling(.data[[day_col]] / 7)) %>%
        group_by(.data[[pid_col]], .data[[phase_col]], .week, .add = FALSE) %>%
        summarise(.y = mean({{ var }}, na.rm = TRUE), .groups = "drop") %>%
        rename(.x = .week)
    }
  }

  conds <- unique(data[[cond_col]])
  out <- lapply(conds, function(cn) {
    dfc <- dplyr::filter(data, .data[[cond_col]] == cn)
    ids <- unique(dfc[[pid_col]])

    pls <- purrr::map(ids, ~ {
      dfp <- dplyr::filter(dfc, .data[[pid_col]] == .x) |>
        dplyr::filter(!is.na({{ var }})) |>
        dplyr::mutate(!!phase_col := factor(.data[[phase_col]], levels = phase_levels)) |>
        aggregate_time()

      # skip if only one phase and requested
      if (skip_single_phase) {
        nph <- dfp |>
          mutate(.ph = dplyr::if_else(time_unit == "day", NA, NA)) # dummy to keep pipes happy
        if (nlevels(droplevels(dplyr::pull(dplyr::distinct(dfp, !!sym(phase_col)), !!sym(phase_col)))) < 2) return(NULL)
      }

      x_lab <- if (time_unit == "day") "Day" else "Week"

      p <- ggplot(
        dfp,
        aes(x = .x, y = .y, color = .data[[phase_col]], group = .data[[phase_col]])
      ) +
        geom_line(linewidth = 0.6) +
        geom_point(size = 1.2, stroke = 0) +
        scale_x_continuous(breaks = scales::pretty_breaks(n = 4)) +
        scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
        labs(x = x_lab, y = ylab) +
        theme_bw(base_size = 9) +
        theme(
          plot.title       = element_text(size = 9, hjust = 0),
          axis.title.x     = element_blank(),   # keep tiles compact
          axis.title.y     = element_blank(),
          axis.text.x      = element_text(size = 7),
          axis.text.y      = element_text(size = 7),
          panel.grid.minor = element_blank(),
          plot.margin      = margin(2, 2, 2, 2)
        )

      if (!is.null(color_values)) {
        p <- p + scale_color_manual(values = color_values)
      }
      p
    })

    keep <- !vapply(pls, is.null, logical(1))
    pls <- pls[keep]
    rlang::set_names(pls, ids[keep])
  })
  rlang::set_names(out, conds)
}

print_condition <- function(plots_by_condition,
                            condition_name,
                            ncol = 2,
                            shared_legend = TRUE,
                            show_headers = FALSE) {
  if (!condition_name %in% names(plots_by_condition)) stop("Condition not found: ", condition_name)
  cond_plots <- plots_by_condition[[condition_name]]
  if (length(cond_plots) == 0L) { message("No plots for condition: ", condition_name); return(invisible(NULL)) }

  if (show_headers) cat("### ", condition_name, "\n\n")

  combined <- patchwork::wrap_plots(
    cond_plots, ncol = ncol,
    guides = if (shared_legend) "collect" else "keep"
  ) +
    patchwork::plot_layout(heights = 1, widths = 1) &
    ggplot2::theme(plot.margin = ggplot2::margin(4, 4, 4, 4))

  if (shared_legend) {
    combined <- combined &
      ggplot2::theme(
        legend.position   = "top",
        legend.text       = ggplot2::element_text(size = 12),
        legend.title      = ggplot2::element_text(size = 13, face = "bold"),
        legend.key.width  = grid::unit(10, "mm"),
        legend.key.height = grid::unit(8, "mm")
      ) &
      ggplot2::guides(color = ggplot2::guide_legend(override.aes = list(size = 3)))
  } else {
    combined <- combined & ggplot2::theme(legend.position = "none")
  }

  print(combined)
  invisible(combined)
}
```

### Craving {.tabset}

```{r}
craving_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_average_crave,
  time_unit = "day",        
  ylab = "Weekly mean craving",
  color_values = palette_phase,
  skip_single_phase = TRUE
)
```

#### Control: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
craving_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_average_crave,
  time_unit = "week",        
  ylab = "Weekly mean craving",
  color_values = palette_phase,
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(craving_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```

### Smoking {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
smoking_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_cigs,
  time_unit = "day", 
  ylab = "Daily cigarettes",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
smoking_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_cigs,
  time_unit = "week", 
  ylab = "Daily cigarettes",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(smoking_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```


# Temporal patterns of additional variables {.tabset}

## Group level {.tabset}

### Exposures (Intent-to-treat)

```{r, fig.width=10, fig.height=8}
exposures_daily_itt <- daily_mean_se(
  data = itt,
  var = daily_exposures_1000ft_100ft,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  exposures_daily_itt,
  title = "Daily exposures by condition and phase",
  ylab = "Daily exposures"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

### Exposures (Completers)

```{r, fig.width=10, fig.height=8}
exposures_daily_completers <- daily_mean_se(
  data = completers,
  var = daily_exposures_1000ft_100ft,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  exposures_daily_completers,
  title = "Daily exposures by condition and phase",
  ylab = "Daily exposures"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

### Stress

```{r, fig.width=10, fig.height=8}
stress_daily <- daily_mean_se(
  data = completers,
  var = daily_stress,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  stress_daily,
  title = "Daily stress by condition and phase",
  ylab = "Daily stress"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

### Negative mood

```{r, fig.width=10, fig.height=8}
neg_mood_daily <- daily_mean_se(
  data = completers,
  var = daily_average_neg,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  neg_mood_daily,
  title = "Daily negative mood by condition and phase",
  ylab = "Daily negative mood"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

### Positive mood

```{r, fig.width=10, fig.height=8}
pos_mood_daily <- daily_mean_se(
  data = completers,
  var = daily_average_pos,
  group_by_phase = TRUE,   
  pid_col  = "pid",
  day_col  = "day",
  cond_col = "cond"
)

plot_daily_mean_se(
  pos_mood_daily,
  title = "Daily positive mood by condition and phase",
  ylab = "Daily positive mood"
) +
  scale_color_manual(values = palette_condition) +
  scale_fill_manual(values = palette_condition)
```

## Subject level {.tabset}

### Stress {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
stress_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_stress,
  time_unit = "day",
  ylab = "Daily stress",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
stress_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_stress,
  time_unit = "week",
  ylab = "Daily stress",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(stress_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```

### Negative mood:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
neg_mood_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_average_neg,
  time_unit = "day",
  ylab = "Daily negative mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
neg_mood_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_average_neg,
  time_unit = "week",
  ylab = "Daily negative mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```


### Positive mood {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
pos_mood_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_average_pos,
  time_unit = "day",
  ylab = "Daily positive mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
pos_mood_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_average_pos,
  time_unit = "week",
  ylab = "Daily positive mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(pos_mood_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
# mobility
# load baseline stay events
geo_data_stay_events_baseline <- read_csv("/Volumes/cnlab/GeoRemote/Data/Geodata/clean/stay_events/baseline/stay_events_baseline.csv")
```

```{r}
# load intervention stay events
geo_data_stay_events_intervention <- read_csv("/Volumes/cnlab/GeoRemote/Data/Geodata/clean/stay_events/intervention/stay_events_intervention.csv")
```

```{r}
# get distance traveled: baseline
geo_data_distance_traveled_baseline_averages <- geo_data_stay_events_baseline %>%
  group_by(pid, day) %>%
  summarise(
    distance_traveled_day_miles_baseline = sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  group_by(pid) %>%
  summarise(
    avg_distance_traveled_per_day_miles_baseline = mean(distance_traveled_day_miles_baseline, na.rm = TRUE)
  )
```

```{r}
# get distance traveled: intervention
geo_data_distance_traveled_intervention_averages <- geo_data_stay_events_intervention %>%
  group_by(pid, day) %>%
  summarise(
    distance_traveled_day_miles_intervention = sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  group_by(pid) %>%
  summarise(
    avg_distance_traveled_per_day_miles_intervention = mean(distance_traveled_day_miles_intervention, na.rm = TRUE)
  )
```

```{r}
# join baseline and intervention averages
geo_data_distance_traveled_averages_combine <- full_join(
  geo_data_distance_traveled_baseline_averages,
  geo_data_distance_traveled_intervention_averages,
  by = "pid"
)
```

```{r}
# join the distance averages with the completers df by pid, condition, and phone type
geo_data_distance_traveled_averages <- geo_data_distance_traveled_averages_combine %>%
  inner_join(
    completers %>% select(pid, cond, platformType) %>% distinct(),
    by = "pid"
  )
```

```{r}
# calculate the difference in distance traveled between phases
geo_data_distance_traveled_averages <- geo_data_distance_traveled_averages %>%  mutate(distance_difference = avg_distance_traveled_per_day_miles_intervention - avg_distance_traveled_per_day_miles_baseline) 
```

```{r}
# calculate z-scores so we can filter outliers later
geo_data_distance_traveled_averages <- geo_data_distance_traveled_averages %>%
  mutate(
    z_distance_difference = (distance_difference - mean(distance_difference, na.rm = TRUE)) /
                            sd(distance_difference, na.rm = TRUE)
  )
```

```{r}
# subset to just IOS users
geo_data_distance_traveled_averages_ios <- geo_data_distance_traveled_averages %>% 
  filter(platformType == "IOS")
```

```{r}
# subset to just Android users
geo_data_distance_traveled_averages_android <- geo_data_distance_traveled_averages %>% 
  filter(platformType == "ANDROID")
```


```{r}
# plot: average distance traveled per day by condition and phase
# pivot df to long format 
geo_long <- geo_data_distance_traveled_averages %>%
  pivot_longer(
    cols = c(avg_distance_traveled_per_day_miles_baseline,
             avg_distance_traveled_per_day_miles_intervention),
    names_to = "phase",
    values_to = "avg_distance_miles"
  ) %>%
  mutate(
    phase = recode(phase,
      "avg_distance_traveled_per_day_miles_baseline" = "Baseline",
      "avg_distance_traveled_per_day_miles_intervention" = "Intervention"
    )
  )

# get summary stats
dist_summary <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "summary"
)

# plot
ggplot(dist_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Avg miles/day", fill = "Phase",
       title = "Average distance traveled per day by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# get summary stats
dist_pid_means <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "pid"
)

# plot
ggplot(dist_pid_means, aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of average miles/day by condition and phase",
    x = "PID mean miles/day",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )

```


```{r}
# filters outliers 
geo_data_distance_traveled_averages_no_outliers <- geo_data_distance_traveled_averages %>%
  filter(abs(z_distance_difference) <= 3)

distance_summary <- calc_mean_se(geo_data_distance_traveled_averages_no_outliers, "distance_difference", group_by_phase = FALSE)

# recall palette condition because for some reason it is not working 
palette_condition <- c(
  "Control" = "#C29B5B",  # deep teal
  "Low"     = "#5BC29B",
  "High"    = "#9B5BC2"   # rust
)

# plot difference 
ggplot(distance_summary, aes(x = cond, y = mean, fill = cond)) +
  geom_col(color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2) +
  scale_fill_manual(values = palette_condition) +
  labs(x = "Condition", y = "Miles traveled difference",
       title = "Miles traveled difference by condition") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

```{r}
# plot: average distance traveled per day by condition and phase for IOS users
# pivot df to long format 
geo_long <- geo_data_distance_traveled_averages_ios %>%
  pivot_longer(
    cols = c(avg_distance_traveled_per_day_miles_baseline,
             avg_distance_traveled_per_day_miles_intervention),
    names_to = "phase",
    values_to = "avg_distance_miles"
  ) %>%
  mutate(
    phase = recode(phase,
      "avg_distance_traveled_per_day_miles_baseline" = "Baseline",
      "avg_distance_traveled_per_day_miles_intervention" = "Intervention"
    )
  )

# get summary stats
dist_summary <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "summary"
)

# plot
ggplot(dist_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Avg miles/day", fill = "Phase",
       title = "Average distance traveled per day by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# get summary stats
dist_pid_means <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "pid"
)

# plot
ggplot(dist_pid_means, aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of average miles/day by condition and phase",
    x = "PID mean miles/day",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )
```

```{r}
# plot: average distance traveled per day by condition and phase for Android users
# pivot df to long format 
geo_long <- geo_data_distance_traveled_averages_android %>%
  pivot_longer(
    cols = c(avg_distance_traveled_per_day_miles_baseline,
             avg_distance_traveled_per_day_miles_intervention),
    names_to = "phase",
    values_to = "avg_distance_miles"
  ) %>%
  mutate(
    phase = recode(phase,
      "avg_distance_traveled_per_day_miles_baseline" = "Baseline",
      "avg_distance_traveled_per_day_miles_intervention" = "Intervention"
    )
  )

# get summary stats
dist_summary <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "summary"
)

# plot
ggplot(dist_summary, aes(x = cond, y = mean, fill = phase)) +
  geom_col(position = position_dodge(0.6), color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                position = position_dodge(0.6), width = 0.2) +
  scale_fill_manual(values = palette_phase) +
  labs(x = "Condition", y = "Avg miles/day", fill = "Phase",
       title = "Average distance traveled per day by condition and phase") +
  theme_bw(base_size = 14) +
  theme(axis.text = element_text(color = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# get summary stats
dist_pid_means <- calc_mean_se(
  geo_long,
  avg_distance_miles,
  group_by_phase = TRUE,
  pid_col = "pid",
  return = "pid"
)

# plot
ggplot(dist_pid_means, aes(x = pid_mean)) +
  geom_histogram(bins = 20, color = "black", fill = "#79C3BC") +
  facet_grid(phase ~ cond) +
  labs(
    title = "Distribution of average miles/day by condition and phase",
    x = "PID mean miles/day",
    y = "Count"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5)
  )
```

```{r}
# analyzing distance traveled at the day level
geo_data_distance_traveled_baseline_day <- geo_data_stay_events_baseline %>%
  group_by(pid, day) %>%
  summarise(
    miles_traveled = sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  mutate(phase = "Baseline")

geo_data_distance_traveled_intervention_day <- geo_data_stay_events_intervention %>%
  group_by(pid, day) %>%
  summarise(
    miles_traveled = sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  mutate(phase = "Intervention")
```

```{r}
# join baseline and intervention distance dfs
geo_data_distance_traveled_day_combine <- bind_rows(
  geo_data_distance_traveled_baseline_day,
  geo_data_distance_traveled_intervention_day
)
```

```{r}
# joing the day-level distance data with the day-level completers day
completers <- completers %>%
  left_join(geo_data_distance_traveled_day_combine, by = c("pid", "day", "phase"))
```

### Miles traveled {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
# plot by day
miles_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = miles_traveled,
  time_unit = "day",
  ylab = "Daily miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
# filter to IOS users
completers_ios <- completers %>% 
  filter(platformType == "IOS")
```

#### Control:Day-level (IOS users) {.tabset}
```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
# plot by day
miles_plots_by_condition_day_ios <- make_plots_by_condition(
  data = completers_ios,
  var  = miles_traveled,
  time_unit = "day",
  ylab = "Daily miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control:Day-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "High", ncol = 2, shared_legend = TRUE)
```


```{r}
# filter to Android users
completers_android <- completers %>% 
  filter(platformType == "Android")
```

#### Control:Day-level (Android users) {.tabset}
```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
# plot by day
miles_plots_by_condition_week <- make_plots_by_condition(
  data = completers_ios,
  var  = miles_traveled,
  time_unit = "day",
  ylab = "Daily miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control:Day-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_day_ios, "High", ncol = 2, shared_legend = TRUE)
```


```{r}
miles_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = miles_traveled,
  time_unit = "week",
  ylab = "Miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```


```{r}
# IOS users
miles_plots_by_condition_week_ios <- make_plots_by_condition(
  data = completers_ios,
  var  = miles_traveled,
  time_unit = "week",
  ylab = "Miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_ios, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_ios, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level (IOS users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_ios, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
# Android users
miles_plots_by_condition_week_android <- make_plots_by_condition(
  data = completers_android,
  var  = miles_traveled,
  time_unit = "week",
  ylab = "Miles traveled",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_android, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_android, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level (Android users){.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(miles_plots_by_condition_week_android, "High", ncol = 2, shared_legend = TRUE)
```



### Negative mood:Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
neg_mood_plots_by_condition_day <- make_plots_by_condition(
  data = completers,
  var  = daily_average_neg,
  time_unit = "day",
  ylab = "Daily negative mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Day-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_day, "High", ncol = 2, shared_legend = TRUE)
```

### Negative mood: Week-level {.tabset}
```{r, results='asis', echo=FALSE, fig.width=12, fig.height=30}
neg_mood_plots_by_condition_week <- make_plots_by_condition(
  data = completers,
  var  = daily_average_neg,
  time_unit = "week",
  ylab = "Daily negative mood",
  color_values = palette_phase, 
  skip_single_phase = TRUE
)
```

#### Control: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "Control", ncol = 2, shared_legend = TRUE)
```

#### Low: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "Low", ncol = 2, shared_legend = TRUE)
```

#### High: Week-level {.tabset}

```{r, results='asis', echo=FALSE, fig.width=12, fig.height=50}
print_condition(neg_mood_plots_by_condition_week, "High", ncol = 2, shared_legend = TRUE)
```

```{r}
# weekly survey data
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_qualtrics.r"))

weekly_data <- load_qualtrics_weekly_surveys(type = "clean")
```

```{r}
# joing weekly survey data with completers df
weekly_df <- weekly_data %>%
  inner_join(
    completers %>% select(pid, cond) %>% distinct(),
    by = "pid"
  )
```

```{r}
# 1) participant-week means (one value per pid×week)
weekly_pid_means <- weekly_df %>%
  group_by(pid, cond, week) %>%
  summarise(mean_days_03 = mean(days_03, na.rm = TRUE), .groups = "drop") %>%
  mutate(mean_days_03 = ifelse(is.nan(mean_days_03), NA_real_, mean_days_03)) %>%
  filter(!is.na(mean_days_03))

# 2) per-week means
weekly_means_by_week <- weekly_pid_means %>%
  group_by(cond, week) %>%
  summarise(mean_days_03 = mean(mean_days_03, na.rm = TRUE), .groups = "drop")

# 3) pooled SE per condition (across *all* pid×week rows)
cond_level_se <- weekly_pid_means %>%
  group_by(cond) %>%
  summarise(
    n = dplyr::n(),
    se_days_03 = ifelse(n > 1, sd(mean_days_03, na.rm = TRUE) / sqrt(n), 0),
    .groups = "drop"
  )

# 4) join pooled SE back to each weekly point and compute bars
weekly_summary <- weekly_means_by_week %>%
  left_join(cond_level_se, by = "cond") %>%
  mutate(
    week = suppressWarnings(as.numeric(as.character(week))),
    ymin = mean_days_03 - se_days_03,
    ymax = mean_days_03 + se_days_03
  )

# 5) plot: constant SE within each condition across weeks
ggplot(weekly_summary, aes(x = week, y = mean_days_03, color = cond, group = cond)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.2, size = 0.8) +
  scale_color_manual(values = palette_condition) +
  labs(
    x = "Week",
    y = "Exposure recall",
    color = "Condition",
    title = "Weekly exposure recall by condition"
  ) +
  theme_bw(base_size = 14) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())
```

```{r}
# 1) participant-week means (one value per pid×week)
weekly_pid_means <- weekly_df %>%
  group_by(pid, cond, week) %>%
  summarise(mean_days_04 = mean(days_04, na.rm = TRUE), .groups = "drop") %>%
  mutate(mean_days_04 = ifelse(is.nan(mean_days_04), NA_real_, mean_days_04)) %>%
  filter(!is.na(mean_days_04))

# 2) per-week means
weekly_means_by_week <- weekly_pid_means %>%
  group_by(cond, week) %>%
  summarise(mean_days_04 = mean(mean_days_04, na.rm = TRUE), .groups = "drop")

# 3) pooled SE per condition (across *all* pid×week rows)
cond_level_se <- weekly_pid_means %>%
  group_by(cond) %>%
  summarise(
    n = dplyr::n(),
    se_days_04 = ifelse(n > 1, sd(mean_days_04, na.rm = TRUE) / sqrt(n), 0),
    .groups = "drop"
  )

# 4) join pooled SE back to each weekly point and compute bars
weekly_summary <- weekly_means_by_week %>%
  left_join(cond_level_se, by = "cond") %>%
  mutate(
    week = suppressWarnings(as.numeric(as.character(week))),
    ymin = mean_days_04 - se_days_04,
    ymax = mean_days_04 + se_days_04
  )

# 5) plot: constant SE within each condition across weeks
ggplot(weekly_summary, aes(x = week, y = mean_days_04, color = cond, group = cond)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.2, size = 0.8) +
  scale_color_manual(values = palette_condition) +
  labs(
    x = "Week",
    y = "Impulse purchases",
    color = "Condition",
    title = "Weekly impulse purchases by condition"
  ) +
  theme_bw(base_size = 14) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())
```


```{r}
# 1) participant-week means (one value per pid×week)
weekly_pid_means <- weekly_df %>%
  group_by(pid, cond, week) %>%
  summarise(mean_days_02 = mean(days_02, na.rm = TRUE), .groups = "drop") %>%
  mutate(mean_days_02 = ifelse(is.nan(mean_days_02), NA_real_, mean_days_02)) %>%
  filter(!is.na(mean_days_02))

# 2) per-week means
weekly_means_by_week <- weekly_pid_means %>%
  group_by(cond, week) %>%
  summarise(mean_days_02 = mean(mean_days_02, na.rm = TRUE), .groups = "drop")

# 3) pooled SE per condition (across *all* pid×week rows)
cond_level_se <- weekly_pid_means %>%
  group_by(cond) %>%
  summarise(
    n = dplyr::n(),
    se_days_02 = ifelse(n > 1, sd(mean_days_02, na.rm = TRUE) / sqrt(n), 0),
    .groups = "drop"
  )

# 4) join pooled SE back to each weekly point and compute bars
weekly_summary <- weekly_means_by_week %>%
  left_join(cond_level_se, by = "cond") %>%
  mutate(
    week = suppressWarnings(as.numeric(as.character(week))),
    ymin = mean_days_02 - se_days_02,
    ymax = mean_days_02 + se_days_02
  )

# 5) plot: constant SE within each condition across weeks
ggplot(weekly_summary, aes(x = week, y = mean_days_02, color = cond, group = cond)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.2, size = 0.8) +
  scale_color_manual(values = palette_condition) +
  labs(
    x = "Week",
    y = "Media exposure",
    color = "Condition",
    title = "Weekly media exposure by condition"
  ) +
  theme_bw(base_size = 14) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())
```

```{r}
# compute correlations
cor.test(weekly_df$days_03, weekly_df$days_04)
```

```{r}
# control only
weekly_df_control <- weekly_df %>% 
  filter(cond == "Control")

cor.test(weekly_df_control$days_03, weekly_df_control$days_04)
```

```{r}
# low only
weekly_df_low <- weekly_df %>% 
  filter(cond == "Low")

cor.test(weekly_df_low$days_03, weekly_df_low$days_04)
```

```{r}
# high only
weekly_df_high <- weekly_df %>% 
  filter(cond == "High")

cor.test(weekly_df_high$days_03, weekly_df_high$days_04)
```

```{r}
completers_intervention <- completers %>% 
  filter(phase == "Intervention")
```

```{r}
completers_intervention_weekly <- completers %>%
  filter(phase == "Intervention") %>%        
  group_by(pid, week) %>%
  summarise(
    exposures = mean(daily_exposures_1000ft_100ft, na.rm = TRUE)     
  )
```

```{r}
weekly_df_intervention <- weekly_df %>% 
  filter(week != 0)
```

```{r}
intervention_weekly_all <- completers_intervention_weekly %>%
  left_join(weekly_df_intervention, by = c("pid", "week"))
```

```{r}
# compute correlations
cor.test(intervention_weekly_all$exposures, intervention_weekly_all$days_03)
```

```{r}
# control only
intervention_weekly_all_control <- intervention_weekly_all %>% 
  filter(cond == "Control")

cor.test(intervention_weekly_all_control$exposures, intervention_weekly_all_control$days_03)
```

```{r}
# low only
intervention_weekly_all_low <- intervention_weekly_all %>% 
  filter(cond == "Low")

cor.test(intervention_weekly_all_low$exposures, intervention_weekly_all_low$days_03)
```

```{r}
# high only
intervention_weekly_all_high <- intervention_weekly_all %>% 
  filter(cond == "High")

cor.test(intervention_weekly_all_high$exposures, intervention_weekly_all_high$days_03)
```


```{r}
cor.test(intervention_weekly_all$exposures, intervention_weekly_all$days_04)
```

```{r}
# control only
intervention_weekly_all_control <- intervention_weekly_all %>% 
  filter(cond == "Control")

cor.test(intervention_weekly_all_control$exposures, intervention_weekly_all_control$days_04)
```

```{r}
# low only
intervention_weekly_all_low <- intervention_weekly_all %>% 
  filter(cond == "Low")

cor.test(intervention_weekly_all_low$exposures, intervention_weekly_all_low$days_04)
```

```{r}
# high only
intervention_weekly_all_high <- intervention_weekly_all %>% 
  filter(cond == "High")

cor.test(intervention_weekly_all_high$exposures, intervention_weekly_all_high$days_04)
```