---
title: "Aim 1 Analysis"
author: "Ben Muzekari"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # Show code by default
  message = FALSE,  # Suppress messages by default
  warning = FALSE   # Suppress warnings by default
)
```

# Setup {.tabset}

## Set scripts directory

```{r, echo=FALSE}
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

## Load analysis functions

```{r}
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis.r"))
```

## Load EMA, and covariate data

```{r}
EMA_Baseline_Covariates_Distinct = load_ema_with_covs(Type="Baseline",
                                                      ema_variables = c("day", "daily_average_crave", "daily_cigs", "daily_stress"),
                        redcap_variables = c("pid","age","gender","ethnicity","race")) %>%
  add_survey_measure("FTND", session=1) %>%
  add_descriptives(vars="platformType") %>%
  distinct()

zips <- read_csv("/Volumes/cnlab/GeoRemote/Data/Geodata/utility/Geo Remote Zipcodes.csv")
pid_order <- read_excel("/Volumes/cnlab/GeoRemote/Data/Geodata/utility/pids_order.xlsx")
location_df <- cbind(zips, pid_order) %>%
  select(-City, -Zip)

EMA_Baseline_Covariates_Distinct <- EMA_Baseline_Covariates_Distinct %>%
  left_join(location_df, by = "pid")
```

## Load Geo Data

### Exposures

```{r, echo=FALSE}
# Load in geo data
geo_data_baseline_exposures = load_geo_exposures(Type="Baseline")
```

## Check craving min and max

```{r, echo=FALSE}
min(EMA_Baseline_Covariates_Distinct$daily_average_crave, na.rm = TRUE) 
max(EMA_Baseline_Covariates_Distinct$daily_average_crave, na.rm = TRUE)
#[1] 0
#[1] 100
```

## Check cigs descriptives

```{r, echo=FALSE}
psych::describe(EMA_Baseline_Covariates_Distinct$daily_cigs)
#    vars    n  mean   sd median trimmed  mad min max range skew kurtosis   se
# X1    1 4186 13.39 8.03     12   12.39 5.93   0  87    87 2.59    14.09 0.12
```

# Analyses and models

## Join Data

```{r}
Final_df <- left_join(geo_data_baseline_exposures, EMA_Baseline_Covariates_Distinct, by = c("pid", "day"))
```

## Check min and max day counts for geo data

```{r, echo=FALSE}
min(geo_data_baseline_exposures$day, na.rm = TRUE) 
max(geo_data_baseline_exposures$day, na.rm = TRUE) 
# [1] 1
# [1] 14
```

## check if people have less than 14 days

```{r, echo=FALSE}
# print(check_days(Final_df))

#  [1] "GR021" "GR026" "GR027" "GR029" "GR031" "GR055" "GR139" "GR144" "GR146" "GR160" "GR164" "GR167" "GR168" "GR175" "GR193" "GR222" "GR261" "GR263"
# [19] "GR277" "GR286" "GR292" "GR305" "GR310"
```

## get participant count

```{r, echo=FALSE}
num_unique_values <- length(unique(Final_df$pid))
print(num_unique_values)
# [1] 273
```

# Distributions {.tabset}

```{r, echo=FALSE}
# Create df with averages by pid
average_df_by_pid <- Final_df %>%
  group_by(pid) %>%
  dplyr::summarize(
    daily_exposures_1000ft_100ft = mean(daily_exposures_1000ft_100ft, na.rm = TRUE),
    daily_average_crave = mean(daily_average_crave, na.rm = TRUE),
    daily_cigs = mean(daily_cigs, na.rm = TRUE)
  )
```

## Average Exposures (1000 ft, 100 ft)

```{r, echo=FALSE}
create_distribution_plot(average_df_by_pid, "daily_exposures_1000ft_100ft", "Distribution of Average Daily Exposures", "Average Daily Exposures (1000 ft, 100 ft)", "Frequency")
```

## Average Craving

```{r, echo=FALSE}
create_distribution_plot(average_df_by_pid, "daily_average_crave", "Distribution of Average Daily Craving", "Average Daily Craving", "Frequency")
```

## Average Cigarettes

```{r, echo=FALSE}
create_distribution_plot(average_df_by_pid, "daily_cigs", "Distribution of Average Daily Cigarettes", "Average Daily Cigarettes", "Frequency")
```

## Demographics

```{r}
demographics_info <- Final_df %>%
  group_by(pid) %>%
  dplyr::summarize(
    age = first(age),           
    gender = first(gender),   
    race = first(race),         
    ethnicity = first(ethnicity),
    FTND_score = first(FTND_score),
    platformType = first(platformType),
    State = first(State)
  )

psych::describe(demographics_info$age)
#    vars   n  mean    sd median trimmed   mad min max range skew kurtosis   se
# 1	273	42.46	10.67	42	42.45	11.86	21	64	43	0.06	-0.83	0.65

gender_summary <- demographics_info %>%
  group_by(gender) %>%
  dplyr::summarize(
    count = n(),                                 
    percentage = (count / nrow(demographics_info)) * 100 
  ) %>%
  ungroup()                                       

print(gender_summary)
#   gender       count percentage
#   <fct>        <int>      <dbl>
# 1 Man            111     40.7  
# 2 Woman          151     55.3  
# 3 Non-binary       6      2.20 
# 4 Genderqueer      2      0.733
# 5 Gender fluid     1      0.366
# 6 NA               2      0.733

race_summary <- demographics_info %>%
  group_by(race) %>%
  dplyr::summarize(
    count = n(),                                 
    percentage = (count / nrow(demographics_info)) * 100 
  ) %>%
  ungroup()                                       

print(race_summary)
#   race                             count percentage
#   <fct>                            <int>      <dbl>
# 1 Asian                                7      2.56 
# 2 Black                               64     23.4  
# 3 American Indian or Alaska Native     2      0.733
# 4 White                              175     64.1  
# 5 Prefer to self-describe              8      2.93 
# 6 Prefer not to say                    1      0.366
# 7 More than one                       13      4.76 
# 8 NA                                   3      1.10

ethnicity_summary <- demographics_info %>%
  group_by(ethnicity) %>%
  dplyr::summarize(
    count = n(),                                 
    percentage = (count / nrow(demographics_info)) * 100 
  ) %>%
  ungroup()                                       

print(ethnicity_summary)
#   ethnicity         count percentage
#   <fct>             <int>      <dbl>
# 1 No                  252     92.3  
# 2 Yes                  18      6.59 
# 3 Prefer not to say     1      0.366
# 4 NA                    2      0.733

psych::describe(demographics_info$FTND_score)
#    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
# X1    1 270 5.62 1.94      6    5.69 2.97   1  10     9 -0.24    -0.79 0.12

smartphone_type_summary <- demographics_info %>%
  group_by(platformType) %>%
  dplyr::summarize(
    count = n(),                                 
    percentage = (count / nrow(demographics_info)) * 100 
  ) %>%
  ungroup() 

print(smartphone_type_summary)
#   platformType count percentage
#   <chr>        <int>      <dbl>
# 1 ANDROID        152       55.7
# 2 IOS            121       44.3

state_summary <- demographics_info %>%
  group_by(State) %>%
  dplyr::summarize(
    count = n(),                                 
    percentage = (count / nrow(demographics_info)) * 100 
  ) %>%
  ungroup()   

print(state_summary)
# State count percentage
# DE	25	9.157509		
# NJ	43	15.750916		
# PA	205	75.091575	
```

## check count for only pids with variation in exposure

```{r}
variation_only_1000ft_100ft <- Final_df %>%
  group_by(pid) %>%
  filter(sd(daily_exposures_1000ft_100ft, na.rm = TRUE) > 0) %>%
  ungroup()

print(n_distinct(variation_only_1000ft_100ft$pid))
# [1] 273
```

# Outliers {.tabset}

# GR293 outlier z-score (cigs)

```{r}
max_val <- max(average_df_by_pid$daily_cigs, na.rm = TRUE)
mean_val <- mean(average_df_by_pid$daily_cigs, na.rm = TRUE)
sd_val <- sd(average_df_by_pid$daily_cigs, na.rm = TRUE)
z_max <- (max_val - mean_val) / sd_val
z_max
# [1] 8.458328
```

# second highest z-score (cigs)

```{r}
sorted_vals <- sort(average_df_by_pid$daily_cigs, decreasing = TRUE, na.last = NA)
second_highest <- sorted_vals[2]

mean_val <- mean(average_df_by_pid$daily_cigs, na.rm = TRUE)
sd_val <- sd(average_df_by_pid$daily_cigs, na.rm = TRUE)
z_second_highest <- (second_highest - mean_val) / sd_val
z_second_highest
# [1] 3.441116
```

# lowest (cigs)

```{r}
sorted_vals <- sort(average_df_by_pid$daily_cigs, decreasing = TRUE, na.last = NA)
lowest <- sorted_vals[273]

mean_val <- mean(average_df_by_pid$daily_cigs, na.rm = TRUE)
sd_val <- sd(average_df_by_pid$daily_cigs, na.rm = TRUE)
lowest <- (lowest - mean_val) / sd_val
lowest
#[1] -1.430247
```

# highest (crave)

```{r}
max_val <- max(average_df_by_pid$daily_average_crave, na.rm = TRUE)
mean_val <- mean(average_df_by_pid$daily_average_crave, na.rm = TRUE)
sd_val <- sd(average_df_by_pid$daily_average_crave, na.rm = TRUE)
z_max <- (max_val - mean_val) / sd_val
z_max
#[1] 2.513895
```

# lowest (crave)

```{r}
sorted_vals <- sort(average_df_by_pid$daily_average_crave, decreasing = TRUE, na.last = NA)
lowest <- sorted_vals[273]

mean_val <- mean(average_df_by_pid$daily_average_crave, na.rm = TRUE)
sd_val <- sd(average_df_by_pid$daily_average_crave, na.rm = TRUE)
lowest <- (lowest - mean_val) / sd_val
lowest
#[1] -2.39905
```


## Cigs Outlier

```{r}
GR293 <- Final_df  %>%
  filter(pid == "GR293")

psych::describe(GR293$daily_cigs)
#    vars  n  mean   sd median trimmed  mad min max range skew kurtosis  se
# X1    1 14 75.71 5.99   74.5   75.75 5.19  64  87    23 0.09    -0.64 1.6
```

# Data cleaning {.tabset}

```{r, echo=FALSE}
# df excluding outlier
Final_df_no_outliers <- Final_df %>%
  filter(!(pid %in% c("GR293")))
```

## Winsorize variables

```{r}
Final_df = winsorize_variables(Final_df, 
                               c("daily_exposures_1000ft_100ft",
                                 "daily_average_crave", 
                                 "daily_cigs"))
```

### Split variables

```{r}
Final_df <- split_within_between(Final_df,
                                 c("daily_exposures_1000ft_100ft_wins",
                                   "daily_exposures_1000ft_100ft"))
```

# Analysis {.tabset}

## Define models

```{r}
# define model with no autocorrelation, using ML
exposure_model_1000ft_wins_ML_no_auto = create_model_function_lme(
  model = "daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day",
  random_effects = ~ daily_exposures_1000ft_100ft_wins_wn | pid,
  correlation = NULL,
  method = "ML"
)

# define model with autocorrelation, using ML
exposure_model_1000ft_wins_ML <- create_model_function_lme(
  model = "daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day",
  random_effects = ~ daily_exposures_1000ft_100ft_wins_wn | pid,
  correlation = corAR1(form = ~ day | pid),
  method = "ML"
)

# define model with autocorrelation, using REML
exposure_model_1000ft_wins <- create_model_function_lme(
  model = "daily_exposures_1000ft_100ft_wins_wn + daily_exposures_1000ft_100ft_wins_bw + day",
  random_effects = ~ daily_exposures_1000ft_100ft_wins_wn | pid,
  correlation = corAR1(form = ~ day | pid),
    method = "REML"
)
```

## crave, compare model fits

```{r}
# ML, autocorrelation
lme_craving_1000ft_100ft_wins_ML <- exposure_model_1000ft_wins_ML(
  data = Final_df,
  dv = "daily_average_crave_wins",
  covs = NULL 
)
summary(lme_craving_1000ft_100ft_wins_ML)

# ML, no autocorrelation
lme_craving_1000ft_100ft_wins_ML_no_auto = exposure_model_1000ft_wins_ML_no_auto(
  Final_df, 
  dv= "daily_average_crave_wins",
    covs = NULL)
summary(lme_craving_1000ft_100ft_wins_ML_no_auto)

# compare fits using ML with and without autocorrelation
anova(lme_craving_1000ft_100ft_wins_ML, lme_craving_1000ft_100ft_wins_ML_no_auto)
```

## crave, fit final model with autocorrelation, using REML

```{r}
lme_craving_1000ft_100ft_wins <- exposure_model_1000ft_wins(
  data = Final_df,
  dv = "daily_average_crave_wins",
  covs = NULL 
)

summary(lme_craving_1000ft_100ft_wins)
get_lme_stats(lme_craving_1000ft_100ft_wins)
intervals(lme_craving_1000ft_100ft_wins, which = "fixed")
```

## cigs, compare model fits

```{r}
# ML, autocorrelation
lme_cigs_1000ft_100ft_wins_ML <- exposure_model_1000ft_wins_ML(
  data = Final_df,
  dv = "daily_cigs_wins",
  covs = NULL 
)
summary(lme_cigs_1000ft_100ft_wins_ML)

# ML, no autocorrelation
lme_cigs_1000ft_100ft_wins_ML_no_auto = exposure_model_1000ft_wins_ML_no_auto(
  Final_df, 
  dv= "daily_cigs_wins",
    covs = NULL)
summary(lme_cigs_1000ft_100ft_wins_ML_no_auto)

# compare fits using ML with and without autocorrelation
anova(lme_cigs_1000ft_100ft_wins_ML, lme_cigs_1000ft_100ft_wins_ML_no_auto)
```

## cigs, fit final model with autocorrelation, using REML

```{r}
lme_cigs_1000ft_100ft_wins <- exposure_model_1000ft_wins(
  data = Final_df,
  dv = "daily_cigs_wins",
  covs = NULL 
)

summary(lme_cigs_1000ft_100ft_wins)
get_lme_stats(lme_cigs_1000ft_100ft_wins)
intervals(lme_cigs_1000ft_100ft_wins)
```

## for grant power analysis, exposure + craving

```{r}
Final_df_grant <- split_within_between(Final_df,
                                 c("daily_average_crave_wins",
                                   "daily_cigs_wins"))

sd(Final_df_grant$daily_exposures_1000ft_100ft_wins_wn, na.rm = TRUE)
# [1] 17.79002

sd(Final_df_grant$daily_average_crave_wins, na.rm = TRUE)
# [1] 25.21204

sd(Final_df_grant$daily_average_crave_wins_wn, na.rm = TRUE) 
# [1] 14.94846
```

## for grant power analysis, smoking

```{r}
sd(Final_df_grant$daily_cigs_wins, na.rm = TRUE)
# [1] 8.020276

sd(Final_df_grant$daily_cigs_wins_wn, na.rm = TRUE) 
# [1] 3.183946
```

## for grant power analysis, craving and smoking

```{r}
# define model with autocorrelation, using REML
exposure_model_1000ft_wins_grant <- create_model_function_lme(
  model = "daily_average_crave_wins_wn + daily_average_crave_wins_bw + day",
  random_effects = ~ daily_average_crave_wins_wn | pid,
  correlation = corAR1(form = ~ day | pid),
    method = "REML"
)

lme_cigs_1000ft_100ft_wins_grant <- exposure_model_1000ft_wins_grant(
  data = Final_df_grant,
  dv = "daily_cigs_wins",
  covs = NULL 
)

summary(lme_cigs_1000ft_100ft_wins_grant)
get_lme_stats(lme_cigs_1000ft_100ft_wins_grant)
intervals(lme_cigs_1000ft_100ft_wins_grant)
```



## Models with no outliers

```{r}
## Winsorize exposures
Final_df_no_outliers = winsorize_variables(Final_df_no_outliers, 
                               c("daily_exposures_1000ft_100ft",
                                 "daily_average_crave", 
                                 "daily_cigs"))

## Split new winsorized variables
Final_df_no_outliers <- split_within_between(Final_df_no_outliers,
                                   "daily_exposures_1000ft_100ft_wins")

```

### crave \~ exposures 1000ft

```{r, echo=FALSE}
lme_craving_1000ft_100ft_wins_no_outliers = exposure_model_1000ft_wins(
  Final_df_no_outliers, 
  dv= "daily_average_crave_wins",
  covs = NULL)

summary(lme_craving_1000ft_100ft_wins_no_outliers)
get_lme_stats(lme_craving_1000ft_100ft_wins_no_outliers)
intervals(lme_craving_1000ft_100ft_wins_no_outliers, which = "fixed")
```

### cigs \~ exposures 1000ft

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_wins_no_outliers <- 
  exposure_model_1000ft_wins(
    Final_df_no_outliers, 
    dv= "daily_cigs_wins",
     covs = NULL)

summary(lme_cigs_1000ft_100ft_wins_no_outliers)
get_lme_stats(lme_cigs_1000ft_100ft_wins_no_outliers)
intervals(lme_cigs_1000ft_100ft_wins_no_outliers)
```

## Models with non-winsorized data

```{r}
exposure_model_1000ft <- create_model_function_lme(
  model = "daily_exposures_1000ft_100ft_wn + daily_exposures_1000ft_100ft_bw + day",
  random_effects = ~ daily_exposures_1000ft_100ft_wn | pid,
  correlation = corAR1(form = ~ day | pid),
  method = "REML"
)

# cigs model below is not converging, so just specifying a random intercept here:
exposure_model_1000ft_random_intercept_only <- create_model_function_lme(
  model = "daily_exposures_1000ft_100ft_wn + daily_exposures_1000ft_100ft_bw + day",
  random_effects = ~ 1 | pid,
  correlation = corAR1(form = ~ day | pid),
  method = "REML"
)
```

### crave \~ exposures 1000ft

```{r, echo=FALSE}
lme_craving_1000ft_100ft <- exposure_model_1000ft(
  data = Final_df,
  dv = "daily_average_crave",
  covs = NULL 
)
summary(lme_craving_1000ft_100ft)
get_lme_stats(lme_craving_1000ft_100ft)
intervals(lme_craving_1000ft_100ft, which = "fixed")
```

### cigs \~ exposures 1000ft

```{r, echo=FALSE}
lme_cigs_1000ft_100ft <- exposure_model_1000ft_random_intercept_only(
  Final_df, 
  dv= "daily_cigs",
  covs = NULL)

summary(lme_cigs_1000ft_100ft)
get_lme_stats(lme_cigs_1000ft_100ft)
intervals(lme_cigs_1000ft_100ft)
```

### plots

```{r}
# get fixed effects 
fixed_effects_crave <- fixef(lme_craving_1000ft_100ft_wins)
fixed_effects_cigs  <- fixef(lme_cigs_1000ft_100ft_wins)

# get random effects (intercepts and slopes)
random_effects_crave <- ranef(lme_craving_1000ft_100ft_wins) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `daily_exposures_1000ft_100ft_wins_wn`
  )

random_effects_cigs <- ranef(lme_cigs_1000ft_100ft_wins) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("pid") %>%
  dplyr::rename(
    intercept = `(Intercept)`,
    slope = `daily_exposures_1000ft_100ft_wins_wn`
  )

# compute predictions
Final_df_crave <- Final_df %>%
  left_join(random_effects_crave, by = "pid") %>%
  mutate(predicted = (fixed_effects_crave["(Intercept)"] + intercept) + 
                     (fixed_effects_crave["daily_exposures_1000ft_100ft_wins_wn"] + slope) * daily_exposures_1000ft_100ft_wins_wn)

Final_df_cigs <- Final_df %>%
  left_join(random_effects_cigs, by = "pid") %>%
  mutate(predicted = (fixed_effects_cigs["(Intercept)"] + intercept) + 
                     (fixed_effects_cigs["daily_exposures_1000ft_100ft_wins_wn"] + slope) * daily_exposures_1000ft_100ft_wins_wn)

# get betas and p-values
beta_crave <- summary(lme_craving_1000ft_100ft_wins)$tTable["daily_exposures_1000ft_100ft_wins_wn", "Value"]
p_crave    <- summary(lme_craving_1000ft_100ft_wins)$tTable["daily_exposures_1000ft_100ft_wins_wn", "p-value"]

beta_cigs <- summary(lme_cigs_1000ft_100ft_wins)$tTable["daily_exposures_1000ft_100ft_wins_wn", "Value"]
p_cigs    <- summary(lme_cigs_1000ft_100ft_wins)$tTable["daily_exposures_1000ft_100ft_wins_wn", "p-value"]

# format labels
label_b <- function(beta) bquote(italic(b) == .(round(beta, 2)))
label_p <- function(p) bquote(italic(p) == .(ifelse(p < 0.001, "< 0.001", round(p, 2))))

# label positions
x_crave <- max(Final_df_crave$daily_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_crave <- max(Final_df_crave$predicted, na.rm = TRUE) * 0.99

x_cigs <- max(Final_df_cigs$daily_exposures_1000ft_100ft_wins_wn, na.rm = TRUE) * 0.99
y_cigs <- max(Final_df_cigs$predicted, na.rm = TRUE) * 0.99

# plot function
plot_predicted <- function(df, ylab, beta, pval, x_pos, y_pos, y_limit = NULL) {
  ggplot(df, aes(x = daily_exposures_1000ft_100ft_wins_wn, y = predicted)) +
    geom_line(aes(group = pid), color = "gray", alpha = 0.5, size = 0.8) +
    geom_smooth(method = "lm", se = TRUE, color = "maroon", fill = "maroon", size = 1.5, alpha = 0.7) +
    labs(x = "", y = ylab) +
    annotate("text", x = x_pos, y = y_pos, label = label_b(beta), size = 6, hjust = 1) +
    annotate("text", x = x_pos, y = y_pos * 0.9, label = label_p(pval), size = 6, hjust = 1) +
    coord_cartesian(ylim = y_limit) +
    theme_minimal() +
    theme(
      axis.text = element_text(size = 20),
      axis.title = element_text(size = 22),
      axis.title.x = element_text(margin = margin(t = 0, b = -17), size = 23),
      panel.grid = element_blank(),
      axis.line = element_line(color = "black")
    )
}

# create plots
plot_crave <- plot_predicted(Final_df_crave, "Daily craving", beta_crave, p_crave, x_crave, y_crave)
plot_cigs <- plot_predicted(Final_df_cigs, "Daily cigarettes smoked", beta_cigs, p_cigs, x_cigs, y_cigs)

# no outlier version
Final_df_cigs_no_outlier <- Final_df_cigs %>% filter(pid != "GR293")
plot_cigs_no_outlier <- plot_predicted(Final_df_cigs_no_outlier, "Daily cigarettes smoked", beta_cigs, p_cigs, x_cigs, 40, y_limit = c(0, 40))

# combine plots
wrap_plots(plot_crave, plot_cigs, ncol = 2) +
  plot_annotation(
    caption = "Daily tobacco retail exposure (within-person)",
    theme = theme(plot.caption = element_text(size = 20, hjust = 0.8))
  )

# no outlier version
wrap_plots(plot_crave, plot_cigs_no_outlier, ncol = 2) +
  plot_annotation(
    caption = "Daily tobacco retail exposure (within-person)",
    theme = theme(plot.caption = element_text(size = 20, hjust = 0.8))
  )
```

## Final Descriptive Statistics (not grouped by pid)

```{r}
dim(Final_df)
# [1] 3747   21

psych::describe(Final_df$daily_average_crave_wins)
#    vars    n  mean    sd median trimmed   mad min max range skew kurtosis   se
# X1    1 3732 48.38 25.21   48.5   48.36 28.54   0 100   100 0.01    -0.77 0.41

psych::describe(Final_df$daily_cigs_wins)
#    vars    n  mean   sd median trimmed  mad min   max range skew kurtosis   se
# X1    1 3744 13.55 8.02     12   12.54 5.93   0 85.05 85.05  2.6    14.26 0.13

psych::describe(Final_df$daily_exposures_1000ft_100ft_wins)
#    vars    n mean   sd median trimmed   mad min   max range skew kurtosis   se
# X1    1 3747   37 34.9     27    30.9 22.24   0 309.5 309.5 2.48     9.02 0.57
```

# additional descriptives

## load geo observations

```{r}
Observations <- read_csv("/Volumes/cnlab/GeoRemote/Data/RetailerExposure/ConditionalBuffer/Baseline/1000ft_100ft_nExposures_nObservations.csv")

Final_df <- Final_df %>%
  left_join(Observations, by = c("pid", "day"))
```

# descriptives for geo observations

```{r}
psych::describe(Final_df$n_observations_per_day)
#    vars    n   mean     sd median trimmed    mad min  max range skew kurtosis   se
# X1    1 3747 315.34 338.64    220  262.43 255.01   1 4432  4431 2.84    17.26 5.53
```

## plot

```{r}
create_distribution_plot(Final_df, "n_observations_per_day", "Distribution of Daily Geo Obervations", "Geo Observations (1000 ft, 100 ft)", "Frequency")
```

## sumamarize by pid

```{r}
Final_df_by_pid <- Final_df %>%
  group_by(pid) %>%
  dplyr::summarize(
    n_observations_per_day = mean(n_observations_per_day, na.rm = TRUE),
    crave_summary = mean(daily_average_crave_wins, na.rm = TRUE),
    cigs_summary = mean(daily_cigs_wins, na.rm = TRUE),
    exposures_summary = mean(daily_exposures_1000ft_100ft_wins, na.rm = TRUE)
  )
```

# descriptives by pid

```{r}
psych::describe(Final_df_by_pid$n_observations_per_day)
#   vars   n   mean     sd median trimmed    mad  min     max   range skew kurtosis    se
# X1    1 273 311.33 296.17 235.79  268.36 264.43 6.33 2035.86 2029.52 1.75     5.05 17.93

psych::describe(Final_df_by_pid$crave_summary)
#    vars   n  mean    sd median trimmed   mad min  max range skew kurtosis   se
# X1    1 273 48.39 20.39  46.73   48.25 21.02   0 99.1  99.1 0.08    -0.54 1.23

psych::describe(Final_df_by_pid$cigs_summary)
#    vars   n  mean   sd median trimmed  mad  min   max range skew kurtosis   se
# X1    1 273 13.54 7.34  12.05   12.68 5.18 3.07 75.85 72.78 2.89     18.4 0.44

psych::describe(Final_df_by_pid$exposures_summary)
#    vars   n  mean    sd median trimmed   mad  min    max  range skew kurtosis   se
# X1    1 273 36.68 29.98  28.64   31.66 20.58 1.12 206.11 204.99 2.17     6.47 1.81
```

# plot by pid

```{r}
create_distribution_plot(Final_df_by_pid, "n_observations_per_day", "Distribution of Daily Geo Obervations", "Geo Observations (1000 ft, 100 ft)", "Frequency")
```

# Covariates {.tabset}

## Craving

### Age

```{r, echo=FALSE}
lme_craving_1000ft_100ft_age = 
  exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="age")

summary(lme_craving_1000ft_100ft_age)
get_lme_stats(lme_craving_1000ft_100ft_age)
intervals(lme_craving_1000ft_100ft_age, which = "fixed")
```

### Gender

```{r, echo=FALSE}
Final_df$gender <- relevel(Final_df$gender, ref = "Woman")

lme_craving_1000ft_100ft_gender <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="gender")

summary(lme_craving_1000ft_100ft_gender)
get_lme_stats(lme_craving_1000ft_100ft_gender)
intervals(lme_craving_1000ft_100ft_gender, which = "fixed")
```

### Race

```{r, echo=FALSE}
Final_df$race <- relevel(Final_df$race, ref = "White")

lme_craving_1000ft_100ft_race <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="race")

summary(lme_craving_1000ft_100ft_race)
get_lme_stats(lme_craving_1000ft_100ft_race)
intervals(lme_craving_1000ft_100ft_race, which = "fixed")
```

### Ethnicity

```{r, echo=FALSE}
lme_craving_1000ft_100ft_ethnicity <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="ethnicity")

summary(lme_craving_1000ft_100ft_ethnicity)
get_lme_stats(lme_craving_1000ft_100ft_ethnicity)
intervals(lme_craving_1000ft_100ft_ethnicity, which = "fixed")
```

### FTND

```{r, echo=FALSE}
lme_craving_1000ft_100ft_FTND <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="FTND_score")

summary(lme_craving_1000ft_100ft_FTND)
get_lme_stats(lme_craving_1000ft_100ft_FTND)
intervals(lme_craving_1000ft_100ft_FTND, which = "fixed")
```

### Smartphone type

```{r, echo=FALSE}
lme_craving_1000ft_100ft_platformType <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="platformType")

summary(lme_craving_1000ft_100ft_platformType)
get_lme_stats(lme_craving_1000ft_100ft_platformType)
intervals(lme_craving_1000ft_100ft_platformType, which = "fixed")
```

### State

```{r, echo=FALSE}
Final_df$State <- relevel(factor(Final_df$State), ref = "PA")

lme_craving_1000ft_100ft_state <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs="State")

summary(lme_craving_1000ft_100ft_state)
get_lme_stats(lme_craving_1000ft_100ft_state)
intervals(lme_craving_1000ft_100ft_state, which = "fixed")
```

### State and within-person exposure interaction

```{r}
exposure_model_1000ft_wins_state_interaction <- create_model_function_lme(
     model = "daily_exposures_1000ft_100ft_wins_wn * State + daily_exposures_1000ft_100ft_wins_bw + day",
     random_effects = ~ daily_exposures_1000ft_100ft_wins_wn | pid,
     correlation = corAR1(form = ~ day | pid),
     method = "REML")

lme_craving_1000ft_100ft_state_interaction <- 
exposure_model_1000ft_wins_state_interaction(
    Final_df, 
    dv= "daily_average_crave_wins")

summary(lme_craving_1000ft_100ft_state_interaction)
```

### All covariates

```{r, echo=FALSE}
lme_craving_1000ft_100ft_all_covariates <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_average_crave_wins",
    covs=c("age","gender", "race", "ethnicity", "FTND_score", "platformType", "State"))

summary(lme_craving_1000ft_100ft_all_covariates)
get_lme_stats(lme_craving_1000ft_100ft_all_covariates)
intervals(lme_craving_1000ft_100ft_all_covariates, which = "fixed")
```

# Smoking {.tabset}

### Age

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_age = 
  exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="age")

summary(lme_cigs_1000ft_100ft_age)
get_lme_stats(lme_cigs_1000ft_100ft_age)
intervals(lme_cigs_1000ft_100ft_age)
```

### Gender

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_gender <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="gender")

summary(lme_cigs_1000ft_100ft_gender)
get_lme_stats(lme_cigs_1000ft_100ft_gender)
intervals(lme_cigs_1000ft_100ft_gender)
```

### Race

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_race <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="race")

summary(lme_cigs_1000ft_100ft_race)
get_lme_stats(lme_cigs_1000ft_100ft_race)
intervals(lme_cigs_1000ft_100ft_race)
```

### Ethnicity

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_ethnicity <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="ethnicity")

summary(lme_cigs_1000ft_100ft_ethnicity)
get_lme_stats(lme_cigs_1000ft_100ft_ethnicity)
intervals(lme_cigs_1000ft_100ft_ethnicity)
```

### FTND

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_FTND <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="FTND_score")

summary(lme_cigs_1000ft_100ft_FTND)
get_lme_stats(lme_cigs_1000ft_100ft_FTND)
intervals(lme_cigs_1000ft_100ft_FTND)
```

### Smartphone type

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_platformType <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="platformType")

summary(lme_cigs_1000ft_100ft_platformType)
get_lme_stats(lme_cigs_1000ft_100ft_platformType)
intervals(lme_cigs_1000ft_100ft_platformType)
```

### State

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_state <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs="State")

summary(lme_cigs_1000ft_100ft_state)
get_lme_stats(lme_cigs_1000ft_100ft_state)
intervals(lme_cigs_1000ft_100ft_state)
```

### State and within-person exposure interaction

```{r}
lme_cigs_1000ft_100ft_state_interaction <- 
exposure_model_1000ft_wins_state_interaction(
    Final_df, 
    dv= "daily_cigs_wins")

summary(lme_craving_1000ft_100ft_state_interaction)
```

### All covariates

```{r, echo=FALSE}
lme_cigs_1000ft_100ft_all_covariates <- 
exposure_model_1000ft_wins(
    Final_df, 
    dv= "daily_cigs_wins",
    covs=c("age","gender", "race", "ethnicity", "FTND_score", "platformType", "State"))

summary(lme_cigs_1000ft_100ft_all_covariates)
get_lme_stats(lme_cigs_1000ft_100ft_all_covariates)
intervals(lme_cigs_1000ft_100ft_all_covariates)
```

# Data missingness {.tabset}

```{r}
summary_df <- Final_df %>%
  group_by(pid) %>%
  dplyr::summarise(
    days_with_data = n(),
    mean_daily_exposures_1000ft_100ft_wins = mean(daily_exposures_1000ft_100ft_wins, na.rm = TRUE),
    mean_daily_crave_wins = mean(daily_average_crave_wins, na.rm = TRUE),
    mean_daily_cigs_wins = mean(daily_cigs_wins, na.rm = TRUE),
    mean_daily_observations = mean(n_observations_per_day, na.rm = TRUE),
    mean_age = mean(age, na.rm = TRUE),
    mean_FTND_score = mean(FTND_score, na.rm = TRUE),
    gender = first(gender),
    ethnicity = first(ethnicity),
    race = first(race),
    platformType = first(platformType),
    State = first(State)
  )
```

## check ANOVA assumptions

## independence of observations

```{r}
anyDuplicated(summary_df$pid)
#[1] 0 - confirmed that all are independent
```

## days_with_data \~ gender

```{r}
anova_gender <- aov(days_with_data ~ gender, data = summary_df)
summary(anova_gender)

#              Df Sum Sq Mean Sq F value Pr(>F)
# gender        4    4.1   1.031   0.745  0.562
# Residuals   266  368.1   1.384               
# 2 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_gender))
# normality of residuals
qqnorm(rstandard(anova_gender))
qqline(rstandard(anova_gender), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_gender), residuals(anova_gender))
abline(h = 0, col = "red", lwd = 2)

# normality of residuals and homogeneity of variance are violated
# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(days_with_data ~ gender, data = summary_df)

# Kruskal-Wallis chi-squared = 5.3112, df = 4, p-value = 0.2568
```

## days_with_data \~ ethnicity

```{r}
anova_ethnicity <- aov(days_with_data ~ ethnicity, data = summary_df)
summary(anova_ethnicity)

#              Df Sum Sq Mean Sq F value Pr(>F)
# ethnicity     2    0.3  0.1575   0.113  0.893
# Residuals   268  371.9  1.3878               
# 2 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_ethnicity))
# normality of residuals
qqnorm(rstandard(anova_ethnicity))
qqline(rstandard(anova_ethnicity), col = "red", lwd = 2)
# homogeneity
plot(fitted(anova_ethnicity), residuals(anova_ethnicity))
abline(h = 0, col = "red", lwd = 2)

# normality of residuals and homogeneity of variance are violated
# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(days_with_data ~ ethnicity, data = summary_df)

# Kruskal-Wallis chi-squared = 0.29155, df = 2, p-value = 0.8644
```

## days_with_data \~ race

```{r}
anova_race <- aov(days_with_data ~ race, data = summary_df)
summary(anova_race)

#              Df Sum Sq Mean Sq F value Pr(>F)
# race          6    3.0  0.4921   0.351  0.909
# Residuals   263  369.2  1.4039               
# 3 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_race))
# normality of residuals
qqnorm(rstandard(anova_race))
qqline(rstandard(anova_race), col = "red", lwd = 2)
# homogeneity
plot(fitted(anova_race), residuals(anova_race))
abline(h = 0, col = "red", lwd = 2)

# normality of residuals and homogeneity of variance are violated
# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(days_with_data ~ race, data = summary_df)

# Kruskal-Wallis chi-squared = 2.6715, df = 6, p-value = 0.8488
```

## days_with_data \~ platformType

```{r}
anova_platformType <- aov(days_with_data ~ platformType, data = summary_df)
summary(anova_platformType)
TukeyHSD(anova_platformType)

#               Df Sum Sq Mean Sq F value  Pr(>F)   
# platformType   1    9.8   9.848   7.362 0.00709 **
# Residuals    271  362.5   1.338                   
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
#   Tukey multiple comparisons of means
#     95% family-wise confidence level
# 
# Fit: aov(formula = days_with_data ~ platformType, data = summary_df)
# 
# $platformType
#                   diff        lwr        upr     p adj
# IOS-ANDROID -0.3823401 -0.6597721 -0.1049082 0.0070901

platform_means <- summary_df %>%
  group_by(platformType) %>%
  summarise(mean_days = mean(days_with_data, na.rm = TRUE))

print(platform_means)
# ANDROID	13.89474			
# IOS	13.51240	

# normality of residuals
hist(residuals(anova_platformType))
# normality of residuals
qqnorm(rstandard(anova_platformType))
qqline(rstandard(anova_platformType), col = "red", lwd = 2)
# homogeneity
plot(fitted(anova_platformType), residuals(anova_platformType))
abline(h = 0, col = "red", lwd = 2)

# normality of residuals and homogeneity of variance are violated
# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(days_with_data ~ platformType, data = summary_df)
# Kruskal-Wallis chi-squared = 8.7716, df = 1, p-value = 0.00306
```

## days_with_data \~ state

```{r}
anova_state <- aov(days_with_data ~ State, data = summary_df)
summary(anova_state)

#              Df Sum Sq Mean Sq F value Pr(>F)
# State         2    0.8  0.4162   0.302  0.739
# Residuals   270  371.6  1.3762    

# normality of residuals
hist(residuals(anova_state))
# normality of residuals
qqnorm(rstandard(anova_state))
qqline(rstandard(anova_state), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_state), residuals(anova_state))
abline(h = 0, col = "red", lwd = 2)

# normality of residuals and homogeneity of variance are violated
# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(days_with_data ~ State, data = summary_df)

# Kruskal-Wallis chi-squared = 0.14725, df = 2, p-value = 0.929
```

## days_with_data \~ age

```{r}
regression_age <- lm(days_with_data ~ mean_age, data = summary_df)
summary(regression_age)

# Call:
# lm(formula = days_with_data ~ mean_age, data = summary_df)
# 
# Residuals:
#     Min      1Q  Median      3Q     Max 
# -8.7647  0.2112  0.2715  0.3136  0.4040 
# 
# Coefficients:
#              Estimate Std. Error t value Pr(>|t|)    
# (Intercept) 13.469513   0.291111  46.269   <2e-16 ***
# mean_age     0.006023   0.006650   0.906    0.366    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Residual standard error: 1.17 on 271 degrees of freedom
# Multiple R-squared:  0.003018,	Adjusted R-squared:  -0.0006605 
# F-statistic: 0.8205 on 1 and 271 DF,  p-value: 0.3658
```

## days_with_data \~ FTND_score

```{r}
regression_FTND_score <- lm(days_with_data ~ mean_FTND_score, data = summary_df)
summary(regression_FTND_score)

# Call:
# lm(formula = days_with_data ~ mean_FTND_score, data = summary_df)
# 
# Residuals:
#     Min      1Q  Median      3Q     Max 
# -8.7278  0.2722  0.2769  0.2816  0.2886 
# 
# Coefficients:
#                  Estimate Std. Error t value Pr(>|t|)    
# (Intercept)     13.709008   0.219778  62.377   <2e-16 ***
# mean_FTND_score  0.002352   0.036975   0.064    0.949    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Residual standard error: 1.178 on 268 degrees of freedom
#   (3 observations deleted due to missingness)
# Multiple R-squared:  1.51e-05,	Adjusted R-squared:  -0.003716 
# F-statistic: 0.004046 on 1 and 268 DF,  p-value: 0.9493
```

## mean_daily_observations \~ gender

```{r}
anova_gender_obs <- aov(mean_daily_observations ~ gender, data = summary_df)
summary(anova_gender_obs)
TukeyHSD(anova_gender_obs)

#              Df   Sum Sq Mean Sq F value Pr(>F)  
# gender        4   905361  226340   2.636 0.0345 *
# Residuals   266 22842632   85875                 
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 2 observations deleted due to missingness
#   Tukey multiple comparisons of means
#     95% family-wise confidence level
# 
# Fit: aov(formula = mean_daily_observations ~ gender, data = summary_df)
# 
# $gender
#                                diff       lwr        upr     p adj
# Woman-Man                 -94.24753 -194.8771    6.38199 0.0784703
# Non-binary-Man           -165.19237 -502.5422  172.15750 0.6633370
# Genderqueer-Man           145.14097 -429.0911  719.37305 0.9576216
# Gender fluid-Man          374.49811 -433.9874 1182.98362 0.7084945
# Non-binary-Woman          -70.94484 -405.9955  264.10580 0.9777058
# Genderqueer-Woman         239.38850 -333.4959  812.27286 0.7808924
# Gender fluid-Woman        468.74564 -338.7832 1276.27448 0.5023467
# Genderqueer-Non-binary    310.33333 -346.8387  967.50539 0.6933031
# Gender fluid-Non-binary   539.69048 -329.6664 1409.04740 0.4325762
# Gender fluid-Genderqueer  229.35714 -756.4009 1215.11523 0.9685293

# normality of residuals
hist(residuals(anova_gender_obs))
# normality of residuals
qqnorm(rstandard(anova_gender_obs))
qqline(rstandard(anova_gender_obs), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_gender_obs), residuals(anova_gender_obs))
abline(h = 0, col = "red", lwd = 2)

# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(mean_daily_observations ~ gender, data = summary_df)

# Kruskal-Wallis chi-squared = 15.97, df = 4, p-value = 0.003059

wilcox_gender <- pairwise.wilcox.test(summary_df$mean_daily_observations,
                     summary_df$gender,
                     p.adjust.method = "bonferroni")

#              Man   Woman Non-binary Genderqueer
# Woman        0.011 -     -          -          
# Non-binary   0.917 1.000 -          -          
# Genderqueer  1.000 1.000 1.000      -          
# Gender fluid 1.000 1.000 1.000      1.000     

summary_df %>%
  dplyr::group_by(gender) %>%
  dplyr::summarise(
    mean_observations = mean(mean_daily_observations, na.rm = TRUE),
    n = dplyr::n()
  )

#   gender       mean_observations     n
#   <fct>                    <dbl> <int>
# 1 Man                      366.71617    111
# 2 Woman                    272.46864    151
# 3 Non-binary               201.52381      6
# 4 Genderqueer              511.85714      2
# 5 Gender fluid             741.21429      1
# 6 NA                        85.21429    2
```

## mean_daily_observations \~ ethnicity

```{r}
anova_ethnicity_obs <- aov(mean_daily_observations ~ ethnicity, data = summary_df)
summary(anova_ethnicity_obs)

#              Df   Sum Sq Mean Sq F value Pr(>F)
# ethnicity     2     4728    2364   0.027  0.974
# Residuals   268 23743265   88594               
# 2 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_ethnicity_obs))
# normality of residuals
qqnorm(rstandard(anova_ethnicity_obs))
qqline(rstandard(anova_ethnicity_obs), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_ethnicity_obs), residuals(anova_ethnicity_obs))
abline(h = 0, col = "red", lwd = 2)

# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(mean_daily_observations ~ ethnicity, data = summary_df)

# Kruskal-Wallis chi-squared = 0.2147, df = 2, p-value = 0.8982
```

## mean_daily_observations \~ race

```{r}
anova_race_obs <- aov(mean_daily_observations ~ race, data = summary_df)
summary(anova_race_obs)

#              Df   Sum Sq Mean Sq F value Pr(>F)
# race          6   499274   83212   0.948  0.461
# Residuals   263 23092114   87803               
# 3 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_race_obs))
# normality of residuals
qqnorm(rstandard(anova_race_obs))
qqline(rstandard(anova_race_obs), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_race_obs), residuals(anova_race_obs))
abline(h = 0, col = "red", lwd = 2)

# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(mean_daily_observations ~ race, data = summary_df)

# Kruskal-Wallis chi-squared = 4.6285, df = 6, p-value = 0.5923
```

## mean_daily_observations \~ platformType

```{r}
anova_platformType_obs <- aov(mean_daily_observations ~ platformType, data = summary_df)
summary(anova_platformType_obs)
TukeyHSD(anova_platformType_obs)

#               Df   Sum Sq  Mean Sq F value Pr(>F)    
# platformType   1 11321025 11321025   244.7 <2e-16 ***
# Residuals    271 12538391    46267                   
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
#   Tukey multiple comparisons of means
#     95% family-wise confidence level
# 
# Fit: aov(formula = mean_daily_observations ~ platformType, data = summary_df)
# 
# $platformType
#                diff       lwr       upr p adj
# IOS-ANDROID -409.93 -461.5235 -358.3365     0

platform_means_obs <- summary_df %>%
  group_by(platformType) %>%
  summarise(mean_obs = mean(mean_daily_observations, na.rm = TRUE))

print(platform_means_obs)
# ANDROID	493.01939			
# IOS	83.08937

# normality of residuals
hist(residuals(anova_platformType_obs))
# normality of residuals
qqnorm(rstandard(anova_platformType_obs))
qqline(rstandard(anova_platformType_obs), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_platformType_obs), residuals(anova_platformType_obs))
abline(h = 0, col = "red", lwd = 2)

# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(mean_daily_observations ~ platformType, data = summary_df)

# Kruskal-Wallis chi-squared = 183.94, df = 1, p-value < 2.2e-16
```

## mean_daily_observations \~ state

```{r}
anova_state_obs <- aov(mean_daily_observations ~ State, data = summary_df)
summary(anova_race_obs)

#              Df   Sum Sq Mean Sq F value Pr(>F)
# race          6   499274   83212   0.948  0.461
# Residuals   263 23092114   87803               
# 3 observations deleted due to missingness

# normality of residuals
hist(residuals(anova_state_obs))
# normality of residuals
qqnorm(rstandard(anova_state_obs))
qqline(rstandard(anova_state_obs), col = "red", lwd = 2)
# homogeneity of variance
plot(fitted(anova_state_obs), residuals(anova_state_obs))
abline(h = 0, col = "red", lwd = 2)

# using the Kruskal-Wallis test which is a non-parametric test used when ANOVA assumptions are violated.
kruskal.test(mean_daily_observations ~ State, data = summary_df)

# Kruskal-Wallis chi-squared = 2.3523, df = 2, p-value = 0.3085
```

## mean_daily_observations \~ age

```{r}
regression_age_obs <- lm(mean_daily_observations ~ mean_age, data = summary_df)
summary(regression_age_obs)

# Call:
# lm(formula = mean_daily_observations ~ mean_age, data = summary_df)
# 
# Residuals:
#     Min      1Q  Median      3Q     Max 
# -313.40 -242.50  -77.33  135.95 1732.13 
# 
# Coefficients:
#             Estimate Std. Error t value Pr(>|t|)    
# (Intercept) 280.4763    73.7723   3.802 0.000177 ***
# mean_age      0.7266     1.6852   0.431 0.666685    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Residual standard error: 296.6 on 271 degrees of freedom
# Multiple R-squared:  0.0006855,	Adjusted R-squared:  -0.003002 
# F-statistic: 0.1859 on 1 and 271 DF,  p-value: 0.6667
```

## mean_daily_observations \~ FTND_score

```{r}
regression_FTND_score_obs <- lm(mean_daily_observations ~ mean_FTND_score, data = summary_df)
summary(regression_FTND_score_obs)

# Call:
# lm(formula = mean_daily_observations ~ mean_FTND_score, data = summary_df)
# 
# Residuals:
#     Min      1Q  Median      3Q     Max 
# -337.01 -234.74  -66.27  154.46 1702.87 
# 
# Coefficients:
#                 Estimate Std. Error t value Pr(>|t|)    
# (Intercept)      231.691     55.268   4.192 3.76e-05 ***
# mean_FTND_score   14.472      9.298   1.556    0.121    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Residual standard error: 296.3 on 268 degrees of freedom
#   (3 observations deleted due to missingness)
# Multiple R-squared:  0.008957,	Adjusted R-squared:  0.005259 
# F-statistic: 2.422 on 1 and 268 DF,  p-value: 0.1208
```
