---
title: "aim_3_preprocessing"
author: "Ben Muzekari"
date: "2025-10-09"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # Show code by default
  message = FALSE,  # Suppress messages by default
  warning = FALSE   # Suppress warnings by default
)
```

# Setup {.tabset}
## Set scripts directory
```{r, echo=FALSE}
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

## Load analysis functions
```{r}
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis2.r"))
```

## Load baseline data
## Survey
```{r}
EMA_Baseline_Covariates_Distinct = load_ema_with_covs(Type="Baseline",
                                                      ema_variables = c("day", "Type", "daily_average_crave", "daily_cigs", "daily_stress", "daily_average_pos", "daily_average_neg"),
                        redcap_variables = c("pid","age","gender","ethnicity","race","cond", "intervention_complete", "num_receipts")) %>%
  add_survey_measure("FTND", session=1) %>%
  add_descriptives(vars="platformType") %>%
  distinct()
```

```{r}
# load in the qualtrics data
source(file.path(scripts_directory, "Utility Scripts/geo_qualtrics.r"))
qualtrics <- load_qualtrics_survey_measures()
```

```{r}
qualtrics_subset <- qualtrics %>%
  select(pid, bhv_01_new_1_1_1, bhv_01_new_1_1_1, sm_session) %>%
  filter(sm_session == 1)
```

```{r}
EMA_Baseline_Covariates_Distinct <- EMA_Baseline_Covariates_Distinct %>%
  left_join(qualtrics_subset %>% select(pid, bhv_01_new_1_1_1),
            by = "pid")
```

# Geo
```{r}
geo_data_baseline_exposures = load_geo_exposures(Type="Baseline")
```

# Join survey and geo
```{r}
EMA_Baseline_all <- left_join(EMA_Baseline_Covariates_Distinct, geo_data_baseline_exposures, by = c("pid", "day"))
```


```{r}
Baseline_Observations <- read_csv("/Volumes/cnlab/GeoRemote/Data/RetailerExposure/ConditionalBuffer/Baseline/1000ft_100ft_nExposures_nObservations.csv")
```

```{r}
EMA_Baseline_all <- left_join(EMA_Baseline_all, Baseline_Observations, by = c("pid", "day"))
```


## Load intervention data
## Survey
```{r}
EMA_Intervention_Covariates_Distinct = load_ema_with_covs(Type="Intervention",
                                                      ema_variables = c("day", "Type", "daily_average_crave", "daily_cigs", "daily_stress", "daily_average_pos", "daily_average_neg"),
                        redcap_variables = c("pid","age","gender","ethnicity","race","cond", "intervention_complete")) %>%
  add_survey_measure("FTND", session=1) %>%
  add_descriptives(vars="platformType") %>%
  distinct()
```

# Geo
```{r}
geo_data_intervention_exposures = load_geo_exposures(Type="Intervention")
```

# Join survey and geo
```{r}
EMA_Intervention_all <- left_join(EMA_Intervention_Covariates_Distinct, geo_data_intervention_exposures, by = c("pid", "day"))
```

```{r}
Intervention_Observations <- read_csv("/Volumes/cnlab/GeoRemote/Data/RetailerExposure/ConditionalBuffer/Intervention/1000ft_100ft_nExposures_nObservations.csv")
```

```{r}
EMA_Intervention_all <- left_join(EMA_Intervention_all, Intervention_Observations, by = c("pid", "day"))
```


## combine baseline and intervention data
```{r}
EMA_combined <- bind_rows(
  EMA_Baseline_all,
  EMA_Intervention_all
)
```

# Recode condition variable, set as factor, and set control group as the reference
```{r, echo=FALSE}
EMA_combined <- EMA_combined %>%
  mutate(
    cond = case_when(
      cond == 1 ~ "Low",
      cond == 2 ~ "High",
      cond == 3 ~ "Control",
      TRUE ~ as.character(cond) 
    ),
    cond = factor(cond, levels = c("Control", "Low", "High"))
  )
```

# Rename Type to phase
```{r}
EMA_combined <- EMA_combined %>%
  rename(phase = Type)
```

# get participant count and check how many participants are assigned a condition
```{r}
length(unique(EMA_combined$pid))
# [1] 302

EMA_combined %>%
  filter(!is.na(cond)) %>%
  summarise(n_unique_pid = n_distinct(pid))
# 288	
```

# drop participants who are not assigned a condition
```{r}
EMA_combined <- EMA_combined %>%
  filter(!is.na(cond))

print(length(unique(EMA_combined$pid)))
#[1] 288
```

# Remove 6 ppts who were not actually assigned to a condition
```{r}
pids_to_remove <- c("GR095", "GR153", "GR242", "GR258", "GR312", "GR316")

EMA_combined <- EMA_combined %>%
  filter(!pid %in% pids_to_remove)

print(length(unique(EMA_combined$pid)))
#[1] 282
```

# Add in geo data so we look at alternative metrics of exposure and mobility
```{r}
# baseline
geo_data_stay_events_baseline <- read_csv("/Volumes/cnlab/GeoRemote/Data/Geodata/clean/stay_events/baseline/stay_events_baseline.csv")
```

```{r}
# load US statess
all_states <- states(cb = FALSE) 

# convert df to sf object and match coordinate reference system
gps_sf_baseline <- geo_data_stay_events_baseline %>%                     
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(st_crs(all_states))

# spatial join all states
gps_with_states_baseline <- st_join(
  gps_sf_baseline,
  all_states["STUSPS"],
  join = st_within   
)

# define study states
study_states <- c("PA", "NJ", "DE")

# add col that tells us whether the point is within the study area
gps_with_states_baseline <- gps_with_states_baseline %>%
  mutate(in_study_area = STUSPS %in% study_states)    
```

```{r}
# add col that tells us whether the participant has at least point is outside the study area by day
gps_with_states_baseline <- gps_with_states_baseline %>%
  group_by(pid, day) %>%
  mutate(
    at_least_point_outside_by_day = any(!in_study_area | is.na(in_study_area))
  ) %>%
  ungroup()
```

```{r}
# add col that tells us percent of points inside study area by pid and by day
gps_with_states_baseline <- gps_with_states_baseline %>%
  group_by(pid, day) %>%
  mutate(
    at_least_point_outside_by_day = any(!in_study_area | is.na(in_study_area)),
    percent_of_points_inside = 100 * mean(in_study_area, na.rm = TRUE)
  ) %>%
  ungroup()
```

now let's get counts consecutive days when participants are entirely out of the study area
```{r}
# use distinct to avoid duplicates
day_flags_zero <- gps_with_states_baseline %>%
  distinct(pid, day, percent_of_points_inside)
```

```{r}
# define all points outside
day_flags_zero <- day_flags_zero %>%
  mutate(all_points_outside = percent_of_points_inside == 0)
```

```{r}
# define function to calculate streak 
calc_streak <- function(x) {
  streak <- integer(length(x))
  count <- 0L
  for (i in seq_along(x)) {
    if (isTRUE(x[i])) {
      count <- count + 1L
      streak[i] <- count
    } else {
      count <- 0L
      streak[i] <- 0L
    }
  }
  streak
}

# apply function
day_flags_zero <- day_flags_zero %>%
  arrange(pid, day) %>%
  group_by(pid) %>%
  mutate(
    consec_all_outside_days = calc_streak(all_points_outside)
  ) %>%
  ungroup()
```

```{r}
# join back to main df
gps_with_states_baseline <- gps_with_states_baseline %>%
  left_join(
    day_flags_zero %>% select(pid, day, all_points_outside, consec_all_outside_days),
    by = c("pid", "day")
  )
```

```{r}
# get distance traveled including all points
gps_with_states_baseline <- gps_with_states_baseline %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 125 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 125) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_125_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 100 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 100) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_100_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 75 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 75) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_75_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 50 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 50) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_50_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 25 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 25) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_25_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area
gps_with_states_baseline <- gps_with_states_baseline %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 125 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 125) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_125_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 100 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 100) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_100_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 75 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 75) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_75_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 50 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 50) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_50_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 25 mph
gps_with_states_baseline <- gps_with_states_baseline %>%
  filter(is.na(lagmph) | lagmph < 25) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_25_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# create day-level summary df
day_level_geo_df_baseline <- gps_with_states_baseline %>%
  distinct(pid, day, at_least_point_outside_by_day, percent_of_points_inside,
           distance_traveled_day_miles_all_points_included,
           distance_traveled_day_miles_all_points_included_under_125_mph,
           distance_traveled_day_miles_all_points_included_under_100_mph,
           distance_traveled_day_miles_all_points_included_under_75_mph,
           distance_traveled_day_miles_all_points_included_under_50_mph,
           distance_traveled_day_miles_all_points_included_under_25_mph,
           distance_traveled_day_miles_only_points_in_study_area,
           distance_traveled_day_miles_only_points_in_study_area_under_125_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_100_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_75_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_50_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_25_mph)

day_level_geo_df_baseline <- day_level_geo_df_baseline %>%
  mutate(phase = "Baseline")
```

# Let's do the same, but for intervention
```{r}
# intervention
geo_data_stay_events_intervention <- read_csv("/Volumes/cnlab/GeoRemote/Data/Geodata/clean/stay_events/intervention/stay_events_intervention.csv")
```

```{r}
# convert df to sf object and match coordinate reference system
gps_sf_intervention <- geo_data_stay_events_intervention %>%                     
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(st_crs(all_states))

# spatial join all states
gps_with_states_intervention <- st_join(
  gps_sf_intervention,
  all_states["STUSPS"],
  join = st_within   
)

# add col that tells us whether the point is within the study area
gps_with_states_intervention <- gps_with_states_intervention %>%
  mutate(in_study_area = STUSPS %in% study_states)    
```

```{r}
# add col that tells us whether the participant has at least point is outside the study area by day
gps_with_states_intervention <- gps_with_states_intervention %>%
  group_by(pid, day) %>%
  mutate(
    at_least_point_outside_by_day = any(!in_study_area | is.na(in_study_area))
  ) %>%
  ungroup()
```

```{r}
# add col that tells us percent of points inside study area by pid and by day
gps_with_states_intervention <- gps_with_states_intervention %>%
  group_by(pid, day) %>%
  mutate(
    at_least_point_outside_by_day = any(!in_study_area | is.na(in_study_area)),
    percent_of_points_inside = 100 * mean(in_study_area, na.rm = TRUE)
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points
gps_with_states_intervention <- gps_with_states_intervention %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 125 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 125) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_125_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 100 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 100) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_100_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 75 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 75) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_75_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 50 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 50) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_50_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including all points under 25 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 25) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_all_points_included_under_25_mph =
      sum(lagDist_ft, na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area
gps_with_states_intervention <- gps_with_states_intervention %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 125 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 125) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_125_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 100 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 100) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_100_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 75 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 75) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_75_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 50 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 50) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_50_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# get distance traveled including only points in study area under 25 mph
gps_with_states_intervention <- gps_with_states_intervention %>%
  filter(is.na(lagmph) | lagmph < 25) %>%
  group_by(pid, day) %>%
  mutate(
    distance_traveled_day_miles_only_points_in_study_area_under_25_mph =
      sum(lagDist_ft * if_else(in_study_area %in% TRUE, 1, 0), na.rm = TRUE) / 5280
  ) %>%
  ungroup()
```

```{r}
# create day-level summary df
day_level_geo_df_intervention <- gps_with_states_intervention %>%
  distinct(pid, day, at_least_point_outside_by_day, percent_of_points_inside,
           distance_traveled_day_miles_all_points_included,
           distance_traveled_day_miles_all_points_included_under_125_mph,
           distance_traveled_day_miles_all_points_included_under_100_mph,
           distance_traveled_day_miles_all_points_included_under_75_mph,
           distance_traveled_day_miles_all_points_included_under_50_mph,
           distance_traveled_day_miles_all_points_included_under_25_mph,
           distance_traveled_day_miles_only_points_in_study_area,
           distance_traveled_day_miles_only_points_in_study_area_under_125_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_100_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_75_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_50_mph,
           distance_traveled_day_miles_only_points_in_study_area_under_25_mph)

day_level_geo_df_intervention <- day_level_geo_df_intervention %>%
  mutate(phase = "Intervention")
```

```{r}
# combine
day_level_geo_df <- bind_rows(
  day_level_geo_df_baseline,
  day_level_geo_df_intervention
)
```

```{r}
# join ema and geo data
EMA_geo_combined <- EMA_combined %>%
  left_join(
    day_level_geo_df,
    by = c("pid", "day", "phase")
  )
```

# write out df
```{r}
write.csv(EMA_geo_combined, "/Volumes/cnlab/GeoRemote/Output/aim_3/EMA_geo_combined.csv", row.names = FALSE)
```

