---
title: "Clinical_Trials_EMA_Analysis"
author: "Ben Muzekari"
date: "2025-06-05"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # Show code by default
  message = FALSE,  # Suppress messages by default
  warning = FALSE   # Suppress warnings by default
)
```

# Setup {.tabset}
```{r, echo=FALSE}
# Set scripts directory
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}

# load analysis functions
source(file.path(scripts_directory, 
                 "Utility Scripts", 
                 "geo_analysis.r"))
```

## load GR data
```{r}
# EMA data
source(file.path(scripts_directory, "Utility Scripts/geo_lifedata.r"))
GR_df = load_lifedata(format="wide")

# meta data
GR_meta <- read_csv("/Volumes/cnlab/GeoRemote/Data/admin/meta_df.csv")
```

# merge GR data
```{r}
GR_df <- GR_df %>%
  full_join(GR_meta, by = "pid")
```

## recode condition variable
```{r}
# Recode condition variable, set as factor, and set control group as the reference
GR_df <- GR_df %>%
  mutate(
    cond = case_when(
      cond == 1 ~ "Low",
      cond == 2 ~ "High",
      cond == 3 ~ "Control",
      TRUE ~ as.character(cond)
    )
  )
```

```{r}
source(file.path(scripts_directory, "Utility Scripts/geo_redcap.r"))
redcap <- load_redcap()

redcap_vars <-redcap[, c("pid", "intervention_complete")]
```

## Load GS data
```{r}
# EMA data
GS_ema <- read_csv("/Volumes/cnlab/GeoScan/LifeData/EMA/processed_geoscan_lifedata.csv")

# Condition assignment data
GS_cond <- read_csv("/Volumes/cnlab/GeoScan/ClinicalTrials/GeoScanR01-FinalStatusNC_DATA.csv")
```

# merge GS data
```{r}
GS_df <- GS_ema %>%
  full_join(GS_cond %>% select(pid, cond, intervention_complete), by = "pid")
```

# rename craving col to match GR_df
```{r}
GS_df <- GS_df %>%
  rename(
    daily_average_crave = crave_avg,
    Type = type
  )
```

```{r}
GR_df <- merge(redcap, GR_df, by = "pid", all = TRUE)
```

```{r}
GR_df <- GR_df %>%
  rename(cond = cond.y)
```

# combine GR and GS
```{r}
GS_df <- GS_df %>% mutate(across(everything(), as.character))
GR_df <- GR_df %>% mutate(across(everything(), as.character))

combined_df <- bind_rows(GS_df, GR_df)
```

# get distinct rows by pid, day, and type
```{r}
Final_df <- combined_df %>%
  distinct(pid, day, Type, .keep_all = TRUE)
```

# remove ppts
```{r}
Final_df <- Final_df %>%
  filter(!pid %in% c("GS000", "GR095", "GR153", "GR242", "GR258", "GR312", "GR316"))
```

# change n/a cond assignment to "Not Assigned"
```{r}
Final_df <- Final_df %>%
  mutate(cond = ifelse(is.na(cond), "Not Assigned", cond))
```

# get averages
```{r}
pid_averages <- Final_df %>%
  mutate(
    daily_average_crave = as.numeric(as.character(daily_average_crave)),
    daily_cigs = as.numeric(as.character(daily_cigs)),
    Protocol = case_when(
      startsWith(pid, "GS") ~ "GS",
      startsWith(pid, "GR") ~ "GR",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(pid, Type) %>%
  summarise(
    avg_crave = mean(daily_average_crave, na.rm = TRUE),
    avg_cigs = mean(daily_cigs, na.rm = TRUE),
    cond = first(cond),
    Protocol = first(Protocol),
    s2_complete = first(s2_complete),
    .groups = "drop"
  )
```

# get counts
```{r}
pid_averages %>%
  distinct(pid, Protocol, cond) %>%
  count(Protocol, cond)
```

# plot distributions
```{r}
create_distribution_plot(pid_averages, "avg_crave", "Distribution of Craving", "Average Craving", "Frequency")
create_distribution_plot(pid_averages, "avg_cigs", "Distribution of Cigarettes", "Average Cigarettes", "Frequency")
```

# get averages
```{r}
group_averages <- pid_averages %>%
  group_by(Type, Protocol, cond) %>%
  summarise(
    n = n(),
    mean_crave = mean(avg_crave, na.rm = TRUE),
    sd_crave = sd(avg_crave, na.rm = TRUE),
    mean_cigs = mean(avg_cigs, na.rm = TRUE),
    sd_cigs = sd(avg_cigs, na.rm = TRUE),
    .groups = "drop"
  )

print(group_averages)

group_averages_protocol <- pid_averages %>%
  group_by(Type, Protocol) %>%
  summarise(
    n = n(),
    mean_crave = mean(avg_crave, na.rm = TRUE),
    sd_crave = sd(avg_crave, na.rm = TRUE),
    mean_cigs = mean(avg_cigs, na.rm = TRUE),
    sd_cigs = sd(avg_cigs, na.rm = TRUE),
    .groups = "drop"
  )

print(group_averages_protocol)

group_averages_cond <- pid_averages %>%
  group_by(Type, cond) %>%
  summarise(
    n = n(),
    mean_crave = mean(avg_crave, na.rm = TRUE),
    sd_crave = sd(avg_crave, na.rm = TRUE),
    mean_cigs = mean(avg_cigs, na.rm = TRUE),
    sd_cigs = sd(avg_cigs, na.rm = TRUE),
    .groups = "drop"
  )

print(group_averages_cond)

group_averages_type <- pid_averages %>%
  group_by(Type) %>%
  summarise(
    n = n(),
    mean_crave = mean(avg_crave, na.rm = TRUE),
    sd_crave = sd(avg_crave, na.rm = TRUE),
    mean_cigs = mean(avg_cigs, na.rm = TRUE),
    sd_cigs = sd(avg_cigs, na.rm = TRUE),
    .groups = "drop"
  )

print(group_averages_type)
```

# models

# remove not assigned ppts
```{r}
pid_averages_model <- pid_averages %>%
  filter(cond != "Not Assigned")
```

# set high exposure as reference group
```{r}
pid_averages_model <- pid_averages_model %>%
  mutate(cond = factor(cond, levels = c("High", "Low", "Control")))
```

## intent to treat
# crave
```{r}
crave_model <- lme(
  avg_crave ~ Type * cond,
  random = ~Type | pid,
  data = pid_averages_model
)

summary(crave_model)
```



## cigs
```{r}
cigs_model <- lme(
  avg_cigs ~ Type * cond,
  random = ~Type | pid,
  data = pid_averages_model
)

summary(cigs_model)
```

## completed all 20 visits
```{r}
pid_averages_complete <- Final_df %>%
  mutate(
    daily_average_crave = as.numeric(as.character(daily_average_crave)),
    daily_cigs = as.numeric(as.character(daily_cigs)),
    Protocol = case_when(
      startsWith(pid, "GS") ~ "GS",
      startsWith(pid, "GR") ~ "GR",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(pid, Type) %>%
  summarise(
    avg_crave = mean(daily_average_crave, na.rm = TRUE),
    avg_cigs = mean(daily_cigs, na.rm = TRUE),
    cond = first(cond),
    Protocol = first(Protocol),
    intervention_complete = first(intervention_complete),
    .groups = "drop"
  )
```

```{r}
pid_averages_complete <- pid_averages_complete %>%
  filter(intervention_complete == 1)
```

# remove not assigned ppts
```{r}
pid_averages_complete_model <- pid_averages_complete %>%
  filter(cond != "Not Assigned")
```

# set high exposure as reference group
```{r}
pid_averages_complete_model <- pid_averages_complete_model %>%
  mutate(cond = factor(cond, levels = c("High", "Low", "Control")))
```

```{r}
crave_model <- lme(
  avg_crave ~ Type * cond,
  random = ~Type | pid,
  data = pid_averages_complete_model
)

summary(crave_model)
```

## cigs
```{r}
cigs_model <- lme(
  avg_cigs ~ Type * cond,
  random = ~Type | pid,
  data = pid_averages_complete_model
)

summary(cigs_model)
```




