# Setup {.tabset}
connect to forticlient (if it not connecting it is waiting for dual athentification), then connect to server smb://asc.upenn.edu/cnlab (short cut is Cmd+K in finder)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999) #add to top of script to get rid of scientific notification 
```

## Set scripts directory
```{r, echo=FALSE}
if ("Scripts" %in% unlist(strsplit(normalizePath("."), "/"))) {
  scripts_directory = paste(unlist(strsplit(normalizePath("."), "/"))[1:which(unlist(strsplit(normalizePath("."), "/"))=="Scripts")],collapse="/")
} else {
  print("Select any file within Scripts to set up the path")
  temp = file.choose()
  scripts_directory = paste(unlist(strsplit(temp, "/"))[1:which(unlist(strsplit(temp, "/"))=="Scripts")],collapse="/")
}
```

## Load analysis functions
```{r}
source(file.path(scripts_directory, 
                 "Utility Scripts",
                 "geo_lifedata.r"))

source(file.path(scripts_directory, 
                 "Utility Scripts",
                 "geo_analysis2.r"))

#error goes away if I run "geo_lifedata.r" first

```

# Load in Data
Load ema
```{r}
ema = load_lifedata()
ema_wide = load_lifedata(format = "wide") 
```

```{r}
head(ema_wide)
```


## Load EMA, and covariate data
trans
1: Yes
 5: No
 4: Prefer not to say

sexuality
1: Straight; 2: Lesbian or gay; 3: Bisexual; 4: Prefer to self-describe; 5: I don't know the answer; 7: Prefer not to say

Ethnicity
Latine 1: Yes; 0: No; 2: Prefer not to say

ses_level - People talk about social classes such as the poor, the working class, the middle class, the upper-middle class, and the upper class. Which of these classes would you say you belong to?
1: Poor; 2: Working Class; 3: Middle Class; 4: Upper-Middle Class; 5: Upper Class

income_individual & income_household
1: Less than $5,000
2: $5,000 through $11,999
 3: $12,000 through $15,999
 4: $16,000 through $24,999
 5: $25,000 through $34,999
 6: $35,000 through $49,999
 7: $50,000 through $74,999
 8: $75,000 through $99,999
 9: $100,000 and greater
 10: I don't know
 11: Prefer not to say

school - What is the highest degree or level of school you have completed? If currently enrolled, indicate highest degree completed.
1: No formal education
 2: Less than high school
 3: High school graduate (diploma)
 4: High school graduate (GED)
 5: Some college (1-4 years, no degree)
 6: Associate's degree (including occupational or academic degrees)
 7: Bachelor's degree (BA, BS, etc.)
 8: Master's degree (MA, MS, MENG, MSW, etc.)
 9: Professional school degree (MD, DDC, JD, etc.)
 10: Doctorate degree (PhD, EdD, etc)
 
```{r}
EMA_Baseline_Covariates_Distinct = load_ema_with_covs(Type="Baseline",
                                                      ema_variables = c("day", "daily_average_crave", "daily_cigs", "daily_stress", "microagg_day", "microagg_count", "daily_average_neg", "daily_average_pos", "stress_day", "stress_events_interpersonal tensions", "stress_events_health/accident", "stress_events_events that happened to others", "stress_events_being evaluated", "stress_events_work/education", "stress_events_home", "stress_events_other", "stress_events_none of the above", "microagg_Because of my education",  "microagg_Because of my gender", "microagg_Because of my income level", "microagg_Because of my race", "microagg_Because of my sexual orientation", "microagg_Because of another personal attribute", "microagg_Because I am a smoker"), 
#Look up variable descriptions in the geo_lifedata.R 
                        redcap_variables = c("pid", "age", "gender", "sexuality", "ethnicity", "ethnicity_open", "race", "race_6_text", "ses_level", "income_individual", "income_household", "school", "jobtitle", "occupation", "industry")) %>% 
  add_descriptives(vars="platformType") %>% 
  distinct()
```

```{r}
cols <- c("stress_events_interpersonal tensions", 
      "stress_events_health/accident", 
      "stress_events_events that happened to others", 
      "stress_events_being evaluated", 
      "stress_events_work/education", 
      "stress_events_home", 
      "stress_events_other", 
      "stress_events_none of the above", 
      "microagg_Because of my education",  
      "microagg_Because of my gender", 
      "microagg_Because of my income level", 
      "microagg_Because of my race", 
      "microagg_Because of my sexual orientation", 
      "microagg_Because of another personal attribute", 
      "microagg_Because I am a smoker")


# Convert them to numeric
EMA_Baseline_Covariates_Distinct[cols] <- lapply(EMA_Baseline_Covariates_Distinct[cols], function(x) as.numeric(as.character(x)))
```

```{r}
head(EMA_Baseline_Covariates_Distinct)
```

## Load in Geo data
```{r, echo=FALSE}
geo_data_baseline_exposures = load_geo_exposures(Type="Baseline")
```

## Join Data
```{r}
All_data <- left_join(geo_data_baseline_exposures, EMA_Baseline_Covariates_Distinct, by = c("pid", "day"))
```

```{r}
head(All_data)
```
```{r}
table(All_data$jobtitle)
```

# Analyses 

## Calculate within and between exposure measures
```{r, echo=FALSE}
All_data = All_data %>%
  split_within_between(c("daily_exposures_500ft_100ft",
                          "daily_exposures_1000ft_100ft",
                         "daily_average_neg",
                          "daily_stress",
                          "microagg_day",
                          "stress_day"))
```

```{r}
All_data = All_data %>%
  split_within_between(c("stress_events_interpersonal tensions", 
      "stress_events_health/accident", 
      "stress_events_events that happened to others", 
      "stress_events_being evaluated", 
      "stress_events_work/education", 
      "stress_events_home", 
      "stress_events_other", 
      "stress_events_none of the above", 
      "microagg_Because of my education",  
      "microagg_Because of my gender", 
      "microagg_Because of my income level", 
      "microagg_Because of my race", 
      "microagg_Because of my sexual orientation", 
      "microagg_Because of another personal attribute", 
      "microagg_Because I am a smoker")) 
```

# Correlation for negative affect variables 
```{r}
cor(All_data$daily_average_neg, All_data$daily_stress, use = "complete.obs")
# r = 0.6367383 which is below 0.7, so I'll be looking at stress and neg mood separately 

#install.packages("rmcorr")
#library(rmcorr)

rmcorr(pid,
daily_average_neg_wn, daily_stress_wn, All_data) # r = 0.4067717, use this stat instead for within person stats. It is below 0.7, so I'll be looking at stress and neg mood separately 
```

## Check day counts for geo data
```{r, echo=FALSE}
min(geo_data_baseline_exposures$day, na.rm = TRUE) # check min value
max(geo_data_baseline_exposures$day, na.rm = TRUE) # check max value
# [1] 1
# [1] 14
```

## check if people have less than x days
```{r, echo=FALSE}
#is this less than 14 days?
print(check_days(All_data))
```

## get participant count
```{r, echo=FALSE}
num_unique_values <- length(unique(All_data$pid))
print(num_unique_values)
# [1] 273
```

## Define models
```{r}
neg_mood_model = create_model_function(
  "daily_average_neg_wn + daily_average_neg_bw + day + (1|pid)"
  )

stress_model = create_model_function(
  "daily_stress_wn + daily_stress_bw + day + (1|pid)"
  )

discrim_model1 = create_model_function(
  "microagg_day + microagg_day_bw + day + (1|pid)"
  )

discrim_model2 = create_model_function(
  "microagg_day_wn + microagg_day_bw + day + (1|pid)"
  )

discrimANDexposure_model_500ft = create_model_function(
  "microagg_day + microagg_day_bw + daily_exposures_500ft_100ft_wn + daily_exposures_500ft_100ft_bw + microagg_day*daily_exposures_500ft_100ft_wn + day + (1|pid)"
  )

discrim2ANDexposure_model_500ft = create_model_function(
  "microagg_day_wn + microagg_day_bw + daily_exposures_500ft_100ft_wn + daily_exposures_500ft_100ft_bw + microagg_day_wn*daily_exposures_500ft_100ft_wn + day + (1|pid)"
  )

discrimANDexposure_model_1000ft = create_model_function(
  "microagg_day + microagg_day_bw + daily_exposures_1000ft_100ft_wn + daily_exposures_1000ft_100ft_bw + microagg_day*daily_exposures_1000ft_100ft_wn + day + (1|pid)"
  )

discrim2ANDexposure_model_1000ft = create_model_function(
  "microagg_day_wn + microagg_day_bw + daily_exposures_1000ft_100ft_wn + daily_exposures_1000ft_100ft_bw + microagg_day_wn*daily_exposures_500ft_100ft_wn + day + (1|pid)"
  )

discrimANDstress_model = create_model_function(
  "microagg_day + microagg_day_bw + stress_day + stress_day_bw + day + (1|pid)"
  )

allstress_model = create_model_function(
  "stress_day + stress_day_bw + day + (1|pid)"
  )

interpersonalstress_model = create_model_function(
  "`stress_events_interpersonal tensions` + `stress_events_interpersonal tensions_bw` + day + (1|pid)"
  )

healthstress_model = create_model_function(
  "`stress_events_health/accident` + `stress_events_health/accident_bw` + day + (1|pid)"
  )


discrimANDhealthstress_model = create_model_function(
  "microagg_day + microagg_day_bw + `stress_events_health/accident` + `stress_events_health/accident_bw` + day + (1|pid)"
  )

otherpeoplestress_model = create_model_function(
  "`stress_events_events that happened to others` + `stress_events_events that happened to others_bw` + day + (1|pid)"
  )

evalstress_model = create_model_function(
  "`stress_events_being evaluated` + `stress_events_being evaluated_bw` + day + (1|pid)"
  )

edustress_model = create_model_function(
  "`stress_events_work/education` + `stress_events_work/education_bw` + day + (1|pid)"
  )

discrimANDedustress_model = create_model_function(
  "microagg_day + microagg_day_bw + `stress_events_work/education` + `stress_events_work/education_bw` + day + (1|pid)"
  )

homestress_model = create_model_function(
  "`stress_events_home` + `stress_events_home_bw` + day + (1|pid)"
  )

otherstress_model = create_model_function(
  "`stress_events_other` + `stress_events_other_bw` + day + (1|pid)"
  )

interpersonalstress_model = create_model_function(
  "`stress_events_interpersonal tensions` + `stress_events_interpersonal tensions` + day + (1|pid)"
  )

interpersonalstress_model = create_model_function(
  "`stress_events_interpersonal tensions` + `stress_events_interpersonal tensions` + day + (1|pid)"
  )
```

# Hypotheses & Research Questions
(switched all models from lme to lmer becuase lme was getting errors when I tried adding random effects)

##Stress as an outcome

### Hypothesis 1:
On days when smokers experience interpersonal discrimination, they will feel more negative than they will on days when they don’t experience interpersonal discrimination.

#### Negative mood as an outcome (H1)
```{r}
lme_neg_discrim1 <- discrim_model1(All_data, "daily_average_neg")
summary(lme_neg_discrim1)

lme_neg_discrim2 <- discrim_model2(All_data, "daily_average_neg")
summary(lme_neg_discrim2)
```
##### Plot/viz (haven't checked/updated)
```{r}
lme_neg_discrim1_plot <- discrim_model1(All_dataNA, "daily_average_neg")
summary(lme_neg_discrim1_plot)
```

```{r}
All_dataNA$predH1b <- predict(lme_neg_discrim1_plot)

ggplot(data=All_dataNA, aes(x=microagg_day, y=predH1b, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="red4") +
  xlab("Interpersonal Discrimination") + ylab("Negative Mood") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination makes people feel more negative")
```

```{r}
ggplot(data=All_dataNA, aes(x=microagg_day, y=predH1b), legend=FALSE) +
  geom_smooth(method=lm, se=TRUE, fullrange=FALSE, lty=1, linewidth=.5, fill="pink", color="black") +
  geom_smooth(aes(group=1), method=lm, se=TRUE, fullrange=FALSE, lty=1, size=2, color="red4", fill="red4", alpha=0.2) +
  xlab("Interpersonal Discrimination") + ylab("Negative Mood") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination was associated \n with feeling more negative")
```


### Hypothesis 2:
On days when smokers experience interpersonal discrimination, they will feel more stressed than they will on days when they don’t experience interpersonal discrimination.

#### Stress as an outcome (H2)
```{r}
#needed to reinstall lme4
lme_stress_discrim1 <- discrim_model1(All_data, "daily_stress")
summary(lme_stress_discrim1)

lme_stress_discrim2 <- discrim_model2(All_data, "daily_stress")
summary(lme_stress_discrim2)
```


##### Plot/Viz (haven't checked/updated)
remove missing data before plotting
```{r}
All_dataNA <- All_data[complete.cases(All_data$daily_stress),]
All_dataNA <- All_dataNA[complete.cases(All_dataNA$microagg_day),]
All_dataNA <- All_dataNA[complete.cases(All_dataNA$daily_average_crave),]
All_dataNA <- All_dataNA[complete.cases(All_dataNA$stress_day),]
All_dataNA <- All_dataNA[complete.cases(All_dataNA$daily_average_neg),]
```

```{r}
lme_stress_discrim1_plot <- discrim_model1(All_dataNA, "daily_stress")
summary(lme_stress_discrim1_plot)
```

```{r}
All_dataNA$predH1 <- predict(lme_stress_discrim1_plot)

ggplot(data=All_dataNA, aes(x=microagg_day, y=predH1, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Interpersonal Discrimination") + ylab("Stress") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination makes people more stresed")
```
```{r}
table(All_dataNA$predH1)
```


```{r}
ggplot(data=All_dataNA, aes(x=microagg_day, y=predH1)) +
  geom_smooth(method=lm, se=TRUE, fullrange=FALSE, lty=1, linewidth=.5, fill="lightblue", color="black") +
  geom_smooth(aes(group=1), method=lm, se=TRUE, fullrange=FALSE, lty=1, size=2, color="blue", fill="blue", alpha=0.2) +
  xlab("Interpersonal Discrimination") + 
  ylab("Stress") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination was associated with \n feeling more stressed")
```



### H3: On days when smokers experience interpersonal discrimination, they will crave cigarettes more than they will on days when they don’t experience interpersonal discrimination 
#### Craving as an outcome
```{r}
lme_craving_discrim1 <- discrim_model1(All_data, "daily_average_crave")
summary(lme_craving_discrim1)

lme_craving_discrim2 <- discrim_model2(All_data, "daily_average_crave")
summary(lme_craving_discrim2)

# Use the model with covariates
lme_craving_discrim1_cov = 
  discrim_model1(
    data = All_data, 
    dv = "daily_average_crave",
    covs ="age") #can add more if I think I should 
summary(lme_craving_discrim1_cov)
```


(non-hypotheses)
```{r}
lme_craving_discrim1ANDexpo500 <- discrimANDexposure_model_500ft(All_data, "daily_average_crave")
summary(lme_craving_discrim1ANDexpo500)
```

```{r}
lme_craving_discrim2ANDexpo500 <- discrim2ANDexposure_model_500ft(All_data, "daily_average_crave")
summary(lme_craving_discrim2ANDexpo500)
```

```{r}
lme_craving_discrim1ANDexpo1000 <- discrimANDexposure_model_1000ft(All_data, "daily_average_crave")
summary(lme_craving_discrim1ANDexpo1000)
```


#### Smoking as an outcome
```{r}
lme_smoke_discrim1 <- discrim_model1(All_data, "daily_cigs")
summary(lme_smoke_discrim1)

lme_smoke_discrim2 <- discrim_model2(All_data, "daily_cigs")
summary(lme_smoke_discrim2)
```


```{r}
lme_smoke_discrim1ANDexpo500 <- discrimANDexposure_model_500ft(All_data, "daily_cigs")
summary(lme_smoke_discrim1ANDexpo500)
```

```{r}
lme_smoke_discrim1ANDexpo1000 <- discrimANDexposure_model_1000ft(All_data, "daily_cigs")
summary(lme_smoke_discrim1ANDexpo1000)
```

####plotting interaction 
```{r}
# Define the variables for the interaction plot
terms <- c("microagg_day", "daily_exposures_500ft_100ft_wn")

# Use ggpredict to calculate and plot the interaction
interact_plot_smoke <- ggpredict(lme_smoke_discrim1ANDexpo500, terms)

# Print the interaction plot
plot(interact_plot_smoke)
```

### Research Question 1: Will participants crave cigarettes more on days they experience other types of stressors (e.g., stress due to home, work, school, finances, etc.) than on days they did not experience those stressors? 
```{r}
lme_craving_allstress <- allstress_model(All_data, "daily_average_crave")
summary(lme_craving_allstress)
```

```{r}
lme_craving_interpersonalstress <- interpersonalstress_model(All_data, "daily_average_crave")
summary(lme_craving_interpersonalstress)
```

```{r}
lme_craving_healthstress <- healthstress_model(All_data, "daily_average_crave")
summary(lme_craving_healthstress)
```


```{r}
lme_craving_otherpeoplestress <- otherpeoplestress_model(All_data, "daily_average_crave")
summary(lme_craving_otherpeoplestress)
```


```{r}
lme_craving_evalstress <- evalstress_model(All_data, "daily_average_crave")
summary(lme_craving_evalstress)
```

```{r}
lme_craving_edustress <- edustress_model(All_data, "daily_average_crave")
summary(lme_craving_edustress)
```


```{r}
lme_craving_homestress <- homestress_model(All_data, "daily_average_crave")
summary(lme_craving_homestress)
```


```{r}
lme_craving_otherstress <- otherstress_model(All_data, "daily_average_crave")
summary(lme_craving_otherstress)
```

### Research Question 2: Will participants crave cigarettes more on days they experience interpersonal discrimination above and beyond experiencing other types of stressors that day? 
```{r}
lme_craving_discrimANDstress <- discrimANDstress_model(All_data, "daily_average_crave")
summary(lme_craving_discrimANDstress)
```

```{r}
lme_craving_discrimANDhealthstress <- discrimANDhealthstress_model(All_data, "daily_average_crave")
summary(lme_craving_discrimANDhealthstress)
```
```{r}
lme_craving_discrimANDedustress <- discrimANDedustress_model(All_data, "daily_average_crave")
summary(lme_craving_discrimANDedustress)
```

####Plot/Viz
```{r}
lme_craving_discrimANDstress_plot <- discrimANDstress_model(All_dataNA, "daily_average_crave")
summary(lme_craving_discrimANDstress_plot)
```

```{r}
All_dataNA$predStressors <- predict(lme_craving_discrimANDstress_plot)

ggplot(data=All_dataNA, aes(x=microagg_day, y=predStressors, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="green4") +
  xlab("Interpersonal Discrimination") + ylab("Cigarette Craving") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination leads to higher craving \n even when controling for other stressors")
```
```{r}
ggplot(data=All_dataNA, aes(x=microagg_day, y=predStressors, legend=FALSE)) +
  geom_smooth(method=lm, se=TRUE, fullrange=FALSE, lty=1, linewidth=.5, fill="lightgreen", color="black") +
  geom_smooth(aes(group=1), method=lm, se=TRUE, fullrange=FALSE, lty=1, size=2, color="green4", fill="green4", alpha=0.2) +
  xlab("Interpersonal Discrimination") + ylab("Cigarette Craving") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination associated with higher craving \n even when controling for (non identity-based) stressors")
```

```{r}
ggplot(data=All_dataNA, aes(x=stress_day, y=predStressors, group=factor(pid), color="gray"), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, linewidth=.5, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="red4") +
  xlab("Other Daily Stressors") + ylab("Cigarette Craving") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Interpersonal discrimination...")
```
```{r}
# Define the variables for the interaction plot
terms <- c("microagg_day", "stress_day")

# Use ggpredict to calculate and plot the interaction
StressorPlot <- ggpredict(lme_craving_discrimANDstress_plot, terms)

# Print the interaction plot
plot(StressorPlot)
```

```{r}
# Define the variables for the interaction plot
terms <- c("stress_day", "microagg_day")

# Use ggpredict to calculate and plot the interaction
StressorPlot2 <- ggpredict(lme_craving_discrimANDstress_plot, terms)

# Print the interaction plot
plot(StressorPlot2)
```

### Research Question 3: Which groups of smokers report experiencinge more interpersonal discrimination in their daily lives? 

#### Delete duplicates in dataset
```{r}

```


Testing writeins  
```{r}
ValueList_race <- pull(DFclean, microagg_text) 

table(ValueList_discrimOther)
```

#### Race and Ethnicity

```{r}
table(All_data$ethnicity)
# Set the reference group to "White"
All_data$race <- relevel(All_data$race, ref = "White")
```

```{r}
summary(lm(microagg_day_bw ~ race, data=All_data)) 
```


